### 2024-11-19 project_21/reports/profiling_plots_2021.Rmd
First push

---
title: "Profiling plots 2021"
author: "Emanuel Mauch"
date: "2023-08-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The following plots are Thermoclines from the ponds used for the Stickleback-
experiments in 2021.
This profiles are used to estimate the actively mixed layer depth of the ponds, which
are subsequently used to model metabolism (GPP, R, NEP).

# Pond-profiles
## B1P1

This is the code for B1P1, the other ponds were analysed equivalently:
```{r, message=FALSE}
# Step 0: set up R-script ------------------------------------------------------
rm(list= ls())

setwd("~/ZIVI_EAWAG/project_21")

source("~/ZIVI_EAWAG/project_21/Moritz_Luehrig_paper_stuff/methods_packages.R")
library(GGally)

# Profile B1P1 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B1P1Sept10_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]

# Rename columns
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 762:812, where the profiling was done
prof <- prof[c(762:812),]

# Create the thermocline plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B1P1 2021-09-10")
```
I interpret that the mixed layer depth in B1P1 was at least 3.163m on Sept 10 2021,
since the demperature differences from top to bottom are only minimal (< 0.5°C).

## B2P2
```{r, echo=FALSE, warning=FALSE}
# Profile B2P2 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P2_Sept12_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 936-964, where the profiling was done
prof <- prof[c(936:964),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P2 2021-09-12")
```
I interpret that the mixed layer depth in B2P2 was at least 1.916m on Sept 12 2021,
since the demperature differences from top to bottom are only minimal (< 0.1°C)

## B3P3
```{r, echo=FALSE, warning=FALSE}
# Profile B3P3 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P3_Sept13_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 811:856, where the profiling was done
prof <- prof[c(811:856),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P3 2021-09-13")
```
I interpret that the mixed layer depth in B3P3 was at least 3.933m on Sept 13 2021,
since the temperature differences from top to bottom are only minimal (< 0.2°C)

## B2P3
```{r, echo=FALSE, warning=FALSE}
# Profile B2P3 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P3_Sept12_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 588:619, where the profiling was done
prof <- prof[c(588:619),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P3 2021-09-12")
```
I interpret that the mixed layer depth in B2P3 was at least 2.842 on Sept 12 2021,
since the temperature differences from top to bottom are only minimal (< 0.1°C)

# B3P1
```{r, echo=FALSE, warning=FALSE}
# Profile B3P1 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P1_Sept13_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 943:966, where the profiling was done
prof <- prof[c(943:966),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P1 2021-09-13")
```
I interpret that the mixed layer depth in B3P1 was at least 1.494m on Sept 13 2021,
since the temperature differences from top to bottom are only minimal (< 0.2°C).

# B3P2
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P2_Sept13_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 979:1028, where the profiling was done
prof <- prof[c(979:1028),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P2 2021-09-13")
```
I interpret that the mixed layer depth in B3P2 was at least 2.988m on Sept 13 2021,
since the temperature differences from top to bottom are only minimal (< 0.1°C).

## B3P0
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P0_Sept13_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 649:694, where the profiling was done
prof <- prof[c(649:694),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P0 2021-09-13")
```
I interpret that the mixed layer depth in B3P0 was at least 2.978m on Sept 13 2021,
since the temperature differences from top to bottom are only minimal (< 0.1°C).

## ERL85
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL85_Sept21_2021.csv", sep = ",")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 991:1108, where the profiling was done
prof <- prof[c(992:1108),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL85 2021-09-21")
```
I interpret that the mixed layer depth in ERL85 was at least 6.819m on Sept 21 2021,
since the temperature differences from top to bottom are only minor (< 0.6°C).

## B2P4
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P4_Sept15_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 912:969, where the profiling was done
prof <- prof[c(912:969),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P4 2021-09-15")
```
Even though the temperature difference from top to bottom is about 1.4°C,
I would say that the mixed layer depth of B2P4 on Sept 15 2021 was at least
4.857m.

## ERL152
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL152_Sept16_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 521:565, where the profiling was done
prof <- prof[c(521:565),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL152 2021-09-16")
```
I interpret that the mixed layer depth in ERL152 was at least 4.117m on Sept 16 2021,
since the temperature differences from top to bottom are only minor (< 0.2°C)

## ERL122
```{r, echo=FALSE, warning=FALSE}
# Profile ERL122 ---------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL122_Sept16_2021.csv", sep = ";")
# In lake ERL122, the profile datset seems to be cut right about at the moment the sondes
# reaches its deepest point

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 515:561, where the profiling was done
prof <- prof[c(515:561),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL122 2021-09-16")
```
I interpret that the mixed layer depth in ERL122 was at least 3.783m on Sept 16 2021,
since the temperature differences from top to bottom are only minor (< 0.4°C)

## B1P4 
```{r, echo=FALSE, warning=FALSE}
# Profile B1P4 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B1P4_Sept11_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 1148:1193, where the profiling was done
prof <- prof[c(1148:1193),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B1P4 2021-09-11")
```
I interpret that the mixed layer depth in B1P4 was at least 1.681m on Sept 11 2021,
since the temperature differences from top to bottom are only minimal (< 0.1°C).

# Appendix
## Version and packages used to generate this report:
```{r, echo=FALSE}
cat(paste(Sys.time(), Sys.timezone(), "\n"))
sessionInfo()
```

## Code used to generate the plots:
```{r, eval=FALSE}
################################################################################
# This is a code to plot the sondes profiles of 2021 to determine a reasonable
# actively mixed layer depth for the metabolism models of the different ponds
################################################################################

# Step 0: set up R-script ------------------------------------------------------
rm(list= ls())

setwd("~/ZIVI_EAWAG/project_21")

source("~/ZIVI_EAWAG/project_21/Moritz_Luehrig_paper_stuff/methods_packages.R")
library(GGally)

# Profile B1P1 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B1P1Sept10_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]

# Rename columns
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 762:812, where the profiling was done
prof <- prof[c(762:812),]

# Create the thermocline plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B1P1 2021-09-10")

# I interpret that the mixed layer depth in B1P1 was at least 3.163m on Sept 10 2021,
# since the demperature differences from top to bottom are only minimal (< 0.5°C)

# Profile B2P2 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P2_Sept12_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 936-964, where the profiling was done
prof <- prof[c(936:964),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P2 2021-09-12")

# I interpret that the mixed layer depth in B2P2 was at least 1.916m on Sept 12 2021,
# since the demperature differences from top to bottom are only minimal (< 0.1°C)

# Profile B3P3 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P3_Sept13_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 811:856, where the profiling was done
prof <- prof[c(811:856),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P3 2021-09-13")

# I interpret that the mixed layer depth in B3P3 was at least 3.933m on Sept 13 2021,
# since the temperature differences from top to bottom are only minimal (< 0.2°C)

# Profile B2P3 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P3_Sept12_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 588:619, where the profiling was done
prof <- prof[c(588:619),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P3 2021-09-12")

# I interpret that the mixed layer depth in B2P3 was at least 2.842 on Sept 12 2021,
# since the temperature differences from top to bottom are only minimal (< 0.1°C)

# Profile B3P1 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P1_Sept13_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 943:966, where the profiling was done
prof <- prof[c(943:966),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P1 2021-09-13")

# I interpret that the mixed layer depth in B3P1 was at least 1.494m on Sept 13 2021,
# since the temperature differences from top to bottom are only minimal (< 0.2°C)

# Profile B3P2 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P2_Sept13_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 979:1028, where the profiling was done
prof <- prof[c(979:1028),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P2 2021-09-13")

# I interpret that the mixed layer depth in B3P2 was at least 2.988m on Sept 13 2021,
# since the temperature differences from top to bottom are only minimal (< 0.1°C)

# Profile B3P0 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B3P0_Sept13_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 649:694, where the profiling was done
prof <- prof[c(649:694),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P0 2021-09-13")

# I interpret that the mixed layer depth in B3P0 was at least 2.978m on Sept 13 2021,
# since the temperature differences from top to bottom are only minimal (< 0.1°C)

# Profile ERL85 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL85_Sept21_2021.csv", sep = ",")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 991:1108, where the profiling was done
prof <- prof[c(992:1108),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL85 2021-09-21")

# I interpret that the mixed layer depth in ERL85 was at least 6.819m on Sept 21 2021,
# since the temperature differences from top to bottom are only minor (< 0.6°C)

# Profile B2P4 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B2P4_Sept15_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 912:969, where the profiling was done
prof <- prof[c(912:969),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P4 2021-09-15")

# Even though the temperature difference from top to bottom is about 1.4°C,
# I would say that the mixed layer depth of B2P4 on Sept 15 2021 was at least
# 4.857m.

# Profile ERL152 ---------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL152_Sept16_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 521:565, where the profiling was done
prof <- prof[c(521:565),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL152 2021-09-16")
# I interpret that the mixed layer depth in ERL152 was at least 4.117m on Sept 16 2021,
# since the temperature differences from top to bottom are only minor (< 0.2°C)

# Profile ERL122 ---------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/ERL122_Sept16_2021.csv", sep = ";")
# In lake ERL122, the profile datset seems to be cut right about at the moment the sondes
# reaches its deepest point

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 515:561, where the profiling was done
prof <- prof[c(515:561),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile ERL122 2021-09-16")
# I interpret that the mixed layer depth in ERL122 was at least 3.783m on Sept 16 2021,
# since the temperature differences from top to bottom are only minor (< 0.4°C)

# Profile B1P4 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_21/sondes_profiling/B1P4_Sept11_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 1148:1193, where the profiling was done
prof <- prof[c(1148:1193),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B1P4 2021-09-11")
# I interpret that the mixed layer depth in B1P4 was at least 1.681m on Sept 11 2021,
# since the temperature differences from top to bottom are only minimal (< 0.1°C)
```

### 2024-11-19 project_21/reports/project_report1_2021.Rmd
First push

---
title: "Report data processing 2021"
author: "Emanuel Mauch"
date: "2023-07-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This is a report of what I have done so far regarding the sondes data of 2021. For the analysis, I adapted Moritz' code
from his paper (https://doi.org/10.1002/ecy.3371). I have cleaned all the raw datasets, stored them as .txt files (folder "Raw_sonde_2021_2"), merged them with RStudio, processed the merged dataset and plotted some figures for the parameters of interest discussed with Blake and Danina. The code was adapted from Moritz' file "make_data.R", using his "method_packages.R". All the files I've used to make this report are in the "project_21" folder that I have uploaded.

# Steps done so far
## Step 0: Clean raw datafiles in Excel, store them as .txt files
I cleaned all the raw .csv files with Excel (e.g. reassembling split files, fixing date bugs which lead to wrong .txt file conversions etc.). They can be found in the folder "Raw_sonde_2021_2".

## Step 1: set up R-script
```{r}
rm(list= ls())

setwd("~/ZIVI_EAWAG/project_21")

source("~/ZIVI_EAWAG/project_21/Moritz_Luehrig_paper_stuff/methods_packages.R")
library(GGally)

sonde_key = fread( "~/ZIVI_EAWAG/project_21/sondes_key_2021.txt", header=T)
```

## Step 2: merge all raw data files into a single big one
```{r}
path = "~/ZIVI_EAWAG/project_21/raw_data/Raw_sonde_2021_2"
filenames <- list.files(path=path, pattern=".txt")
files<-data.table(NULL)

system.time(for(i in filenames){
  filepath <- file.path(path,paste(i,sep=""))
  dummy1<-fread(filepath,
                colClasses = "character" ,
                sep = "\t",
                header = FALSE,
                fill=TRUE,
                encoding ="UTF-8")
  rownumb<-dummy1[V1 %like% "(MM/DD/YYYY)", which=TRUE]+1
  colname<-dummy1[V1 %like% "(MM/DD/YYYY)"]
  colname<-gsub(" ", "",(gsub("[[:punct:]]", "",c(lapply(colname,as.character)))))
  colname<-unlist(strsplit(colname,"\t"))
  dummy2<-dummy1[rownumb:.N]
  setnames(dummy2,colname)
  dummy2[,(colname[c(3,5:length(dummy2))]):=lapply(.SD, as.numeric),.SDcols=colname[c(3,5:length(dummy2))]]
  dummy2$Pond<-sub("_Sept.*", "", i)
  dummy2$Source_file<-i
  files<-rbindlist(list(files, dummy2), fill=TRUE)
})

all <- files

# remove last 3 columns (some variables only measured by few sondes)
all <- all[,!c("Depthm", "Pressurepsia", "VerticalPositionm")]

# replace "µ" with "" in colnames
setnames(all, gsub("µ", "",  names(all)))

# save intermediate stage 1 (FULL RAW DATA, NO REMOVAL)
fwrite(all, "~/ZIVI_EAWAG/project_21/intermediate_processing_steps/ponds_sonde_data_intermediate_1.txt", sep="\t")
print(head(all,3))
```

## Step 3: add exp. design, phases and format time
```{r}
all <- fread("~/ZIVI_EAWAG/project_21/intermediate_processing_steps/ponds_sonde_data_intermediate_1.txt", sep="\t")

# format date & time
all$TimeHHMMSS<-substr(all$TimeHHMMSS,1,5) #gsub("\\D+", "", cleaning$TimeHHMMSS)
all$DateMMDDYYYY<-mdy(all$DateMMDDYYYY)
all$Date_time<-ymd_hm(paste(all$DateMMDDYYYY, all$TimeHHMMSS))
setnames(all,1:2,c("Date","Time"))

# Cut before and after to obtain the same period for all the ponds
# 2021-09-16 22:00:00 to 2021-09-24 03:00:00
all <- subset(all, Date_time>"2021-09-16 22:00:00") # For some reason: starts at 2021-09-16 20:00:00
all <- subset(all, Date_time<"2021-09-24 05:00:00") # For some reason: ends at 2021-09-24 03:00:00

# add fractions of day since start
all[,Time_seq:=round(((as.numeric(Date_time))-
                        (as.numeric(Date_time)[1]))/86400,7)]

# merge with key
all<-merge(all,sonde_key, by = "Pond")

# reorder and revalue
setorderv(all, c("Pond", "Date_time"), c(1, 1))

# select columns to keep
all<-all[,c("Pond", "Treatment", "Date_time", "Time_seq",
            "ChlorophyllRFU", "ChlorophyllugL", "ConduScm" , "BGAPCRFU", 
            "BGAPCugL", "ODOsat", "ODOmgL", "pH", "fDOMRFU", "SpConduScm", "TempC")]

# rename
setnames(all, c("Pond", "Treatment", "Date_time", "Time_seq",
                "Chlorophyll_RFU", "Chlorophyll_ugL", "Cond_uScm", "BGAPC_RFU",
                "BGAPC_ugL", "ODO_sat", "ODO_mgL", "pH", "fDOM_RFU", "SpCond_uScm", "Temp_C"))

# debug: rm duplicate value
all = unique(all, by=c("Pond", "Time_seq"))

fwrite(all, "~/ZIVI_EAWAG/project_21/intermediate_processing_steps/ponds_sonde_data_intermediate_2.txt", sep="\t")
print(head(all,3))
```

# Step 4.1: remove outliers
The outlier plots are in the folder "outliers".

```{r, eval=FALSE}
all <- fread("~/ZIVI_EAWAG/project_21/intermediate_processing_steps/ponds_sonde_data_intermediate_2.txt", sep="\t")

save_path = "outliers/"

for(i in  c("Chlorophyll_RFU", "BGAPC_RFU", "ODO_mgL")){
  all[,  (i) := lapply(.SD[,..i],
                       outlier_removal,
                       window=48,
                       threshold=10,
                       plot=T,
                       return="removed",
                       save=T,
                       path=save_path,
                       name=paste0(i,"_",Pond)),
      by = c("Pond")]
}

for(i in c("fDOM_RFU")){
  all[,  (i) := lapply(.SD[,..i],
                       outlier_removal,
                       window=96,
                       threshold=10,
                       plot=F,
                       return="removed",
                       save=T,
                       path=save_path,
                       name=paste0(i,"_",Pond)),
      by = c("Pond")]
}

for(i in c("Temp_C", "SpCond_uScm", "Cond_uScm")){
  all[,  (i) := lapply(.SD[,..i],
                       outlier_removal,
                       window=96,
                       threshold=20,
                       plot=F,
                       return="removed",
                       save=T,
                       path=save_path,
                       name=paste0(i,"_",Pond)),
      by = c("Pond")]
}

# save
fwrite(all, "~/ZIVI_EAWAG/project_21/intermediate_processing_steps/ponds_sonde_data_intermediate_3.1.txt", sep="\t")
```

## Step 4.2: remove anomalies
We inspected the data for anomalies and remove them here - for details see 
Russo, S., M. Lührig, W. Hao, B. Matthews, and K. Villez. 2020. 
Active learning for anomaly detection in environmental data. 
Environmental Modelling & Software 134:104869.

I didn't do this step, since I would need some time to refresh my python skills, 
but if you think it is worth, I will manage.

## Step 5: add light and precipitation data
I do not have this data available.

## Step 6: intercept correction
This uses the results form a cross correlation survey to adjust the 
sondes for "off factory differences, i.e. remove any intercept variation
among the data.

I do not have the sonds correlation factors.

## Step 7: save
```{r, eval=FALSE}
# order and remove rownames
all = all[order(Pond, Time_seq), ]
rownames(all)<-NULL

fwrite(all, "~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_all.txt")
```

```{r}
all<-fread("~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_all.txt")
print(head(all,3))
```

## Step 8: check completeness
```{r}
all <- fread("~/ZIVI_EAWAG/project_21/intermediate_processing_steps/ponds_sonde_data_intermediate_3.1.txt", sep="\t")
all$Date_time <- as.POSIXct((all$Time_seq*86400), origin="2021-09-16 20:00:00", tz="UTC")
# is that the correct code for as.POSIXTct in our case?

all$Date <-date(all$Date_time)

# N per date
all[, N := uniqueN(Date), by = Pond]
complete <- setDT(data.frame(unclass(table(all$Date, all$Pond))), keep.rownames=T)
colnames(complete)[1]<-"Date"
fwrite(complete, "~/ZIVI_EAWAG/project_21/data/sonde_data_completeness.txt", sep="\t")
# Some major data-gaps for B1P1!

print(complete)
```

## Step 9: calculate daily averages
Does it make sense to calculate daily averages in our case?
```{r}
all<-fread("~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_all.txt")

all[,Time_seq:=as.integer(Time_seq)]

parameters = c("Chlorophyll_RFU", "Chlorophyll_ugL", "Cond_uScm", "BGAPC_RFU", "BGAPC_ugL",
               "ODO_sat", "ODO_mgL", "pH", "fDOM_RFU", "SpCond_uScm",
               "Temp_C")
groups = c("Time_seq", "Pond", "Treatment")

all.summ = all[,lapply(.SD, m_r, 2), by=groups, .SDcols = parameters]

fwrite(all.summ, "~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_daily_avg.txt", sep=",")

table(all.summ$Pond, all.summ$Treatment)
print(head(all.summ,3))
```

## Step 10: hourly averages
```{r}
all<-fread("~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_all.txt")

parameters = c("Chlorophyll_RFU", "Cond_uScm", "BGAPC_RFU", "ODO_mgL", "pH",
               "fDOM_RFU", "SpCond_uScm", "Temp_C")

all$Time_seq = as.integer(all$Time_seq)
all$Hour <- as.numeric(substr(as.character(all$Date_time),12,13))

groups = c("Time_seq", "Hour", "Pond", "Treatment")

all.summ = all[,lapply(.SD, m_r, 2), by=groups, .SDcols = parameters]

fwrite(all.summ, "~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_hourly_avg.txt", sep=",")
print(head(all.summ,3))
```

## Step 11: 10-minute averages
I thought that maybe the hour interval is too large for our time series,
so maybe a 10-minute interval could be more appropriate (or just plot¨
the absolute values).

```{r}
all<-fread("~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_all.txt")

parameters = c("Chlorophyll_RFU", "Chlorophyll_ugL", "Cond_uScm", "BGAPC_RFU", "BGAPC_ugL",
               "ODO_sat", "ODO_mgL", "pH", "fDOM_RFU", "SpCond_uScm",
               "Temp_C")

all$Date_time <- as.POSIXct((all$Time_seq*86400), origin="2021-09-16 20:00:00", tz="UTC")
# is that the correct code for as.POSIXTct in our case?

all$Time_seq = as.integer(all$Time_seq)
all$Hour <- as.numeric(substr(as.character(all$Date_time),12,13))
all$Ten_min <- as.numeric(substr(as.character(all$Date_time),15,15))

groups = c("Time_seq", "Hour", "Ten_min", "Pond", "Treatment")

all.summ = all[,lapply(.SD, m_r, 2), by=groups, .SDcols = parameters]

fwrite(all.summ, "~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_ten_min_avg.txt", sep=",")
print(head(all.summ,3))
```

## Step 12: Calculate overall averages of individual ponds
```{r}
all<-fread("~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_all.txt")

parameters = c("Chlorophyll_RFU", "Cond_uScm", "BGAPC_RFU", "ODO_mgL", "pH",
               "fDOM_RFU", "SpCond_uScm", "Temp_C")
groups = c("Pond","Treatment")

all.summ = all[,lapply(.SD, m_r, 2), by=groups, .SDcols = parameters]

fwrite(all.summ, "~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_overall_avg.txt", sep=",")

table(all.summ$Pond, all.summ$Treatment)
```

## Step 13: control plots
```{r}
all<-fread("~/ZIVI_EAWAG/project_21/data/ponds_sonde_data_all.txt")

all$Date_time <- as.POSIXct((all$Time_seq*86400), origin="2021-09-16 20:00:00", tz="UTC")

table(all$Pond, all$Treatment)
```

### Chlorophyll RFU
```{r, echo=FALSE, fig.height=9}
# Chlorophyll RFU
p1 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p2 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p1, p2, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))
```

### BGAPC RFU
```{r, echo=FALSE, fig.height=9}
# BGAPC RFU
p3 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p4 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p3, p4, nrow = 2)
```

### ODO mg/L
```{r, echo=FALSE, fig.height=9, warning=FALSE}
# ODO mg/L
p5 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p6 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p5, p6, nrow = 2)
```

### Cond uS/cm
```{r, echo=FALSE, fig.height=9}
# Cond uS/cm
p7 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p8 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p7, p8, nrow = 2)
```

###  Specific Conductivity uS/cm
```{r, echo=FALSE, fig.height=9}
# Specific Cond uS/cm
p9 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p10 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p9, p10, nrow = 2)
```

### fDOM RFU
```{r, echo=FALSE, fig.height=9}
# fDOM RFU
p11 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p12 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p11, p12, nrow = 2)
```

# 14: Appendix
## Version and packages used to generate this report:
```{r, echo=FALSE}
cat(paste(Sys.time(), Sys.timezone(), "\n"))
sessionInfo()
```
## Code used to generate control plots:
```{r, eval=FALSE}
# Chlorophyll RFU
p1 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p2 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p1, p2, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))

# BGAPC RFU
p3 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p4 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p3, p4, nrow = 2)

# ODO mg/L
p5 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p6 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p5, p6, nrow = 2)

# Cond uS/cm
p7 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p8 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p7, p8, nrow = 2)

# Specific Cond uS/cm
p9 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p10 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p9, p10, nrow = 2)

# fDOM RFU
p11 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p12 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B1P4"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL122"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B1P4', "ERL152", "ERL85", "ERL122"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B1P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate", "ERL122"="midnightblue")) +
  ggtitle("Fishless reference")

plot_grid(p11, p12, nrow = 2)
```

### 2024-11-19 project_22/reports/profiling_plots__2022.Rmd
First push

---
title: "Profiling-plots 2022"
author: "Emanuel Mauch"
date: "2023-08-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The following plots are Thermoclines from the ponds used for the Stickleback-
experiments in 2022.
For some of the ponds, the profiling was not done in 2022, and data from 2021
was subsequently taken.
This profiles are used to estimate the actively mixed layer depth of the ponds, which
are subsequently used to model metabolism (GPP, R, NEP).

# Pond-profiles
## B3P3

This is the code for B3P3, the other ponds were analysed equivalently:
```{r, message=FALSE}
# Step 0: set up R-script
rm(list= ls())

setwd("~/ZIVI_EAWAG/project_22")

source("~/ZIVI_EAWAG/project_22/Moritz_Luehrig_paper_stuff/methods_packages.R")
library(GGally)

prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B3P3 June 21 22.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]

# Rename columns
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 464-555, where the profiling was done
prof <- prof[c(464:531),]

# Create the thermocline plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B3P3 2022")

# I interpert that the mixed layer depth is only about 0.5 meters deep, since
# Temperature starts to decline rapidly after 0.5 meters from about 14.25 down to 13.00
# at 1.75 meters.
# -> mixed layer depth = 0.5m
```
I interpert that the mixed layer depth is only about 0.5 meters deep, since
Temperature starts to decline rapidly after 0.5 meters from about 14.25 down to 13.00
at 1.75 meters. -> mixed layer depth = 0.5m

## B1P1
```{r, echo=FALSE, warning=FALSE}
#####
# This is the profile from 2021, since for 2022, it was not available
#####
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B1P1Sept10_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 756-813, where the profiling was done
prof <- prof[c(756:813),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B1P1 2021")

# The drop in temperature is very small (<0.5°C) and I therefore conlcude that the
# actively mixed layer depth at that time was at least 3 meters.

# -> set mixed layer depth to maximum profiling depth (3.163m)
```
The drop in temperature is very small (<0.5°C) and I therefore conlcude that the
actively mixed layer depth at that time was at least 3 meters. -> set mixed layer depth to maximum profiling depth (3.163m)

## B2P2
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B2P2 June 19 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 219-278, where the profiling was done
prof <- prof[c(219:278),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P2 2022")

# Same temperature across all depths

# -> set mixed layer depth to maximum profiling depth (1.948m)
```
Same temperature across all depths. -> set mixed layer depth to maximum profiling depth (1.948m)

## B2P3
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B2P3 June 19 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 216-283, where the profiling was done
prof <- prof[c(216:283),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B2P3 2022")

# Same temperature across all depths

# -> set mixed layer depth to maximum profiling depth (3.144m)
```
Same temperature across all depths. -> set mixed layer depth to maximum profiling depth (3.144m)

# B3P1
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B3P1 June 20 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 173-238, where the profiling was done
prof <- prof[c(173:238),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B3P1 2022")

# Same temperature across all depths

# -> set mixed layer depth to maximum profiling depth (2.026m)
```
Same temperature across all depths. -> set mixed layer depth to maximum profiling depth (2.026m)

# B3P2
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B3P2 June 20 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 150-188, where the profiling was done
prof <- prof[c(150:188),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B3P2 2022")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (1.928m)
```
Same temperature across all depths (difference < 0.5°C). -> set mixed layer depth to maximum profiling depth (1.928m)

## B3P0
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B3P0 June 20 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 257-307, where the profiling was done
prof <- prof[c(257:307),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B3P0 2022")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (1.713m)
```
Same temperature across all depths (difference < 0.5°C). -> set mixed layer depth to maximum profiling depth (1.713m)

## ERL85
```{r, echo=FALSE, warning=FALSE}
#####
# This is the profile from 2021, since for 2022, it was not available
#####
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/ERL85_Sept21_2021.csv", sep = ",")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 992-1108, where the profiling was done
prof <- prof[c(992:1108),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile ERL85 2021")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (1.713m)
```
Same temperature across all depths (difference < 0.5°C). -> set mixed layer depth to maximum profiling depth (1.713m)

## B2P4
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B2P4 June 19 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 789-869, where the profiling was done
prof <- prof[c(789:869),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B2P4 2022")

# Quite a steep thermocline from 2m downwards

# -> set mixed layer depth to 2m
```
Quite a steep thermocline from 2m downwards. -> set mixed layer depth to 2m

## ERL152
```{r, echo=FALSE, warning=FALSE}
#####
# This is the profile from 2021, since for 2022, it was not available
#####
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/ERL152_Sept16_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 521-565, where the profiling was done
prof <- prof[c(521:565),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile ERL152 2021")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (4.117m)
```
Same temperature across all depths (difference < 0.5°C). -> set mixed layer depth to maximum profiling depth (4.117m)

## B3P4
```{r, echo=FALSE, warning=FALSE}
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B3P4 June 21 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 505-543, where the profiling was done
prof <- prof[c(505:543),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B3P4 2022")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (1.879)
```
Same temperature across all depths (difference < 0.5°C). -> set mixed layer depth to maximum profiling depth (1.879)

# Appendix
## Version and packages used to generate this report:
```{r, echo=FALSE}
cat(paste(Sys.time(), Sys.timezone(), "\n"))
sessionInfo()
```

## Code used to generate the plots:
```{r, eval=FALSE}
# Profile B1P1 -----------------------------------------------------------------

#####
# This is the profile from 2021, since for 2022, it was not available
#####
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B1P1Sept10_2021.csv", sep = ";")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 756-813, where the profiling was done
prof <- prof[c(756:813),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B1P1 2021")

# The drop in temperature is very small (<0.5°C) and I therefore conlcude that the
# actively mixed layer depth at that time was at least 3 meters.

# -> set mixed layer depth to maximum profiling depth (3.163m)

# Profile B2P2 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B2P2 June 19 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 219-278, where the profiling was done
prof <- prof[c(219:278),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)), ylab = "Depth (m)",
     main = "Profile B2P2 2022")

# Same temperature across all depths

# -> set mixed layer depth to maximum profiling depth (1.948m)

# Profile B2P3 -----------------------------------------------------------------
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B2P3 June 19 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 216-283, where the profiling was done
prof <- prof[c(216:283),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B2P3 2022")

# Same temperature across all depths

# -> set mixed layer depth to maximum profiling depth (3.144m)

# Profile B3P1 -----------------------------------------------------------------
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B3P1 June 20 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 173-238, where the profiling was done
prof <- prof[c(173:238),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B3P1 2022")

# Same temperature across all depths

# -> set mixed layer depth to maximum profiling depth (2.026m)

# Profile B3P2 -----------------------------------------------------------------
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B3P2 June 20 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 150-188, where the profiling was done
prof <- prof[c(150:188),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B3P2 2022")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (1.928m)

# Profile B3P0 -----------------------------------------------------------------
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B3P0 June 20 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 257-307, where the profiling was done
prof <- prof[c(257:307),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B3P0 2022")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (1.713m)

# Profile ERL85 -----------------------------------------------------------------

#####
# This is the profile from 2021, since for 2022, it was not available
#####
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/ERL85_Sept21_2021.csv", sep = ",")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 992-1108, where the profiling was done
prof <- prof[c(992:1108),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile ERL85 2021")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (1.713m)

# Profile B2P4 -----------------------------------------------------------------
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B2P4 June 19 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 789-869, where the profiling was done
prof <- prof[c(789:869),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B2P4 2022")

# Quite a steep thermocline from 2m downwards

# -> set mixed layer depth to 2m

# Profile ERL152 ---------------------------------------------------------------

#####
# This is the profile from 2021, since for 2022, it was not available
#####
prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/ERL152_Sept16_2021.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V10", "V29")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 521-565, where the profiling was done
prof <- prof[c(521:565),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile ERL152 2021")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (4.117m)

# Profile B3P4 -----------------------------------------------------------------

prof <- fread("~/ZIVI_EAWAG/project_22/sonde_profiling/B3P4 June 21 22.txt", sep = "\t")

# Choose columns of interest
prof <- prof[,c("V8", "V23")]
prof <- setnames(prof, c("Depth_m", "Temp_C"))

# As numeric
prof$Depth_m <- as.numeric(prof$Depth_m)
prof$Temp_C <- as.numeric(prof$Temp_C)

# Choose rows 505-543, where the profiling was done
prof <- prof[c(505:543),]

# plot
plot(prof$Temp_C, prof$Depth_m, type = "o", xlab = "Temperature (°C)",
     ylim = c(max(prof$Depth_m), min(prof$Depth_m)),
     ylab = "Depth (m)", main = "Profile B3P4 2022")

# Same temperature across all depths (difference < 0.5°C)

# -> set mixed layer depth to maximum profiling depth (1.879)
```

### 2024-11-19 Literature/Moritz_Luehrig_paper_stuff/make_data.R

@@ -1,0 +1,407 @@
+# step 0: startup --------------------------------------------------------------
+
+rm(list = ls())
+
+# replace for your directory
+setwd("D:/Temp/pond_exp_osf")
+
+source("./R/methods_packages.R")
+
+corr<-fread("./data_raw/ponds_sonde_corr_factors.txt")
+sonde_key = fread( "./data_raw/ponds_sonde_key.txt"  ,header=T)
+
+# step 1: merge all raw data files into a single big one -------------------
+## takes a while to run
+
+path = "./data_raw/sonde_csv_files"
+filenames <- list.files(path=path, pattern=".txt")
+files<-data.table(NULL)
+
+system.time(for(i in filenames){
+  filepath <- file.path(path,paste(i,sep=""))
+  dummy1<-fread(filepath,
+                colClasses = "character" ,
+                sep = "\t",
+                header = FALSE,
+                fill=TRUE,
+                encoding ="UTF-8")
+  rownumb<-dummy1[V1 %like% "(MM/DD/YYYY)", which=TRUE]+1
+  colname<-dummy1[V1 %like% "(MM/DD/YYYY)"]
+  colname<-gsub(" ", "",(gsub("[[:punct:]]", "",c(lapply(colname,as.character)))))
+  colname<-unlist(strsplit(colname,"\t"))
+  dummy2<-dummy1[rownumb:.N]
+  dummy3<-dummy2[,tstrsplit(V1, "\t", fixed=TRUE)]
+  setnames(dummy3,colname)
+  dummy3[,(colname[c(3,5:length(dummy3))]):=lapply(.SD, as.numeric),.SDcols=colname[c(3,5:length(dummy3))]]
+  dummy3$Sonde<-substr(i, 1,7)
+  dummy3$Source_file<-i
+  files<-rbindlist(list(files, dummy3), fill=TRUE)
+})
+
+all <- files
+
+# replace "µ" with "" in colnames
+setnames(all, gsub("µ", "",  names(all)))
+
+# save intermediate stage 1 (FULL RAW DATA, NO REMOVAL)
+fwrite(all, "./data/intermediate_processing_steps/ponds_sonde_data_intermediate_1.txt", sep="\t")
+
+
+# step 2: add exp. design, phases and format time ---------------------------
+
[…]

### 2024-11-19 Literature/Moritz_Luehrig_paper_stuff/make_figures.R

@@ -1,0 +1,608 @@
+# startup ------------------------------------------------------------------
+
+# replace for your directory
+setwd("D:/Temp/pond_exp_osf")
+
+rm(list = ls())
+
+source("./R/methods_packages.R")
+
+
+# load data --------------------------------------------------------------------
+
+## data
+all<-fread("./data/ponds_sonde_data_all.txt")
+all[, Date := as.Date(Time_seq, origin="2016-06-25", tz="UTC")]
+all[, Date_time := as.POSIXct(Time_seq*86400, origin="2016-06-25 00:00:00", tz="UTC")]
+
+hourly<-fread("./data/ponds_sonde_data_hourly_avg.txt")
+hourly[, Date := as.Date(Time_seq, origin="2016-06-25", tz="UTC")]
+hourly[, Date_time := ymd_hms(paste(Date, paste0(Hour,":00:00")))]
+
+daily<-fread("./data/ponds_sonde_data_daily_avg.txt")
+daily[, Date := as.Date(Time_seq, origin="2016-06-25", tz="UTC")]
+
+## meta info
+key<-fread("./data_raw/ponds_sonde_key.txt")
+pond.treat.col<-c(C= "#0570b0" ,O = "grey50",D = "#f46d43", M = "#7fbc41", MD = "#dd3497",   "Additive" = "grey20")
+
+## disturbance timepoints & phases
+dist_seq = c(48, 62, 76, 90, 107, 472)
+dist_dates<-ymd(c("2016-08-12", "2016-08-26", "2016-09-09", "2016-09-23", "2016-10-10", "2017-10-10"))
+dist_phases = data.table(Subphase=1:12, Disturbance=c(F,F,T,T,T,T,T,F,F,F,T,F))
+
+## exclude dates (phase 1 and ice cover)
+time_seq_excl = unique(daily[Subphase==1 | (Subphase==8 & Time_seq>170),]$Time_seq)
+daily = daily[!Time_seq %in% time_seq_excl,]
+hourly = hourly[!Time_seq %in% time_seq_excl,]
+all = all[!Time_seq %in% time_seq_excl,]
+
+cols = c("Chlorophyll_RFU", "BGAPC_RFU", "ODO_sat", "fDOM_RFU")
+cols.metab=c("GPP","NEP","R_day")
+date_breaks = c(as.Date("2016-07-30"),as.Date("2016-09-20"), as.Date("2016-11-15"), 
+                as.Date("2017-04-15"), as.Date("2017-06-15"), as.Date("2017-08-15"),
[…]

### 2024-11-19 Literature/Moritz_Luehrig_paper_stuff/methods_packages.R

@@ -1,0 +1,114 @@
+
+rm(list= ls())
+# load packages -----------------------------------------------------------
+
+pkgs<-c(
+  "bit64",
+  "cowplot",
+  "data.table",
+  "lubridate",
+  "tidyverse",
+  "viridis",
+  "zoo"
+)
+
+## install if needed
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(char=pkgs,install=T)
+rm(pkgs)
+
+
+# outlier removal function ------------------------------------------------
+
+outlier_removal <- function(timeseries, window, threshold, return="removed", plot=F, save=F, name, path){
+  
+  upper <- rollapply(timeseries, window, FUN=function(x){
+    m = median(x); median(x) + threshold * median(abs(x - m))
+  }, fill=NA)
+  
+  lower <- rollapply(timeseries, window, FUN=function(x){
+    m = median(x); median(x) - threshold * median(abs(x - m))
+  }, fill=NA)
+  
+  outliers <- timeseries > upper | timeseries < lower
+  n_out <- length(timeseries[outliers])
+  n <- length(outliers)
+
+  
+  if(plot==T){
+    x=seq(1,length(timeseries),1)
+    plot(x,timeseries, type="l", lwd=1.5, col="red", 
+            ylim=c(min(lower, na.rm = T)-(min(lower, na.rm = T)/50), c(max(upper, na.rm = T)+(max(upper, na.rm = T)/50))))
+    lines(x, upper, col="blue", lwd=1)
+    lines(x, lower, col="blue", lwd=1)
+    points(x[outliers], timeseries[outliers], pch=19, cex=1)
+    title(name, sub = paste("window = ",window, ", threshold = ", threshold, ", number of outliers = ", n_out, ", number of observations = ", n))
+    dev.off()
+  }
+  if(save==T){
+    save_path = file.path(getwd(), path)
+    dir.create(save_path, recursive=T)
+    png(paste0(save_path, "/",name, ".png"), width = 18, height = 9, units = 'in', res = 300)
+    x=seq(1,length(timeseries),1)
+    plot(x,timeseries, type="l", lwd=1.5, col="red", 
+         ylim=c(min(lower, na.rm = T)-(min(lower, na.rm = T)/50), c(max(upper, na.rm = T)+(max(upper, na.rm = T)/50))))
[…]

### 2024-11-19 Synthesis_21_22_23/code/results_plots_synthesis.R

@@ -1,0 +1,235 @@
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# For plotting
+require(GGally)
+require(ggpubr)
+require(grid)
+require(gridExtra)
+
+# For images
+require(grDevices)
+
+# Step 1: Import metabolism results datasets -----------------------------------
+# 2021
+all_21 <- fread("../../project_21/results_metabolism/merged_results_complete_2021.txt")
+
+# 2022
+all_22 <- fread("../../project_22/results_metabolism/merged_results_complete_2022.txt")
+
+# 2023
+all_23 <- fread("../../project_23/results_metabolism/merged_results_complete_2023.txt")
+# In total, we have 425 days of estimated metabolism across all 3 years
+
+# Step 2: Create datasets for pond-wise means and standard errors of means by year
+means_21 <- all_21 %>%
+  group_by(Treatment, Pond) %>%
+  summarise(
+    mean_GPP = mean(GPP),
+    mean_R = mean(R),
+    mean_NEP = mean(NEP),
+    se_mean_GPP = sd(GPP)/sqrt(length(GPP)),
+    se_mean_R = sd(R)/sqrt(length(R)),
+    se_mean_NEP = sd(NEP)/sqrt(length(NEP)),
+    .groups = "drop"
+  )
+
+means_22 <- all_22 %>%
+  group_by(Treatment, Pond) %>%
+  summarise(
+    mean_GPP = mean(GPP),
+    mean_R = mean(R),
+    mean_NEP = mean(NEP),
+    se_mean_GPP = sd(GPP)/sqrt(length(GPP)),
+    se_mean_R = sd(R)/sqrt(length(R)),
+    se_mean_NEP = sd(NEP)/sqrt(length(NEP)),
+    .groups = "drop"
+  )
+
+means_23 <- all_23 %>%
+  group_by(Treatment, Pond) %>%
+  summarise(
+    mean_GPP = mean(GPP),
+    mean_R = mean(R),
+    mean_NEP = mean(NEP),
+    se_mean_GPP = sd(GPP)/sqrt(length(GPP)),
+    se_mean_R = sd(R)/sqrt(length(R)),
+    se_mean_NEP = sd(NEP)/sqrt(length(NEP)),
+    .groups = "drop"
+  )
+
+# Treatment as fa
+
[…]

### 2024-11-19 project_21/code/analysis_Chloro_mgL_2021.R

@@ -1,0 +1,281 @@
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+setwd("~/ZIVI_EAWAG/project_21")
+
+source("~/ZIVI_EAWAG/project_21/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Mixed model packages
+library(lme4)
+library(nlme)
+
+# Assisting packages
+library(car)
+library(pastecs)
+library(ggpubr)
+library(GGally)
+library(effects)
+library(arm)
+library(MuMIn)
+
+sonde_key = fread( "~/ZIVI_EAWAG/project_22/ponds_sonde_key.txt", header=T)
+# Treatments:
+# S: fish from single population (L26)
+# D: fish from 2 populations (double, L26+ERL33)
+# NF: no fish
+
+# For t-test:
+# overall pond-wise means
+dat = fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_overall_avg.txt")
+
+# For mixed model:
+# daily pond-wise means (want to account for daily fluctuations by using the daily
+# means of the individual ponds, simultaneously having enough datapoints to fit the model
+# -> need more datapoints than levels of the random effect Sonde later)
+dat2 = fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_daily_avg.txt")
+
+# Step 1: format dataset -------------------------------------------------------
+
+dat = dat[, c("Pond", "Treatment", "Sonde", "Chlorophyll_RFU")]
+dat2 = dat2[, c("Pond", "Treatment", "Sonde", "Chlorophyll_RFU")]
+
+# Summarize S (fish from single population) and D (fish from two populations) into F (Fish)
+dat$Fish <- recode(dat$Treatment, "c('S', 'D') = 'yes'; c('NF') = 'no'")
+dat2$Fish <- recode(dat2$Treatment, "c('S', 'D') = 'yes'; c('NF') = 'no'")
+
+# Convert characters to factors
+dat$Fish <- factor(dat$Fish)
+dat$Sonde <- factor(dat$Sonde)
+dat2$Fish <- factor(dat2$Fish)
+dat2$Sonde <- factor(dat2$Sonde)
+
+# Step 2: EDA ------------------------------------------------------------------
+
+# Step 2.1: Visualize research question
+# Graphically
+ggplot(dat, aes(Fish, Chlorophyll_RFU)) +
[…]

### 2024-11-19 project_21/code/analysis_metabolism_B1P4_2021.R

@@ -1,0 +1,302 @@
+################################################################################
+# This is a metabolism analysis of Pond B1P4 in 2021
+# Treatment B1P4: Control (no fish)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of B1P4. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of B1P4:
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
[…]

### 2024-11-19 project_21/code/analysis_metabolism_B2P2_2021.R

@@ -1,0 +1,304 @@
+################################################################################
+# This is a metabolism analysis of Pond B2P2 in 2021
+# Treatment B2P2: Fish (Sticklebacks)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of B2P2. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of B2P2:
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
[…]

### 2024-11-19 project_21/code/analysis_metabolism_B2P3_2021.R

@@ -1,0 +1,302 @@
+################################################################################
+# This is a metabolism analysis of Pond B2P3 in 2021
+# Treatment B2P3: Fish (Sticklebacks)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of B2P3. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of B2P3:
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
[…]

### 2024-11-19 project_21/code/analysis_metabolism_B2P4_2021.R

@@ -1,0 +1,302 @@
+################################################################################
+# This is a metabolism analysis of Pond B2P4 in 2021
+# Treatment B2P4: Control (no fish)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of B2P4. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of B3P0:
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
[…]

### 2024-11-19 project_21/code/analysis_metabolism_B3P0_2021.R

@@ -1,0 +1,301 @@
+################################################################################
+# This is a metabolism analysis of Pond B3P0 in 2021
+# Treatment B3P0 : Control (no fish)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of B3P0. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of B3P0:
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
[…]

### 2024-11-19 project_21/code/analysis_metabolism_B3P1_2021.R

@@ -1,0 +1,301 @@
+################################################################################
+# This is a metabolism analysis of Pond B3P1 in 2021
+# Treatment B3P1: Fish (Sticklebacks)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of B3P1. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of B3P1:
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
[…]

### 2024-11-19 project_21/code/analysis_metabolism_B3P2_2021.R

@@ -1,0 +1,301 @@
+################################################################################
+# This is a metabolism analysis of Pond B3P2 in 2021
+# Treatment B3P2 : Fish (Sticklebacks)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of B3P2 . The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of B3P2 :
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
[…]

### 2024-11-19 project_21/code/analysis_metabolism_B3P3_2021.R

@@ -1,0 +1,301 @@
+################################################################################
+# This is a metabolism analysis of Pond B3P3 in 2021
+# Treatment B3P3: Fish (Sticklebacks)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of B3P3. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of B3P3:
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
[…]

### 2024-11-19 project_21/code/analysis_metabolism_ERL122_2021.R

@@ -1,0 +1,303 @@
+################################################################################
+# This is a metabolism analysis of Pond ERL122 in 2021
+# Treatment ERL122: Control (no fish)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of ERL122. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of ERL122:
+# 2021-09-19 00:00:00 to 2021-09-24 00:00:00
+# There is a data-gap on 2021-09-18 of a few hours
+# I chose to estimate metabolism after this data-gap, 5 consecutive days
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
[…]

### 2024-11-19 project_21/code/analysis_metabolism_ERL152_2021.R

@@ -1,0 +1,300 @@
+################################################################################
+# This is a metabolism analysis of Pond ERL152 in 2021
+# Treatment ERL152: Control (no fish)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of ERL152. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of ERL152:
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
[…]

### 2024-11-19 project_21/code/analysis_metabolism_ERL85_2021.R

@@ -1,0 +1,301 @@
+################################################################################
+# This is a metabolism analysis of Pond ERL85 in 2021
+# Treatment ERL85: Control (no fish)
+#
+# This analysis is made in the context of the Stickleback-experiments by Blake's
+# group in Greenland 2021.
+#
+# Aim of this sript: model ecosystem metabolism of ERL85. The whole workflow is
+# described in the report "report_analysis_metabolism_B3P3_2022",
+# which serves as a blueprint for this analysis.
+#
+# Observation period used to estimate metabolism of B3P0:
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+#
+# Model used: Bayesian (see report "report_analysis_metabolism_B3P3_2022"),
+# which serves as a blueprint for this analysis.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS (Gibbs sampler) is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
[…]

### 2024-11-19 project_21/code/make_data_2021.R

@@ -1,0 +1,454 @@
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+require(GGally)
+require(grDevices)
+
+sonde_key = fread( "../data/sondes_key_2021.txt", header=T)
+
+# step 1: merge all raw data files into a single big one -----------------------
+
+path = "../data/raw_data_sondes/Raw_sonde_2021_preprocessed"
+filenames <- list.files(path=path, pattern=".txt")
+files<-data.table(NULL)
+
+system.time(for(i in filenames){
+  filepath <- file.path(path,paste(i,sep=""))
+  dummy1<-fread(filepath,
+                colClasses = "character" ,
+                sep = "\t",
+                header = FALSE,
+                fill=TRUE,
+                encoding ="UTF-8")
+  rownumb<-dummy1[V1 %like% "(MM/DD/YYYY)", which=TRUE]+1
+  colname<-dummy1[V1 %like% "(MM/DD/YYYY)"]
+  colname<-gsub(" ", "",(gsub("[[:punct:]]", "",c(lapply(colname,as.character)))))
+  colname<-unlist(strsplit(colname,"\t"))
+  dummy2<-dummy1[rownumb:.N]
+  setnames(dummy2,colname)
+  dummy2[,(colname[c(3,5:length(dummy2))]):=lapply(.SD, as.numeric),.SDcols=colname[c(3,5:length(dummy2))]]
+  dummy2$Pond<-sub("_Sept.*", "", i)
+  dummy2$Source_file<-i
+  files<-rbindlist(list(files, dummy2), fill=TRUE)
+})
+
+all <- files
+
+# remove last 3 columns (some variables only measured by few sondes)
+all <- all[,!c("Depthm", "Pressurepsia", "VerticalPositionm")]
+
+# replace "µ" with "" in colnames
+setnames(all, gsub("µ", "",  names(all)))
+
+# save intermediate stage 1 (FULL RAW DATA, NO REMOVAL)
+fwrite(all, "../data/data_sondes_IntermProcessingSteps/ponds_sonde_data_intermediate_1.txt", sep="\t")
+
+# step 2: add exp. design, phases and format time ------------------------------
+
+# format date & time
[…]

### 2024-11-19 project_21/code/make_data_2021_intercept_correction.R

@@ -1,0 +1,671 @@
+################################################################################
+# This is a script where the aim is to do an intercept-correction regarding the
+# Sondes-data of the Stickeback-experiments of Blakes Group in Greenland 2021.
+# The variable of interest is Chlorophyll ug/L measured by the Sondes, which will
+# be compared with the actual Chlorophyll content measured chemically at the same specific
+# point in time. All the other datapoints of this sonde will then be adjusted according to
+# this difference. For example, if the sondes measurement at a given time-point 
+# gives 12 ug/L and the chemical analysis gives 11 ug/L, 1 ug/L will be subtracted
+# from all the datapoints of this sonde.
+# The idea is that the Sondes in the different ponds are then adjusted for factory-differences
+# which makes them better comparable.
+# Unfortunately, the chemical measurements were made a few days prior to the
+# deployment sondes. Therefore, I will take the average
+# of the Chlorophyll measurements measured by the deployment sondes at the same day-time
+# as the chemical measurements to compare.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+
+rm(list= ls())
+
+library(lubridate)
+
+setwd("~/ZIVI_EAWAG/project_21")
+
+source("~/ZIVI_EAWAG/project_21/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# import the chlorophyll A dataset, containing the Chlorophyll mg/L measurements
+# chemically analyzed at a specific point in time
+# Danina told me that they took the water samples mostly right after the deployment,
+# so I added 10 minutes to the last deployment observation to determine the timepoint
+# of the water-sample
+chloro <- fread("~/ZIVI_EAWAG/project_21/data/chloro_a_2021.txt", sep = "\t")
+
+# Import the complete dataset
[…]

### 2024-11-19 project_21/code/make_sonde_profiles_2021.R

@@ -1,0 +1,239 @@
+################################################################################
+# This script is meant to import, cut, store, and plot all sonde profiles
+# from 2021 in Greenland.
+# Please note, that it is important that the .csv files are encoded
+# as UTF-8, otherwise the code will not work.
+# In excel, one can save a file as UTF-8 .csv.
+# I converted some of the files imported to UTF-8 beforehand.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+require(GGally)
+require(gridExtra)
+# For images
+require(grDevices)
+
+# Step 1: merge all raw data files into a single big one -----------------------
+# Please ensure that all files are UTF-8 encoded (you'll get an error message
+# that hints to that problem if you try run the following script)
+
+path = "../data/sondes_profiling_raw"
+filenames <- list.files(path=path, pattern=".csv")
+files<-data.table(NULL)
+
+system.time(for(i in filenames){
+  filepath <- file.path(path,paste(i,sep=""))
+  dummy1<-fread(filepath,
+                colClasses = "character" ,
+                sep = ";",
+                header = FALSE,
+                fill=TRUE,
+                encoding ="UTF-8",
+                quote = FALSE)
+
+  rownumb<-dummy1[V1 %like% "(MM/DD/YYYY)", which=TRUE]+1
+  colname<-dummy1[V1 %like% "(MM/DD/YYYY)"]
+  colname <- iconv(as.character(colname), from = "UTF-8", to = "UTF-8//IGNORE")
+  colname <- gsub("µ", "", colname)  # Remove mu character
+  colname <- gsub("°", "", colname)  # Remove degree symbol
+  colname<-gsub(" ", "",(gsub("[[:punct:]]", "",c(lapply(colname,as.character)))))
+  colname <- make.unique(colname)  # Ensure unique column names
+  colname<-unlist(strsplit(colname,"\t"))
[…]

### 2024-11-19 project_21/code/metadata_prep_2021.R

@@ -1,0 +1,37 @@
+################################################################################
+# This is the script to process raw data of wind and irradiation
+# in Narsarsuaq 2021
+# The data stem from the
+# QAS_L automated weather station a couple of kilometers away from Narsarsuaq
+# It's the closest weather station measuring this parameter, that I could find.
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# The data will be subsequently used to model lake metabolism
+# The data are hourly averages of shortwave irradiation and wind speed
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+require(data.table) # data wrangling
+require(dplyr) # data wrangling
+
+# Import dataset ---------------------------------------------------------------
+meta <- fread("../data/metadata_metabolism_analysis/QAS_L_hour.csv",
+             sep = ",")
+
+# reduce to wanted variables
+meta <- meta[,c("time","dsr_cor","wspd_u")]
+# downwelling shortwave radiation
+# wind speed upper boom
+# sensor height upper boom: 2.65 + 0.4 = ca 3.05m
+
+# rename variables
+setnames(meta, c("Date_time", "dsr_cor", "wspd_ms"))
+
+# choose appropriate range
+# 2021-09-17 00:00:00 to 2021-09-24 00:00:00
+meta <- meta[meta$Date_time > "2021-09-17 01:00:00" &
+               meta$Date_time < "2021-09-24 03:00:00",]
+
+# save
+fwrite(meta, "../data/metadata_metabolism_analysis/metadata_2021.txt", sep="\t")

### 2024-11-19 project_22/code/analysis_chloro_rfu_2022.R

@@ -1,0 +1,378 @@
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+setwd("~/ZIVI_EAWAG/project_22")
+
+source("~/ZIVI_EAWAG/project_22/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Mixed model packages
+library(lme4)
+library(nlme)
+
+# Assisting packages
+library(emmeans)
+library(car)
+library(pastecs)
+library(ggpubr)
+library(GGally)
+library(effects)
+library(arm)
+library(MuMIn)
+
+sonde_key = fread( "~/ZIVI_EAWAG/project_22/ponds_sonde_key.txt", header=T)
+# Treatments:
+# S: fish from single population (L26)
+# D: fish from 2 populations (double, L26+ERL33)
+# NF: no fish
+
+# daily pond-wise means (want to account for daily fluctuations by using the daily
+# means of the individual ponds, simultaneously having enough datapoints to fit the model
+# -> need more datapoints than levels of the random effect Sonde later)
+dat = fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_daily_avg.txt")
+
+# Step 1: format dataset -------------------------------------------------------
+
+dat = dat[, c("Pond", "Treatment", "Sonde", "Chlorophyll_RFU")]
+
+# Summarize S (fish from single population) and D (fish from two populations) into F (Fish)
+dat$Fish <- recode(dat$Treatment, "c('S', 'D') = 'yes'; c('NF') = 'no'")
+
+# Convert characters to factors
+dat$Fish <- factor(dat$Fish)
+dat$Sonde <- factor(dat$Sonde)
+
+# Step 2: EDA ------------------------------------------------------------------
+
+# Step 2.1: Visualize research question
+# Graphically
+ggplot(dat, aes(Fish, Chlorophyll_RFU)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(aes(col = Sonde), width = 0.25, alpha=1, size = 3) +
+  labs(y = "Chlorophyll RFU", title = "Pond-wise daily means Chloropyll RFU no Fish vs. Fish") +
+  theme_light()
+# Different sondes seem to have different intercepts, even though the treatment
+# is the same
+
+# Step 2.2: Independence of Chlorophyll_RFU-------------------------------------
+# Although Chlorophyll_RFU is strongly time-dependent, we sort of accounted
+# for this dependence by taking the overall or daily means of the individual ponds
+
[…]

### 2024-11-19 project_22/code/analysis_metabolism_B1P1_2022.R

@@ -1,0 +1,296 @@
+################################################################################
+# This is a metabolism analysis of pond B1P1 in 2022
+# For 2022, we chose to fit the maximum number of days for any given Pond (instead
+# of the maximum shared days among all ponds),
+# since we did not have access to the same amount of data compared to other years
+# Treatment B1P1: Fish (Sticklebacks)
+# Observation period used to estimate metabolism of B1P1:
+# 2022-06-23 00:00:00 to 2022-07-02 00:00:00
+# Model used
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2022
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all_uncut.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: ca. 2.87m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2022.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
[…]

### 2024-11-19 project_22/code/analysis_metabolism_B2P2_2022.R

@@ -1,0 +1,289 @@
+################################################################################
+# This is a metabolism analysis of pond B2P2
+# Treatment B2P2: Fish (Sticklebacks)
+# Observation period used to estimate metabolism of B2P2:
+# 2022-06-23 00:00:00 to 2022-07-02 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2022
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all_uncut.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2022.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B2P2")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
+# Isolate the desired period (described in the introduction)
[…]

### 2024-11-19 project_22/code/analysis_metabolism_B2P3_2022.R

@@ -1,0 +1,287 @@
+################################################################################
+# This is a metabolism analysis of pond B2P3
+# Treatment B2P3: Fish (Sticklebacks)
+# Observation period used to estimate metabolism of B2P3:
+# 2022-06-23 00:00:00 to 2022-07-03 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2022
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all_uncut.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: ca. 2.87m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2022.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B2P3")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_22/code/analysis_metabolism_B2P4_2022.R

@@ -1,0 +1,290 @@
+################################################################################
+# This is a metabolism analysis of pond B2P4
+# Treatment B2P4: no Fish
+# Observation period used to estimate metabolism of B2P4:
+# 2022-06-23 00:00:00 to 2022-07-03 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2022
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all_uncut.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: ca. 2.87m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2022.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B2P4")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_22/code/analysis_metabolism_B3P1_2022.R

@@ -1,0 +1,290 @@
+################################################################################
+# This is a metabolism analysis of pond B3P1
+# Treatment B3P1: Fish (Sticklebacks)
+# Observation period used to estimate metabolism of B3P1:
+# 2022-06-24 00:00:00 to 2022-07-02 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2022
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all_uncut.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: ca. 2.87m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2022.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B3P1")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_22/code/analysis_metabolism_B3P2_2022.R

@@ -1,0 +1,291 @@
+################################################################################
+# This is a metabolism analysis of pond B3P2
+# Treatment B3P2: Fish (Sticklebacks)
+# Observation period used to estimate metabolism of B3P2:
+# 2022-06-24 00:00:00 to 2022-07-03 00:00:00
+# After that, the Sonde 13 probably went out of battery
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2022
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all_uncut.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: ca. 2.87m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2022.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B3P2")
+
+# Rename
[…]

### 2024-11-19 project_22/code/analysis_metabolism_B3P3_2022.R

@@ -1,0 +1,363 @@
+################################################################################
+# This metabolism analysis of Pond B3P3 is meant to serve as a blueprint for future
+# anlyses regarding the ponds from the Greenland expeditions of EAWAG
+#
+# Aim of this sript: model ecosystem metabolism of B3P3. The whole workflow is
+# described in the corresponding report.
+#
+# Model used: Bayesian
+#
+# Observation period used to estimate metabolism of B3P3:
+# 2022-06-23 00:00:00 to 2022-07-03 00:00:00
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2022
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all_uncut.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: ca. 2.87m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2022.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
[…]

### 2024-11-19 project_22/code/analysis_metabolism_ERL122_2022.R

@@ -1,0 +1,292 @@
+################################################################################
+# This is a metabolism analysis of pond ERL122
+# Treatment ERL122: no Fish
+# Observation period used to estimate metabolism:
+# 2022-06-23 00:00:00 to 2022-06-29 00:00:00
+# Model used: Bayesian
+# The pond has been named B3P4 in the raw data.
+# ERL122 is the correct name and will be used for subsequent analyses
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2022
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all_uncut.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: ca. 2.87m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2022.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "ERL122")
+
+# Rename
[…]

### 2024-11-19 project_22/code/analysis_metabolism_ERL85_2022.R

@@ -1,0 +1,291 @@
+################################################################################
+# This is a metabolism analysis of pond ERL85
+# Treatment ERL85: no Fish
+# Observation period used to estimate metabolism of ERL85:
+# 2022-06-23 00:00:00 to 2022-07-03 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2022
+# Measurement Interval: 2 minutes
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all_uncut.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: ca. 2.87m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2022.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "ERL85")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_22/code/analysis_sliding_windows2022.R

@@ -1,0 +1,50 @@
+# startup --------------------------------------------------------------
+
+rm(list = ls())
+
+# replace for your directory
+setwd("~/ZIVI_EAWAG/project_22/code")
+
+source("~/ZIVI_EAWAG/project_22/Moritz_Lührig_paper_stuff/methods_packages.R")
+
+cols = c("Chlorophyll_RFU", "BGAPC_RFU", "ODO_sat", "fDOM_RFU")
+sonde_key = fread( "~/ZIVI_EAWAG/project_22/ponds_sonde_key.txt", header=T)
+
+# sliding windows --------------------------------------------------
+
+tenmin<-fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_ten_min_avg.txt")
+
+data = tenmin[order(Pond, Time_seq, Hour, Ten_min), ]
+
+# What window size should I choose here?
+winsize = 2 # 2 hours
+
+mean.df = data[, lapply(.SD, rollapplyr, width=winsize, fill=NA, FUN=mean, na.rm=T), 
+               by=c("Pond", "Replicate","Treatment"), .SDcols = cols]
+mean.df$Time_seq = data$Time_seq
+mean.df$Hour = data$Hour
+mean.df$Ten_min = data$Ten_min
+mean.df[,(cols):=lapply(.SD, round, 2), .SDcols=cols]
+mean.df$Variable = "MEAN"
+fwrite(mean.df, "~/ZIVI_EAWAG/project_22/data/sliding_ten_min_mean_2h.txt")
+
+
+cv.df = data[, lapply(.SD, rollapplyr, width=winsize, fill=NA, FUN=CV), 
+             by=c("Pond", "Replicate","Treatment"), .SDcols = cols]
+cv.df$Time_seq = data$Time_seq
+cv.df$Hour = data$Hour
+cv.df$Ten_min = data$Ten_min
+cv.df[,(cols):=lapply(.SD, round, 2), .SDcols=cols]
+cv.df$Variable = "CV"
+fwrite(cv.df, "~/ZIVI_EAWAG/project_22/data/sliding_ten_min_cv_2h.txt")
+
+ac.df = data[, lapply(.SD, rollapplyr, width=winsize, fill=NA, FUN=AC), 
+             by=c("Pond", "Replicate","Treatment"), .SDcols = cols]
+ac.df$Time_seq = data$Time_seq
[…]

### 2024-11-19 project_22/code/make_figure_metabolism_2022.R

@@ -1,0 +1,254 @@
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# For plotting
+require(GGally)
+require(ggpubr)
+require(grid)
+
+# For images
+require(grDevices)
+
+# Import the metabolism result datasets
+
+# Treatment: Fish
+B3P3 <- fread("../results_metabolism/B3P3_bayesian_2022.txt")
+B1P1 <- fread("../results_metabolism/B1P1_bayesian_2022.txt")
+B2P2 <- fread("../results_metabolism/B2P2_bayesian_2022.txt")
+B2P3 <- fread("../results_metabolism/B2P3_bayesian_2022.txt")
+B3P1 <- fread("../results_metabolism/B3P1_bayesian_2022.txt")
+B3P2 <- fread("../results_metabolism/B3P2_bayesian_2022.txt")
+
+# Treatment: no Fish
+B2P4 <- fread("../results_metabolism/B2P4_bayesian_2022.txt")
+ERL122 <- fread("../results_metabolism/ERL122_bayesian_2022.txt")
+ERL85 <- fread("../results_metabolism/ERL85_bayesian_2022.txt")
+
+# Create a merged results dataset
+# Fish
+B3P3$Treatment <- "Fish"
+B3P3$Pond <- "B3P3"
+
+B1P1$Treatment <- "Fish"
+B1P1$Pond <- "B1P1"
+
+B2P2$Treatment <- "Fish"
+B2P2$Pond <- "B2P2"
+
+B2P3$Treatment <- "Fish"
+B2P3$Pond <- "B2P3"
+
+B3P1$Treatment <- "Fish"
+B3P1$Pond <- "B3P1"
+
+B3P2$Treatment <- "Fish"
+B3P2$Pond <- "B3P2"
+
+# No Fish
+B2P4$Treatment <- "no Fish"
+B2P4$Pond <- "B2P4"
+
+ERL122$Treatment <- "no Fish"
+ERL122$Pond <- "ERL122"
+
+ERL85$Treatment <- "no Fish"
+ERL85$Pond <- "ERL85"
+
+# Merge
+all <- rbind(B1P1, B2P2, B3P3, B2P3, B3P1, B3P2, B2P4, ERL122, ERL85)
+
+# Save
+fwrite(all, "../results_metabolism/merged_results_complete_2022.txt", sep = "\t")
+
+# Plot: GPP
[…]

### 2024-11-19 project_22/code/make_sonde_profiles_2022.R

@@ -1,0 +1,226 @@
+################################################################################
+# This script is meant to import, cut, store, and plot all sonde profiles
+# from 2022 in Greenland.
+# Please note, that it is important that the .csv files are encoded
+# as UTF-8, otherwise the code will not work.
+# In excel, one can save a file as UTF-8 .csv.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+require(GGally)
+require(gridExtra)
+# For images
+require(grDevices)
+
+# Step 1: merge all raw data files into a single big one -----------------------
+# Please ensure that all files are UTF-8 encoded (you'll get an error message
+# that hints to that problem if you try run the following script)
+
+path = "../data/sondes_profiling_raw"
+filenames <- list.files(path=path, pattern=".csv")
+files<-data.table(NULL)
+
+system.time(for(i in filenames){
+  filepath <- file.path(path,paste(i,sep=""))
+  dummy1<-fread(filepath,
+                colClasses = "character" ,
+                sep = ";",
+                header = FALSE,
+                fill=TRUE,
+                encoding ="UTF-8",
+                quote = FALSE)
+  
+  rownumb<-dummy1[V1 %like% "(MM/DD/YYYY)", which=TRUE]+1
+  colname<-dummy1[V1 %like% "(MM/DD/YYYY)"]
+  colname <- iconv(as.character(colname), from = "UTF-8", to = "UTF-8//IGNORE")
+  colname <- gsub("µ", "", colname)  # Remove mu character
+  colname <- gsub("°", "", colname)  # Remove degree symbol
+  colname<-gsub(" ", "",(gsub("[[:punct:]]", "",c(lapply(colname,as.character)))))
+  colname <- make.unique(colname)  # Ensure unique column names
+  colname<-unlist(strsplit(colname,"\t"))
+  dummy2<-dummy1[rownumb:.N]
[…]

### 2024-11-19 project_23/code/analysis_metabolism_B1P1_2023.R

@@ -1,0 +1,306 @@
+################################################################################
+# This is a metabolism analysis of pond B1P1 in 2023
+# Treatment B1P1: Fish (Sticklebacks)
+# Observation period used to estimate metabolism of B1P1:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B1P1")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/analysis_metabolism_B2P2_2023.R

@@ -1,0 +1,291 @@
+################################################################################
+# This is a metabolism analysis of pond B2P2 in 2023
+# Treatment B2P2: Fish (Sticklebacks), 1 source
+# Observation period used to estimate metabolism:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B2P2")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/analysis_metabolism_B2P3_2023.R

@@ -1,0 +1,292 @@
+################################################################################
+# This is a metabolism analysis of pond B2P3 in 2023
+# Treatment B2P3: Fish (Sticklebacks), 2 sources
+# Observation period used to estimate metabolism of B2P3:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B2P3")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/analysis_metabolism_B2P4_2023.R

@@ -1,0 +1,291 @@
+################################################################################
+# This is a metabolism analysis of pond B2P4 in 2023
+# Treatment B2P4: no Fish
+# Observation period used to estimate metabolism:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B2P4")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/analysis_metabolism_B3P0_2023.R

@@ -1,0 +1,289 @@
+################################################################################
+# This is a metabolism analysis of pond B3P0 in 2023
+# Treatment B3P0: no Fish
+# Observation period used to estimate metabolism:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B3P0")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/analysis_metabolism_B3P1_2023.R

@@ -1,0 +1,290 @@
+################################################################################
+# This is a metabolism analysis of pond B3P1 in 2023
+# Treatment B3P1: Fish (Sticklebacks), 2 sources
+# Observation period used to estimate metabolism:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B3P1")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/analysis_metabolism_B3P2_2023.R

@@ -1,0 +1,289 @@
+################################################################################
+# This is a metabolism analysis of pond B3P2 in 2023
+# Treatment B3P2: Fish (Sticklebacks), 2 sources
+# Observation period used to estimate metabolism:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B3P2")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/analysis_metabolism_B3P3_2023.R

@@ -1,0 +1,298 @@
+################################################################################
+# This is a metabolism analysis of pond B3P3 in 2023
+# Treatment B3P3: Fish (Sticklebacks), 1 source
+# Observation period used to estimate metabolism:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B3P3")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/analysis_metabolism_ERL122_2023.R

@@ -1,0 +1,296 @@
+################################################################################
+# This is a metabolism analysis of pond ERL122 in 2023
+# Treatment ERL152: no Fish
+# Observation period used to estimate metabolism:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "ERL122")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/analysis_metabolism_ERL85_2023.R

@@ -1,0 +1,283 @@
+################################################################################
+# This is a metabolism analysis of pond ERL85 in 2023
+# Treatment ERL85: no Fish
+# Observation period used to estimate metabolism:
+# 2023-06-23 00:00:00 to 2023-07-17 00:00:00
+# Model used: Bayesian
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements
+# Measurement Interval: 5 minutes mostly
+all <- fread("../data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../data/metadata_metabolism_analysis/metadata_2023.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "ERL85")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
[…]

### 2024-11-19 project_23/code/make_data_2023.R

@@ -1,0 +1,417 @@
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+require(GGally)
+
+sonde_key = fread( "../data/key_2023.txt", header=T)
+
+# step 1: merge all raw data files into a single big one -----------------------
+
+path = "../data/raw_data_sondes_preprocessed"
+filenames <- list.files(path=path, pattern=".txt")
+files<-data.table(NULL)
+
+system.time(for(i in filenames){
+  filepath <- file.path(path,paste(i,sep=""))
+  dummy1<-fread(filepath,
+                colClasses = "character" ,
+                sep = "\t",
+                header = FALSE,
+                fill=TRUE,
+                encoding ="UTF-8")
+  rownumb<-dummy1[V1 %like% "(MM/DD/YYYY)", which=TRUE]+1
+  colname<-dummy1[V1 %like% "(MM/DD/YYYY)"]
+  colname<-gsub(" ", "",(gsub("[[:punct:]]", "",c(lapply(colname,as.character)))))
+  colname<-unlist(strsplit(colname,"\t"))
+  dummy2<-dummy1[rownumb:.N]
+  setnames(dummy2,colname)
+  dummy2[,(colname[c(3,5:length(dummy2))]):=lapply(.SD, as.numeric),.SDcols=colname[c(3,5:length(dummy2))]]
+  dummy2$Pond<-sub("_Sonde.*", "", i)
+  dummy2$Source_file<-i
+  files<-rbindlist(list(files, dummy2), fill=TRUE)
+})
+
+all <- files
+
+# remove last 3 columns (some variables only measured by few sondes)
+all <- all[,!c("Depthm", "Pressurepsia", "VerticalPositionm")]
+
+# step 2: add exp. design, phases and format time ------------------------------
+
+# format date & time
+all$TimeHHmmss<-substr(all$TimeHHmmss,1,5) #gsub("\\D+", "", cleaning$TimeHHMMSS)
+all$DateMMDDYYYY<-mdy(all$DateMMDDYYYY)
+all$Date_time<-ymd_hm(paste(all$DateMMDDYYYY, all$TimeHHmmss))
+setnames(all,1:2,c("Date","Time"))
+all$Date_time <- as.POSIXct(all$Date_time, tz = "UTC")
+
+# # Check start and end times for equal cutting
+# all[,c(min(Date_time), max(Date_time)), by = Pond]
+
[…]

### 2024-11-19 project_23/code/make_figures_metabolism_2023.R

@@ -1,0 +1,301 @@
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# For plotting
+require(GGally)
+require(ggpubr)
+require(grid)
+
+# For images
+require(grDevices)
+
+# Import the metabolism result datasets
+
+# Treatment: Fish
+B3P3 <- fread("../results_metabolism/B3P3_bayesian_2023.txt")
+B1P1 <- fread("../results_metabolism/B1P1_bayesian_2023.txt")
+B2P2 <- fread("../results_metabolism/B2P2_bayesian_2023.txt")
+B2P3 <- fread("../results_metabolism/B2P3_bayesian_2023.txt")
+B3P1 <- fread("../results_metabolism/B3P1_bayesian_2023.txt")
+B3P2 <- fread("../results_metabolism/B3P2_bayesian_2023.txt")
+
+# Treatment: no Fish
+B2P4 <- fread("../results_metabolism/B2P4_bayesian_2023.txt")
+B1P4 <- fread("../results_metabolism/B1P4_bayesian_2023.txt")
+ERL85 <- fread("../results_metabolism/ERL85_bayesian_2023.txt")
+# From eyeballing the results, it appears that we had trouble
+# estimating metabolism in pond ERL85 (e.g. positive Respiration on quite a
+# lot of days)
+B3P0 <- fread("../results_metabolism/B3P0_bayesian_2023.txt")
+ERL122 <- fread("../results_metabolism/ERL122_bayesian_2023.txt")
+# We did not havetemperature measurements for ERL152, hence the analysis
+# was not possible for this pond
+
+# Create a merged results dataset
+# Fish
+B3P3$Treatment <- "Fish"
+B3P3$Pond <- "B3P3"
+
+B1P1$Treatment <- "Fish"
+B1P1$Pond <- "B1P1"
+
+B2P2$Treatment <- "Fish"
+B2P2$Pond <- "B2P2"
+
+B2P3$Treatment <- "Fish"
+B2P3$Pond <- "B2P3"
+
+B3P1$Treatment <- "Fish"
+B3P1$Pond <- "B3P1"
+
+B3P2$Treatment <- "Fish"
+B3P2$Pond <- "B3P2"
+
+# No Fish
[…]

### 2024-11-19 project_23/code/make_sonde_profiles_2023.R

@@ -1,0 +1,221 @@
+################################################################################
+# This script is meant to import, cut, store, and plot all sonde profiles
+# from 2023 in Greenland.
+# Please note, that it is important that the .csv files are encoded
+# as UTF-8, otherwise the code will not work.
+# In excel, one can save a file as UTF-8 .csv.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+require(GGally)
+require(gridExtra)
+# For images
+require(grDevices)
+
+# Step 1: merge all raw data files into a single big one -----------------------
+# Please ensure that all files are UTF-8 encoded (you'll get an error message
+# that hints to that problem if you try run the following script)
+
+path = "../data/sondes_profiling_raw"
+filenames <- list.files(path=path, pattern=".csv")
+files<-data.table(NULL)
+
+system.time(for(i in filenames){
+  filepath <- file.path(path,paste(i,sep=""))
+  dummy1<-fread(filepath,
+                colClasses = "character" ,
+                sep = ";",
+                header = FALSE,
+                fill=TRUE,
+                encoding ="UTF-8",
+                quote = FALSE)
+  
+  rownumb<-dummy1[V1 %like% "(MM/DD/YYYY)", which=TRUE]+1
+  colname<-dummy1[V1 %like% "(MM/DD/YYYY)"]
+  colname <- iconv(as.character(colname), from = "UTF-8", to = "UTF-8//IGNORE")
+  colname <- gsub("µ", "", colname)  # Remove mu character
+  colname <- gsub("°", "", colname)  # Remove degree symbol
+  colname<-gsub(" ", "",(gsub("[[:punct:]]", "",c(lapply(colname,as.character)))))
+  colname <- make.unique(colname)  # Ensure unique column names
+  colname<-unlist(strsplit(colname,"\t"))
+  dummy2<-dummy1[rownumb:.N]
+  setnames(dummy2,colname)
[…]

### 2024-11-19 project_23/code/metadata_prep_2023.R

@@ -1,0 +1,48 @@
+################################################################################
+# This is the script to process raw data of wind and irradiation
+# in Narsarsuaq 2023
+# The data stem from the
+# QAS_L automated weather station a couple of kilometers away from Narsarsuaq
+# It's the closest weather station measuring this parameter, that I could find.
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# The data will be subsequently used to model lake metabolism
+# The data are hourly averages of shortwave irradiation and wind speed
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+require(data.table) # data wrangling
+require(dplyr) # data wrangling
+
+# Import dataset ---------------------------------------------------------------
+meta <- fread("../../project_21/data/metadata_metabolism_analysis/QAS_L_hour.csv",
+              sep = ",")
+
+# reduce to wanted variables
+meta <- meta[,c("time","dsr_cor","wspd_u", "z_boom_u")]
+# downwelling shortwave radiation
+# wind speed upper boom
+# sensor height upper boom: 2.47 + 0.4 = ca 2.87m
+
+# rename variables
+setnames(meta, c("Date_time", "dsr_cor", "wspd_ms", "boom_height"))
+
+# make sure Date_time is UTC timezone
+meta$Date_time <- as.POSIXct(meta$Date_time, tz = "UTC")
+
+# # Determine sensor height (boom_height + 0.4m)
+# meta[meta$Date_time>="2023-06-23 00:00:00" &
+#        meta$Date_time<="2023-07-17 04:00:00",meta$boom_height[1]] + 0.4
+# # 3.05m
+
+# choose appropriate range
+# 2022-06-24 00:00:00 to 2022-07-05 00:00:00
+meta <- meta[meta$Date_time>="2023-06-23 00:00:00" &
+               meta$Date_time<="2023-07-17 04:00:00",]
+
+# Select columns to keep
+meta <- meta[,c("Date_time", "dsr_cor", "wspd_ms")]
+
+# save
+fwrite(meta, "../data/metadata_metabolism_analysis/metadata_2023.txt", sep="\t")

### 2024-11-19 project_24/code/make_sonde_profiles_2024.R

@@ -1,0 +1,217 @@
+################################################################################
+# This script is meant to import, cut, store, and plot all sonde profiles
+# from 2024 in Greenland.
+# The result is a single dataset of profiles for all ponds in 2024.
+# Please note, that it is important that the .csv files are encoded
+# as UTF-8, otherwise the code will not work.
+# In excel, one can save a file as UTF-8 .csv.
+################################################################################
+
+# Step 0: set up R-script ------------------------------------------------------
+rm(list= ls())
+
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+require(GGally)
+require(gridExtra)
+# For images
+require(grDevices)
+
+# Step 1: merge all raw data files into a single big one -----------------------
+# Please ensure that all files are UTF-8 encoded (you'll get an error message
+# that hints to that problem if you try run the following script)
+
+path = "../data/sondes_profiling_raw"
+filenames <- list.files(path=path, pattern=".csv")
+files<-data.table(NULL)
+
+system.time(for(i in filenames){
+  filepath <- file.path(path,paste(i,sep=""))
+  dummy1<-fread(filepath,
+                colClasses = "character" ,
+                sep = ";",
+                header = FALSE,
+                fill=TRUE,
+                encoding ="UTF-8",
+                quote = FALSE)
+  
+  rownumb<-dummy1[V1 %like% "(MM/DD/YYYY)", which=TRUE]+1
+  colname<-dummy1[V1 %like% "(MM/DD/YYYY)"]
+  colname <- iconv(as.character(colname), from = "UTF-8", to = "UTF-8//IGNORE")
+  colname <- gsub("µ", "", colname)  # Remove mu character
+  colname <- gsub("°", "", colname)  # Remove degree symbol
+  colname<-gsub(" ", "",(gsub("[[:punct:]]", "",c(lapply(colname,as.character)))))
+  colname <- make.unique(colname)  # Ensure unique column names
+  colname<-unlist(strsplit(colname,"\t"))
[…]

### 2024-11-19 LakeMetabolism_project/project_22/reports/project_report1_2022.Rmd
First push

---
title: "Report data-processing sondes-project 2022"
author: "Emanuel Mauch"
date: "2023-07-07"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This is a report of the data-processing steps of the Greenland sonde data of 2022. I adapted Moritz' code
from his paper (https://doi.org/10.1002/ecy.3371). I have cleaned all the raw datasets, stored them as .txt files (folder "Raw_sonde_2022_3"), merged them with RStudio, processed the merged dataset and plotted some figures of the absolute values. The code was adapted from Moritz' file "make_data.R", using his "method_packages.R". All the files I've used to make this report are in the "project_22" folder that I have uploaded.

# Steps done so far
## Step 0: Clean raw datafiles in Excel, store them as .txt files
I cleaned all the raw .csv files with Excel (e.g. reassembling split files, fixing date bugs which lead to wrong .txt file conversions etc.). They can be found in the folder "Raw_sonde_2022_3".

## Step 1: set up R-script
```{r}
rm(list= ls())

setwd("~/ZIVI_EAWAG/project_22")

source("~/ZIVI_EAWAG/project_22/Moritz_Luehrig_paper_stuff/methods_packages.R")
library(GGally)

sonde_key = fread( "~/ZIVI_EAWAG/project_22/ponds_sonde_key.txt", header=T)
print(head(sonde_key))
```
## Step 2: merge all raw data files into a single big one
```{r, warning = F}
path = "~/ZIVI_EAWAG/project_22/Raw_sonde_2022_3"
filenames <- list.files(path=path, pattern=".txt")
files<-data.table(NULL)

system.time(for(i in filenames){
  filepath <- file.path(path,paste(i,sep=""))
  dummy1<-fread(filepath,
                colClasses = "character" ,
                sep = "\t",
                header = FALSE,
                fill=TRUE,
                encoding ="UTF-8")
  rownumb<-dummy1[V1 %like% "(MM/DD/YYYY)", which=TRUE]+1
  colname<-dummy1[V1 %like% "(MM/DD/YYYY)"]
  colname<-gsub(" ", "",(gsub("[[:punct:]]", "",c(lapply(colname,as.character)))))
  colname<-unlist(strsplit(colname,"\t"))
  dummy2<-dummy1[rownumb:.N]
  setnames(dummy2,colname)
  dummy2[,(colname[c(3,5:length(dummy2))]):=lapply(.SD, as.numeric),.SDcols=colname[c(3,5:length(dummy2))]]
  dummy2$Sonde<-substr(i, 1,7)
  dummy2$Source_file<-i
  files<-rbindlist(list(files, dummy2), fill=TRUE)
})

all <- files

# save intermediate stage 1 (FULL RAW DATA, NO REMOVAL)
fwrite(all, "~/ZIVI_EAWAG/project_22/intermediate_processing_steps/ponds_sonde_data_intermediate_1.txt", sep="\t")
print(head(all,3))
```

## Step 3: add exp. design, phases and format time
```{r}
all <- fread("~/ZIVI_EAWAG/project_22/intermediate_processing_steps/ponds_sonde_data_intermediate_1.txt", sep="\t")

# format date & time
all$TimeHHMMSS<-substr(all$TimeHHMMSS,1,5) #gsub("\\D+", "", cleaning$TimeHHMMSS)
all$DateMMDDYYYY<-mdy(all$DateMMDDYYYY)
all$Date_time<-ymd_hm(paste(all$DateMMDDYYYY, all$TimeHHMMSS))
setnames(all,1:2,c("Date","Time"))

# add fractions of day since start
# all = all[order(Date_time, Sonde)]
all[,Time_seq:=round(((as.numeric(Date_time))-
                        (as.numeric(Date_time)[1]))/86400,7)]

# merge with key
all<-merge(all,sonde_key, by = "Sonde")

# reorder and revalue
setorderv(all, c("Pond", "Sonde", "Date_time"), c(1, 1, 1))

# select columns to keep
all<-all[,c("Pond","Sonde", "Treatment", "Time_seq", "Date_time",
            "ChlorophyllRFU", "ConduScm" , "BGAPCRFU", "ODOmgL", "pH", "fDOMRFU", "SpConduScm", "TempC")]

# rename
setnames(all, c("Pond", "Sonde", "Treatment", "Time_seq", "Date_time",
                "Chlorophyll_RFU", "Cond_uScm", "BGAPC_RFU", "ODO_mgL", "pH", "fDOM_RFU", "SpCond_uScm", "Temp_C"))

# debug: rm duplicate value
all = unique(all, by=c("Pond", "Time_seq"))

fwrite(all, "~/ZIVI_EAWAG/project_22/intermediate_processing_steps/ponds_sonde_data_intermediate_2.txt", sep="\t")
print(head(all,3))
```

# Step 4.1: remove outliers
The outlier plots are in the folder "outliers".

```{r, eval=FALSE}
all <- fread("~/ZIVI_EAWAG/project_22/intermediate_processing_steps/ponds_sonde_data_intermediate_2.txt", sep="\t")

save_path = "outliers/"

for(i in  c("Chlorophyll_RFU", "BGAPC_RFU", "ODO_mgL")){
  all[,  (i) := lapply(.SD[,..i],
                       outlier_removal,
                       window=48,
                       threshold=10,
                       plot=T,
                       return="removed",
                       save=T,
                       path=save_path,
                       name=paste0(i,"_",Pond)),
      by = c("Pond")]
}

for(i in c("fDOM_RFU")){
  all[,  (i) := lapply(.SD[,..i],
                       outlier_removal,
                       window=96,
                       threshold=10,
                       plot=F,
                       return="removed",
                       save=T,
                       path=save_path,
                       name=paste0(i,"_",Pond)),
      by = c("Pond")]
}

for(i in c("Temp_C", "SpCond_uScm", "Cond_uScm")){
  all[,  (i) := lapply(.SD[,..i],
                       outlier_removal,
                       window=96,
                       threshold=20,
                       plot=F,
                       return="removed",
                       save=T,
                       path=save_path,
                       name=paste0(i,"_",Pond)),
      by = c("Pond")]
}

# cut-off "loose ends" on both sides -> all same start and same end of measurements
all <- subset(all, Date_time>"2022-06-23 22:00:00" & Date_time<"2022-06-29 05:00:00")

# add fractions of day since start
# all = all[order(Date_time, Sonde)]
all[,Time_seq:=round(((as.numeric(Date_time))-
                        (as.numeric(Date_time)[1]))/86400,7)]

# ommit date-time (just needed for cutting the dates)
all<-all[,!c("Date_time")]

# save
fwrite(all, "~/ZIVI_EAWAG/project_22/intermediate_processing_steps/ponds_sonde_data_intermediate_3.1.txt", sep="\t")
```

## Step 4.2: remove anomalies
We inspected the data for anomalies and remove them here - for details see 
Russo, S., M. Lührig, W. Hao, B. Matthews, and K. Villez. 2020. 
Active learning for anomaly detection in environmental data. 
Environmental Modelling & Software 134:104869.

I didn't do this step, since I would need some time to refresh my python skills, 
but if you think it is worth, I will manage.

## Step 5: add light and precipitation data
I do not have this data available.

## Step 6: intercept correction
This uses the results form a cross correlation survey to adjust the 
sondes for "off factory differences, i.e. remove any intercept variation
among the data.

I do not have the sonds correlation factors.

## Step 7: save
```{r, eval=FALSE}
## order and remove rownames
all = all[order(Pond, Time_seq), ]

rownames(all)<-NULL

fwrite(all, "~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_all.txt")
```

```{r}
all<-fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_all.txt")
print(head(all,3))
```

## Step 8: check completeness
```{r}
all <- fread("~/ZIVI_EAWAG/project_22/intermediate_processing_steps/ponds_sonde_data_intermediate_3.1.txt", sep="\t")
all$Date_time <- as.POSIXct((all$Time_seq*86400), origin="2022-06-23 20:00:00", tz="UTC")

all$Date <-date(all$Date_time)

# N per date
all[, N := uniqueN(Date), by = Sonde]
complete <- setDT(data.frame(unclass(table(all$Date, all$Sonde))), keep.rownames=T)
colnames(complete)[1]<-"Date"
fwrite(complete, "~/ZIVI_EAWAG/project_22/data/sonde_data_completeness.txt", sep="\t")
print(complete)
```

## Step 9: calculate daily averages
```{r}
all<-fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_all.txt")
summary(all)
all[,Time_seq:=as.integer(Time_seq)]

parameters = c("Chlorophyll_RFU", "Cond_uScm", "BGAPC_RFU", "ODO_mgL", "pH",
               "fDOM_RFU", "SpCond_uScm", "Temp_C")
groups = c("Time_seq", "Pond", "Sonde", "Treatment")

all.summ = all[,lapply(.SD, m_r, 2), by=groups, .SDcols = parameters]

fwrite(all.summ, "~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_daily_avg.txt", sep=",")

table(all.summ$Pond, all.summ$Treatment)
print(head(all.summ,3))
```

## Step 10: hourly averages
```{r}
all<-fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_all.txt")

parameters = c("Chlorophyll_RFU", "Cond_uScm", "BGAPC_RFU", "ODO_mgL", "pH",
               "fDOM_RFU", "SpCond_uScm", "Temp_C")

all$Date_time <- as.POSIXct((all$Time_seq*86400), origin="2022-06-23 20:00:00", tz="UTC")

all$Time_seq = as.integer(all$Time_seq)
all$Hour <- as.numeric(substr(as.character(all$Date_time),12,13))

groups = c("Time_seq", "Hour","Pond", "Treatment")

all.summ = all[,lapply(.SD, m_r, 2), by=groups, .SDcols = parameters]

fwrite(all.summ, "~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_hourly_avg.txt", sep=",")
print(head(all.summ,3))
```

## Step 11: 10-minute averages
I thought that maybe the hour interval is too large for our time series,
so maybe a 10-minute interval could be more appropriate (or just plot¨
the absolute values).

```{r}
all<-fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_all.txt")

parameters = c("Chlorophyll_RFU", "Cond_uScm", "BGAPC_RFU", "ODO_mgL", "pH",
               "fDOM_RFU", "SpCond_uScm", "Temp_C")

all$Date_time <- as.POSIXct((all$Time_seq*86400), origin="2022-06-23 20:00:00", tz="UTC")

all$Time_seq = as.integer(all$Time_seq)
all$Hour <- as.numeric(substr(as.character(all$Date_time),12,13))
all$Ten_min <- as.numeric(substr(as.character(all$Date_time),15,15))

groups = c("Time_seq", "Hour", "Ten_min", "Pond", "Treatment")

all.summ = all[,lapply(.SD, m_r, 2), by=groups, .SDcols = parameters]

fwrite(all.summ, "~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_ten_min_avg.txt", sep=",")
print(head(all.summ,3))
```

## Step 12: calculate overall averages of individual ponds
```{r}
all<-fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_all.txt")

parameters = c("Chlorophyll_RFU", "Cond_uScm", "BGAPC_RFU", "ODO_mgL", "pH",
               "fDOM_RFU", "SpCond_uScm", "Temp_C")
groups = c("Pond","Treatment", "Sonde")

all.summ = all[,lapply(.SD, m_r, 2), by=groups, .SDcols = parameters]

fwrite(all.summ, "~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_overall_avg.txt", sep=",")

table(all.summ$Pond, all.summ$Treatment)
```

## Step 13: control plots
```{r}
all<-fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_all.txt")

all$Date_time <- as.POSIXct((all$Time_seq*86400), origin="2022-06-23 22:00:00", tz="UTC")

table(all$Pond, all$Treatment)
```

### Chlorophyll RFU
```{r, echo=FALSE, fig.height=8, fig.width = 9, warning = FALSE}
# Chloropyll_RFU
p1 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p2 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p1, p2, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))

# Chloropyll_RFU
```

### BGAPC RFU
```{r, echo=FALSE, fig.height=8, fig.width = 9, warning = FALSE}
# BGAPC RFU
p5 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p6 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p5, p6, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))
```

### ODO mg/L
```{r, echo=FALSE, fig.height=8, fig.width = 9, warning = FALSE}
# ODO mg/L
p3 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p4 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p3, p4, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))
```

### Cond uS/cm
```{r, echo=FALSE, fig.height=8, fig.width = 9, warning = FALSE}
# Cond uS/cm
p7 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p8 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p7, p8, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))
```

### Speficic Cond uS/cm
```{r, echo=FALSE, fig.height=8, fig.width = 9, warning = FALSE}
p9 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p10 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p9, p10, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))
```

### fDOM RFU
```{r, echo=FALSE, fig.height=8, fig.width = 9, warning = FALSE}
# fDOM RFU
p11 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p12 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p11, p12, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))
```

# 14: Appendix
## Version and packages used to generate this report:
```{r, echo=FALSE}
cat(paste(Sys.time(), Sys.timezone(), "\n"))
sessionInfo()
```
## Code used to generate control plots:
```{r, eval=FALSE}
# Chloropyll_RFU
p1 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p2 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=Chlorophyll_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p1, p2, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))

# ODO mg/L
p3 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p4 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=ODO_mgL, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p3, p4, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))

# BGAPC RFU
p5 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p6 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=BGAPC_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p5, p6, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))

# Cond uS/cm
p7 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p8 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=Cond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p7, p8, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))

# Speficic Cond uS/cm
p9 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p10 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=SpCond_uScm, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p9, p10, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))

# fDOM RFU
p11 = ggplot(subset(all, Pond=="B1P1")) + theme_light() +
  geom_line(aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P2"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P3"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B2P3"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P1"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P2"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B1P1', 'B2P2', 'B3P3', "B2P3", "B3P1", "B3P2"),
                     values=c('B1P1'="gray17", 'B2P2'='dodgerblue3', 'B3P3'='magenta4',
                              "B2P3"="olivedrab4", "B3P1"="chocolate", "B3P2"="midnightblue")) +
  ggtitle("Fish")

p12 = ggplot(subset(all, Pond=="B2P4")) + theme_light() +
  geom_line(aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P0"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="B3P4"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL152"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  geom_line(data = subset(all, Pond=="ERL85"), aes(y=fDOM_RFU, x=Date_time, color = Pond)) +
  scale_x_datetime(date_breaks = "1 day", date_labels = "%m-%d") +
  scale_color_manual(breaks=c('B2P4', 'B3P0', 'B3P4', "ERL152", "ERL85"),
                     values=c('B2P4'="gray17", 'B3P0'='dodgerblue3', 'B3P4'='magenta4',
                              "ERL152"="olivedrab4", "ERL85"="chocolate")) +
  ggtitle("No Fish")

plot_grid(p11, p12, nrow = 2, rel_heights =  c(0.229,0.2,0.2,0.32))
```

### 2024-11-19 LakeMetabolism_project/project_22/reports/report_analysis_Chloro_RFU_2022.Rmd
First push

---
title: "Analysis Chlorophyll RFU 2022"
author: "Emanuel Mauch"
date: "2023-07-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This is a report of what I've done so far regarding the analysis of Chlorophyll RFU from the Greenland Sondes data 2022. The analysis includes a t-test and a linear mixed model.

# Step 0: set up R-script
```{r, warning = F, message=FALSE}
rm(list= ls())

setwd("~/ZIVI_EAWAG/project_22")

source("~/ZIVI_EAWAG/project_22/Moritz_Luehrig_paper_stuff/methods_packages.R")

# Mixed model packages
library(lme4)
library(nlme)

# Assisting packages
library(car)
library(pastecs)
library(ggpubr)
library(GGally)
library(effects)
library(arm)
library(MuMIn)

sonde_key = fread( "~/ZIVI_EAWAG/project_22/ponds_sonde_key.txt", header=T)
# Treatments:
# S: fish from single population (L26)
# D: fish from 2 populations (double, L26+ERL33)
# NF: no fish

# daily pond-wise means (want to account for daily fluctuations by using the daily
# means of the individual ponds, simultaneously having enough datapoints to fit the model
# -> need more datapoints than levels of the random effect Sonde later)
dat = fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_daily_avg.txt")
```

# Step 1: format dataset
```{r}
dat = dat[, c("Pond", "Treatment", "Sonde", "Chlorophyll_RFU")]

# Summarize S (fish from single population) and D (fish from two populations) into F (Fish)
dat$Fish <- recode(dat$Treatment, "c('S', 'D') = 'yes'; c('NF') = 'no'")

# Convert characters to factors
dat$Fish <- factor(dat$Fish)
dat$Sonde <- factor(dat$Sonde)
```

# Step 2: EDA
## Step 2.1: Visualize research question
```{r}
# Graphically
ggplot(dat, aes(Fish, Chlorophyll_RFU)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(col = Sonde), width = 0.25, alpha=1, size = 3) +
  labs(y = "Chlorophyll RFU", title = "Pond-wise daily means Chloropyll RFU no Fish vs. Fish") +
  theme_light()
# Different sondes seem to have different intercepts, even though the treatment
# is the same
```

## Step 2.2: Independence of Chlorophyll_RFU
Although Chlorophyll_RFU is strongly time-dependent, we sort of accounted
for this dependence by taking the overall or daily means of the individual ponds.

## Step 2.3. homogeneity of Chlorophyll_RFU
```{r}
ggplot(dat, aes(Fish, Chlorophyll_RFU)) +
  geom_boxplot() +
  theme_light()
# Variance in ponds with fish much higher
```

# Step 3: model fitting

Approach:

1. T-test
  + Since the assumption
of homogeneity of variance is violated (ponds with Fish seem to vary much more in their
diurnal Chlorophyll pattern, which is also part of the research question, 
but can be addressed at a later stage), we can just do a two-sample t-test
allowing for unequal variances.
  + A concern is not accounting for the fact that the sondes
have an impact on the measurements as well (as well as the solar radiation).
  + I addition, I'm not sure what consequences follow if one uses aggregated data
(comparing pond-wise means) to do a t-test.
What I am sure is that one looses information about the distribution of chloro
in the different ponds, as well power to detect a relationship.

2. Mixed model
  + I was also thinking about a mixed model with fish as fixed effects and
sondes as a random effect with random intercepts.
For that, I will be using the daily means, to sort of adjust for the daily,
time-dependent fluctuations in Chlorophyll RFU

Hypotheses:

* H0: no associaton between the presence/absence of fish and chlorophyll RFU
* H1: association between presence/absence of fish and chlorophyll RFU

## Step 3.1: T-test
```{r}
# Welch two-sample t-test
(t1 <- t.test(formula = dat$Chlorophyll_RFU ~ dat$Fish, var.equal = FALSE, conf.level = 0.95))
# est. mean for ponds no Fish: -0.21
# est. mean for ponds Fish: 1.07
# Esimated difference in means no Fish - Fish: -1.28
# 95% Wald-CI: from -1.57 to -1.00
# p < 0.0001
# There is strong evidence for an association between the presence/absence of fish in the
# ponds and the mean Chlorophyll RFU measured.
```

## Step 3.2: Mixed effects model: EDA
```{r, message=FALSE, echo=FALSE}
# ECDF no Fish vs. Fish daily means
ggplot(dat, aes(Chlorophyll_RFU, col = Fish)) +
   stat_ecdf() +
   labs(y = expression("P(x"<="X | Fish)"), title = "Empirical Cumulative Distribution
        Function (ECDF) of Chloropyll RFU no Fish vs. Fish") +
   theme_light()
```

```{r, message=FALSE, echo=FALSE, fig.align='center'}
ggarrange(
  ggplot(subset(dat, Fish=="no")) +
     geom_histogram(aes(x=Chlorophyll_RFU)) +
     theme_light() +
     labs(title = "No Fish"),
  ggplot(subset(dat, Fish=="yes")) +
     geom_histogram(aes(x=Chlorophyll_RFU)) +
     theme_light() +
     labs(title = "Fish")
  )
```

* Odd distribution of chloro for ponds without fish
* Overdispesion in ponds with fish ("long tail")
* In gerneral, Chlorphyll_RFU does not seem to be normally distributed.

### Step 3.2.2: Fit Model
```{r, warning=FALSE}

# Identifying the random structure
m1 <- lmer(Chlorophyll_RFU ~ Fish + (1|Sonde), REML = TRUE, data = dat)
# I had this simple model in mind

m2 <- lmer(Chlorophyll_RFU ~ Fish + (1|Sonde) + (1|Pond), REML = TRUE, data = dat)
# Maybe there is also variability caused by the different ponds, independent
# of the treatment (different baseline Chlorophyll RFU for whatever reason)?
# Although pond and sonde will be highly correlated

anova(m1, m2)
# Random intercept for pond doesn't lead to improvement
# take m1

# Rename
m <- m1
```

#### Step 3.2.3: Model diagnostics

```{r, fig.align='center'}
plot(m, warning = F, message = F)
```

* Residual structure looks odd
* Residuals seem to increase, as the fitted values increase (heteroscedasticity)

```{r}
# Diagnostics dataframe
df <- data.frame(z.resid= scale(residuals(m)),
                                Fish= m@frame$Fish,
                                Fitted= fitted.values(m))
```

```{r, warning=FALSE, message=FALSE, echo=FALSE}
# Distribution of Chlorophyll_RFU
ggarrange(
  ggplot(df, aes(z.resid)) +
    geom_histogram(aes(y= ..density..), fill= "white", col= "black") +
    stat_function(fun= dnorm,
                  args= list(mean(df$z.resid),
                             sd(df$z.resid)),
                  n= 1e2,
                  col= "blue") +
    labs(y= "Density", x= "Standardized Residuals") +
    theme_bw(),
  ggplot(df, aes(sample= z.resid)) +
    stat_qq() +
    geom_abline(intercept= 0, slope= 1, col= "red") +
    labs(x= "Theoretical quantiles", y= "Sample Quantiles") +
    theme_bw(),
  ncol= 2)
```

* Deviations from the assumption of normally distributed residuals
* over/underdispersion
* This is probably largely driven through Sonde14, which had very high values
of chlorophyll RFU, lead to this deviation  from the normality assumption.

```{r, warning=FALSE, message=FALSE, echo=FALSE}
# Residual plots
ggarrange(
  ggplot(df, aes(Fish, z.resid)) +
    geom_hline(yintercept= 0, lty= 2, col= "grey") +
    geom_boxplot() +
    theme_bw(),
  ggplot(df, aes(Fitted, z.resid)) +
    geom_hline(yintercept= 0, lty= 2, col= "grey") +
    geom_point() +
    geom_smooth(col= "magenta", se= F) +
    theme_bw(),
  ncol= 2)
```

Heteroscedasticity in Fish

```{r, warning=FALSE, message=FALSE}
# Account for heteroscedasticity in Fish by applying a variance-function
# for the residuals:
# Constant variance for each level of Fish, but allowing for different variances
# in the 2 levels
vf1 <- varIdent(form= ~ 1|Fish)

# Refit our new model with package nlme
m.vf <- lme(Chlorophyll_RFU ~ Fish,
            random = (~1|Sonde),
            weights = vf1,
            na.action=na.exclude,
            data = dat)

# Refit previous model with package nlme
m.or <- lme(Chlorophyll_RFU ~ Fish,
            random = (~1|Sonde),
            na.action=na.exclude,
            data = dat)

# Compare to model without specified variance function
anova(m.or, m.vf)
# Model with specified variance function seems to be a better fit

# Rename
m <- m.vf
```

### Step 3.2.4: Model interpretation and predctions
```{r, warning=FALSE, message=FALSE}
Anova(m)
# Fish contributes significantly to explain the variability
# observed in Chlorophyll_RFU
S(m)
# Fixed effects
# - The expected daily mean RFU level for ponds without Fish is -0.21
# - Compared to ponds without fish, ponds with fish are expected to have daily
# Chlorophyll RFU levels increased by 1.28 units (p = 0.008)

# Random effects
# The additional standard deviation in Chlorophyll RFU caused by the different Sondes
# is estimated to be 0.61

# Variance function
# Compared to ponds with fish, ponds without fish are expected to have a standard
# deviation reduced by a factor of 0.17 of Chlorophyll RFU-levels

# Pseudo-R-squared for mixed models
r.squaredGLMM(m)
# Proportion of variance explained by fixed effects: 0.47
# Proportion of variance explained by entire model: 0.89
```

### Step 3.2.5: Prediction plot
```{r, warning=FALSE, message=FALSE, echo=FALSE, fig.align='center'}
pred.m<- data.frame(Effect("Fish", m))
pred.m$Fish<- factor(pred.m$Fish)

ggplot(pred.m, aes(Fish, fit, col= Fish)) +
  geom_errorbar(aes(ymin= lower, ymax= upper), width= .2, position= "dodge") +
  geom_point(size= 4, position= position_dodge(width= .2)) +
  geom_point(data= m$data, aes(y= Chlorophyll_RFU), alpha= .3,
             position= position_jitterdodge(dodge.width= .2,
                                            jitter.width= .1,
                                            jitter.height= 0)) +
  labs(y= "Chlorophyll RFU", title = "Predicted daily means of Chlorophyll RFU in ponds without
       fish vs. ponds with fish") +
  theme_light()
```

# Step 4: Relationship between Chlorophyll RFU and Chlorophyll ug/L

Now that we have an impression about what levels of Chlorophyll RFU to expect
in these ponds, we can ask ourselves how this RFU values translate to ug/L?

## Step 4.1: Visualization of the question
For that, we can plot Chlorophyll RFU vs. Chlorophyll ug/L of the time series
data from 2022:
```{r, warning = FALSE}
all <- fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_all.txt")

# Lets convert Pond to an unordered factor
all$Pond <- factor(all$Pond)

# plot
ggplot(data = all, aes(x = Chlorophyll_ugL, y = Chlorophyll_RFU, col = Pond)) +
  geom_point() +
  theme_light
```
There seems to be a perfectly linear relationship between the 2 variables. Additionally
it seems very much apparent that the different ponds seem to have different intercepts,
but same slopes.

## Step 4.1: Model Chlorophyll RFU
Lets do a simple mixed model that can estimate a global slope and intercept, yet acknowledges that
observations are clustered in different sondes/ponds
```{r}
m1 <- lmer(Chlorophyll_RFU ~ Chlorophyll_ugL + (1|Pond), data = all)
# Random intercept pond: Quantifies the additional variance around the condtional
# mean E[Chlorophyll_RFU_i | Chlorophyll_ugL = Chlorophyll_ugL_i]

summary(m1)
# (Intercept): global intercept across all ponds
# If there is no Chlorophyll at all in the water, the Chlorophyll RFU measured
# by the sonde is expected to be -1.67 units.

# Chlorophyll_ugL: global slope of Chlorophyll_ugL
# For 1 ug/L increase in Chlorophyll, Chlorophyll RFU is expected to increase
# by 0.318 units.
```

## Step 4.2: Visualize predition of the model

## Step 4.3: Formulate the fitted equation

The fitted equation for the fixed part is:
Chlorophyll_RFU = -1.672 + 0.3181 * Chlorophyll_ugL

# Step 5: Bringing it all together
Interpretation of the mixed model describing the relationship between Fish-
Treatment and Chlorophyll_RFU in terms of Chlorophyll ug/L:

* We learned from Step 3.2 that the expected daily mean RFU level
for ponds without fish is -0.21. This would correspond to a daily mean Chlorophyll ug/L-level
of (-0.21 + 1.672)/0.3181 = 4.60, according to our model.

* Additionally, according to the model from Step 3.2, the expected daily mean RFU level
for ponds with Fish is -0.21 + 1.28 = 1.07. This would correspond to a  daily mean Chlorophyll ug/L-level
of (1.07 + 1.672)/0.3181 = 8.62, according to our model.

# 6: Appendix
## Version and packages used to generate this report:
```{r, echo=FALSE}
cat(paste(Sys.time(), Sys.timezone(), "\n"))
sessionInfo()
```

# 7: Code used to generate the plots
```{r, warning=FALSE, message=FALSE, eval=FALSE}
# ECDF no Fish vs. Fish daily means
ggplot(dat, aes(Chlorophyll_RFU, col = Fish)) +
   stat_ecdf() +
   labs(y = expression("P(x"<="X | Fish)"), title = "Empirical Cumulative Distribution
        Function (ECDF) of Chloropyll RFU no Fish vs. Fish") +
   theme_light()

# Histogram Chlorophyll RFU no Fish vs. Fish
ggarrange(
  ggplot(subset(dat, Fish=="no")) +
     geom_histogram(aes(x=Chlorophyll_RFU)) +
     theme_light() +
     labs(title = "No Fish"),
  ggplot(subset(dat, Fish=="yes")) +
     geom_histogram(aes(x=Chlorophyll_RFU)) +
     theme_light() +
     labs(title = "Fish")
  )

# Distribution of Chlorophyll_RFU
ggarrange(
  ggplot(df, aes(z.resid)) +
    geom_histogram(aes(y= ..density..), fill= "white", col= "black") +
    stat_function(fun= dnorm,
                  args= list(mean(df$z.resid),
                             sd(df$z.resid)),
                  n= 1e2,
                  col= "blue") +
    labs(y= "Density", x= "Standardized Residuals") +
    theme_bw(),
  ggplot(df, aes(sample= z.resid)) +
    stat_qq() +
    geom_abline(intercept= 0, slope= 1, col= "red") +
    labs(x= "Theoretical quantiles", y= "Sample Quantiles") +
    theme_bw(),
  ncol= 2)

# Residual plots
ggarrange(
  ggplot(df, aes(Fish, z.resid)) +
    geom_hline(yintercept= 0, lty= 2, col= "grey") +
    geom_boxplot() +
    theme_bw(),
  ggplot(df, aes(Fitted, z.resid)) +
    geom_hline(yintercept= 0, lty= 2, col= "grey") +
    geom_point() +
    geom_smooth(col= "magenta", se= F) +
    theme_bw(),
  ncol= 2)

# Prediction plot
pred.m<- data.frame(Effect("Fish", m))
pred.m$Fish<- factor(pred.m$Fish)

ggplot(pred.m, aes(Fish, fit, col= Fish)) +
  geom_errorbar(aes(ymin= lower, ymax= upper), width= .2, position= "dodge") +
  geom_point(size= 4, position= position_dodge(width= .2)) +
  geom_point(data= m$data, aes(y= Chlorophyll_RFU), alpha= .3,
             position= position_jitterdodge(dodge.width= .2,
                                            jitter.width= .1,
                                            jitter.height= 0)) +
  labs(y= "Chlorophyll RFU", title = "Predicted daily means of Chlorophyll RFU in ponds without
       fish vs. ponds with fish") +
  theme_light()

```

### 2024-11-19 LakeMetabolism_project/project_22/reports/report_analysis_metabolism_B3P3_2022.Rmd
First push

---
title: "Analysis Metabolism Pond B3P3 2022"
author: "Emanuel Mauch"
date: "2023-07-26"
output: pdf_document
bibliography: metab_B3P3.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center")
```

# Introduction

The following analysis attempts to model ecosystem metabolism of pond B3P3 in 2022
based on dissolved oxygen measurements (do). The analysis is 
made in the context of the Stickelback experiments of Blakes group in Greenland and is based on the paper "LakeMetabolizer:
an R package for estimating lake metabolism from free-water oxygen using diverse statistical models"
by @Winslow2016. The analysis of B3P3 is meant to serve as a possible blueprint
for other ponds in the future. Additionally metadata was downloaded from two different webpages,
which are described in the section "Data sources". This report is deliberatly made as transparent
and reproducible as possible to maintain verifyable for possible readers.

# Step 0: set up R-script
```{r, message=FALSE}
rm(list= ls())

setwd("~/ZIVI_EAWAG/project_22")
source("~/ZIVI_EAWAG/project_22/Moritz_Luehrig_paper_stuff/methods_packages.R")

# Estimating lake metabolism with free-water oxygen
library(LakeMetabolizer)

#demo('fig_metab', package='LakeMetabolizer')

# For plotting
library(GGally)

# Nonparametric Missing Value Imputation using Random Forest
# library(missForest)

# This is our complete dataset of the sondes measurements 2022
# Measurement Interval: 2 minutes
all <- fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_all_uncut.txt")

# This is the wind dataset
# Measurement Interval: 1 hour
wind <- fread("~/ZIVI_EAWAG/project_22/data_metabolism_wind/wind_narsarsuaq_radiosonde_2022_complete.txt")
# The wind variable is the average hourly wind speed in m/s, measured with
# a radiosonde in Narsarsuaq, Greenland
```

# Step 1: data formatting
```{r}
# Select columns to keep from our time series
all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]

# Select Pond B3P3 (Treatment: Sticklebacks from single population; source: pond L26)
all <- subset(all, Pond == "B3P3")

# Rename
all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))

# Isolate the desired period (described in the introduction)
all <- all[c(255:7455),]

# Ommit last row (not included in our timeseries)
all <- all[-nrow(all), ]

# format the wind dataset
wind$datetime <- as.POSIXct(wind$datetime, format = "%d.%m.%Y %H:%M")

wind <- wind %>%
  mutate(datetime = as.POSIXct(format(datetime, format = "%Y-%m-%d %H:01:00")))

# Create a new inflated dataset with wind measurements every 2 minutes
# The hourly mean will be assigned to every observation (2min-interval) within that hour
wind_ext <- wind %>%
  complete(datetime = seq(from = min(datetime), to = max(datetime), by = "2 min"))

# Fill the missing Wind_speed_ms values with the corresponding hourly values using 'fill'
wind_ext <- wind_ext %>%
  fill(wsp, .direction = "up")

# Shift Wind_speed_ms one row up using 'lag'
wind_ext <- wind_ext %>%
  mutate(wsp = lead(wsp, default = last(wsp)))

# Ommit last row (not included in our timeseries)
wind_ext <- wind_ext[-nrow(wind_ext), ]

# Reset row names for the final result
rownames(wind_ext) <- NULL

head(wind_ext,3)
```

# Step 2: merge sonde and wind dataset
```{r}
all <- merge(wind_ext, all, by = "datetime")

# Save
fwrite(all, "~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_B3P3_2022.txt", sep="\t")

head(all,3)
```

# Step 3: Missing data imputation
We need a complete ODO_mgL timeseries. Therefore we will impute the missing values
here, with the package "missForest" (Nonparametric Missing Value Imputation using Random Forest).

Update: since ODO_mgL of B3P3 is complete, we don't need to do that here
But for other ponds, we might need this code.
```{r}
#####
# all <- fread("~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_B3P3_2022.txt", sep="\t")
# 
# # Correct shifted Date_time
# Date_time_col <- all$Date_time
# Shift_date_time <- Date_time_col + hours(2)
# all$Date_time <- Shift_date_time

# # Prepare for imputation
# all$Pond <- factor(all$Pond)
# all_temp <- all[, c("Wind_speed_ms", "Pond", "ODO_mgL", "Temp_C")]
# 
# # Impute
# imp_all_temp <- missForest(all_temp, verbose = T, variablewise = T)
# # Retrieve imputed dataset
# imp_all_temp <- imp_all_temp$ximp
# 
# # Append imputed variable to all
# all$ODO_mgL_imp <- imp_all_temp$ODO_mgL
# 
# colSums(is.na(all))
# 
# fwrite(all,"~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_imp_wind_B3P3_2022.txt", sep="\t")
#####
```

# Step 4: Model choice
Gas transfer coefficient model: kcole() (see paper linked in the introduction, https://doi.org/10.1080/IW-6.4.883)

* only needs wind speed and sensor height (Assumption: wind speed is
measured at 10m, since the data are measured by a radiosonde)

Lake metabolism model: I'll try all the models mentioned in the paper:

* Bookkeeping
* Estimation via Ordinary Least Squares (OLS)
* via Maximum Likelihood Estimation (MLE)
* via Maximum Likelihood Estimation + Kalman filter
* Bayesian approach

# Step 5: Calculate k600 using the Cole method
```{r}
all <- fread("~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_B3P3_2022.txt", sep="\t")

# Correct shifted Date_time
Date_time_col <- all$datetime
Shift_date_time <- Date_time_col + hours(2)
all$datetime <- Shift_date_time

# This function needs specific column names
all$wnd <- all$wsp
all$wsp <- NULL

# Also only the 2 columns of interest, otherwise it gets confused
all.600 <- all[,c("datetime","wnd")]
k600.cole <- k.cole(all.600)

# Merge
all <- merge(all, k600.cole, by = "datetime")
head(all,3)
```

# Step 6: Calculate gas-specific k600
```{r}
kgas <- k600.2.kGAS(all)

# Merge
all <- merge(all, kgas, by = "datetime")

# only keep k.gas
all$k600 <- NULL

head(all,3)
```

# Step 7: Calculate dissolved oxygen saturated (do.sat)
```{r}
# Instead of the sonde-included calculations, I'll use a function
# provided by the authors.

o2.sat <- o2.at.sat(all[,c('datetime','wtr')])

# Merge
all <- merge(all, o2.sat, by = "datetime")

head(all,3)

fwrite(all,"~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_param_B3P3_2022.txt", sep="\t")
```

# Step 8: Calculate Actively mixed layer depth (z.mix)

Pond B3P3 is about 5 meters deep
According to the profiling plots, B3P3 had an actively mixed layer depth of
only 0.5 m on 2022-06-21. However, wind speed was low at that time.
Since Blake told me that I can assume an average mixed layer depth of about
2-3 meters, if a pond has a max depth of 5 meters, I am going to take 2.5m 
for the actively mixed layer depth.
Of course, this is a simplification, and to do it perfectly, one would need
to do a temperature time-series of different layers of the same pond.
This could of course be also incorporated in the following models.

```{r}
all <- fread("~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_param_B3P3_2022.txt", sep="\t")

# Set Actively mixed layer depth to 2.5m
all$z.mix <- 2.5
head(all,3)

# Save
fwrite(all,"~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_param2_B3P3_2022.txt", sep="\t")
```

# Step 9: Derive photosynthetically active radiation (par) from shortwave irradiation (sw)

Here, I take the downwelling shortwave irradiation (tilt corrected) from the
QAS_L automated weather station a couple of kilometers away from Narsarsuaq
It's the closest weather station measuring this parameter, that I could find.
```{r}
# Import irradiation dataset
ir <- fread("~/ZIVI_EAWAG/project_22/data_metabolism_wind/data_down_shortwave_irr_tilt_corr_2022_complete.txt", sep="\t")

# Format datetime
ir$datetime <- as.POSIXct(ir$datetime, format = "%d.%m.%Y %H:%M")

# Align it with the observations of the sonde (always 01, 03, 05, etc.)
ir <- ir %>%
  mutate(datetime = as.POSIXct(format(datetime, format = "%Y-%m-%d %H:01:00")))

# Create a new inflated dataset with wind measurements every 2 minutes
# The hourly mean will be assigned to every observation (2min-interval) within that hour
ir_ext <- ir %>%
  complete(datetime = seq(from = min(datetime), to = max(datetime), by = "2 min"))

# Fill the missing dsr_cor values with the corresponding hourly values using 'fill'
ir_ext <- ir_ext %>%
  fill(dsr_cor, .direction = "up")

# Shift dsr_cor one row up using 'lag'
ir_ext <- ir_ext %>%
  mutate(dsr_cor = lead(dsr_cor, default = last(dsr_cor)))

# Ommit last row (not included in our timeseries)
ir_ext <- ir_ext[-nrow(ir_ext), ]

# Reset row names for the final result
rownames(ir_ext) <- NULL
head(ir_ext,3)

# Derive par from sw
par <- sw.to.par(ir_ext, sw.col = "dsr_cor")
rownames(par) <- NULL
head(par,3)

# Specify correct timezone
# par$datetime <- as.POSIXct(par$datetime, tz = "UTC")

# Correct shifted datetime col
Date_time_col <- par$datetime
Shift_date_time <- Date_time_col + hours(2)
par$datetime <- Shift_date_time

# Merge with our metabolism dataset
# Import
all <- fread("~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_param2_B3P3_2022.txt", sep="\t")

# Merge
all <- merge(all, par, by = "datetime")
head(all,3)

# Save
fwrite(all,"~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_param3_B3P3_2022.txt", sep="\t")
```

# Step 10: Fit models
```{r}
# Now lets read in our prepared metabolism dataset
all <- fread("~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_param3_B3P3_2022.txt", sep="\t")

# Convert z.mix_m
all$z.mix <- as.numeric(all$z.mix)

# Choose columns to keep
all <- all[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
head(all,3)

# Save again
fwrite(all,"~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_param4_B3P3_2022.txt", sep="\t")
```

```{r, eval =FALSE}
# bookkeep model:
# for some reason, it dosen't run yet
bookkeep.res <- metab(all, method = "bookkeep", wtr.name='wtr', do.obs.name='do.obs',
                      irr.name="par", z.mix = "z.mix")
bookkeep.res <- metab(all,irr.name="par")

# OLS model:
ols.res <- metab(all, method = "ols", wtr.name='wtr', do.obs.name='do.obs',
                      irr.name="par", z.mix = "z.mix")
fwrite(ols.res, "~/ZIVI_EAWAG/project_22/metabolism_results/B3P3_ols_2022.txt", sep="\t")

# MLE model:
mle.res <- metab(all, method = "mle", wtr.name='wtr', do.obs.name='do.obs',
                 irr.name="par", z.mix = "z.mix")
fwrite(mle.res, "~/ZIVI_EAWAG/project_22/metabolism_results/B3P3_mle_2022.txt", sep="\t")

# MLE + Kalman filter:
kalman.res <- metab(all, method='kalman', wtr.name='wtr', do.obs.name='do.obs',
                    irr.name='par', z.mix = "z.mix")
fwrite(kalman.res, "~/ZIVI_EAWAG/project_22/metabolism_results/B3P3_kalman_2022.txt", sep="\t")

# Bayesian
bayesian.res <- metab(all, method='bayesian', wtr.name='wtr', do.obs.name='do.obs',
                      irr.name='par', z.mix = "z.mix")
fwrite(bayesian.res, "~/ZIVI_EAWAG/project_22/metabolism_results/B3P3_bayesian_2022.txt", sep="\t")
```

# Step 11: Visualize the results
## Plots of ecosystem parameters
```{r, message=FALSE, echo=FALSE, warning = FALSE, fig.height = 10, fig.width=9, fig.cap="\\label{fig:figs}Plots of ecosystem parameters used to predict metabolism of B3P3."}
# Prepare
library(ggpubr)
require(grid)

all <- fread("~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_param3_B3P3_2022.txt", sep="\t")

p4 = ggplot((all)) + theme_light() +
  geom_line(aes(y=do.obs, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("DO (mg L",NULL^-1,")")))

p5 = ggplot((all)) + theme_light() +
  geom_line(aes(y=do.sat, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("Equilibrium\nDO concentration (mg L",NULL^-1,")")))

p6 = ggplot((all)) + theme_light() +
  geom_line(aes(y=par, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("PAR (",mu,"mol m",NULL^-2," s",NULL^-1,")")))

p7 = ggplot((all)) + theme_light() +
  geom_line(aes(y=k.gas, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("Gas and temperature specific\ngas transfer coefficient (m",NULL^-1,")")))

ggarrange(p4, p5, p6, p7, nrow=5)
```

## Plots of metabolism
```{r, message=FALSE}
ols.res <- fread("~/ZIVI_EAWAG/project_22/metabolism_results/B3P3_ols_2022.txt", sep="\t")
mle.res <- fread("~/ZIVI_EAWAG/project_22/metabolism_results/B3P3_mle_2022.txt", sep="\t")
kalman.res <- fread("~/ZIVI_EAWAG/project_22/metabolism_results/B3P3_kalman_2022.txt", sep="\t")
bayesian.res <- fread("~/ZIVI_EAWAG/project_22/metabolism_results/B3P3_bayesian_2022.txt", sep="\t")

# Modify result datasets to have a column specifiying the model used
ols.res$Model <- "OLS"
mle.res$Model <- "MLE"
kalman.res$Model <- "MLE + Kalman filter"
bayesian.res$Model <- "Bayesian"

# Merge the 4 result datasets from the 4 different models
merged.res <- rbind(ols.res, mle.res, kalman.res, bayesian.res)

# Create a date variable
merged.res$Date <- as.Date(paste(merged.res$year, "-", merged.res$doy, sep = ""), format = "%Y-%j")

# Select columns to keep
merged.res <- merged.res[,c("Date", "GPP", "R", "NEP", "Model")]

# Save
fwrite(merged.res, "~/ZIVI_EAWAG/project_22/metabolism_results/merged_results_B3P3_2022.txt", sep="\t")
```

```{r, echo=FALSE, message = FALSE, warning = FALSE, fig.height = 9, fig.width=9, fig.cap="\\label{fig:figs}estimated metabolism of pond B3P3 during a period of 9 days, estimated with 4 different models."}
# Plot
# GPP
p1 = ggplot(subset(merged.res, Model=="OLS")) + theme_light() +
  geom_line(aes(y=GPP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE"), aes(y=GPP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE + Kalman filter"), aes(y=GPP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="Bayesian"), aes(y=GPP, x=Date, color = Model),lwd = 1.25) +
  ylab(expression(paste("GPP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))

# R
p2 = ggplot(subset(merged.res, Model=="OLS")) + theme_light() +
  geom_line(aes(y=R, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE"), aes(y=R, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE + Kalman filter"), aes(y=R, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="Bayesian"), aes(y=R, x=Date, color = Model),lwd = 1.25) +
  ylab(expression(paste("R (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))

# NEP
p3 = ggplot(subset(merged.res, Model=="OLS")) + theme_light() +
  geom_line(aes(y=NEP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE"), aes(y=NEP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE + Kalman filter"), aes(y=NEP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="Bayesian"), aes(y=NEP, x=Date, color = Model),lwd = 1.25) +
  ylab(expression(paste("NEP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))

fig1 <- ggarrange(p1 + rremove("xlab"), p2 + rremove("xlab"), p3 + rremove("xlab"),
                  nrow=3, common.legend = TRUE, legend="bottom")

annotate_figure(fig1, top = text_grob("Estimated metabolism of pond B3P3"))
```

After talking to Blake, we suggest to take the Bayesian approach to
model metabolism, since its the most flexible approach, allowing us
to yield the maximum amount of information out of our data.

According to the Bayesian model, B3P3 is productive during the whole time-span
(NEP > 0).

# 12: Data Sources

* Wind data: https://www.dmi.dk/lokationarkiv/show/GL/3421711/Narsarsuaq/#arkiv
* Irradiation data: https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU

# 13: Appendix
## Version and packages used to generate this report:
```{r, echo=FALSE}
cat(paste(Sys.time(), Sys.timezone(), "\n"))
sessionInfo()
```

## Code used to generate plots:
```{r, eval=FALSE}
# Plots of ecosystem parameters
all <- fread("~/ZIVI_EAWAG/project_22/data_metabolism/merged_ODO_wind_param3_B3P3_2022.txt", sep="\t")

p4 = ggplot((all)) + theme_light() +
  geom_line(aes(y=do.obs, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("DO (mg L",NULL^-1,")")))

p5 = ggplot((all)) + theme_light() +
  geom_line(aes(y=do.sat, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("Equilibrium\nDO concentration (mg L",NULL^-1,")")))

p6 = ggplot((all)) + theme_light() +
  geom_line(aes(y=par, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("PAR (",mu,"mol m",NULL^-2," s",NULL^-1,")")))

p7 = ggplot((all)) + theme_light() +
  geom_line(aes(y=k.gas, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("Gas and temperature specific\ngas transfer coefficient (m",NULL^-1,")")))

fig2 <- ggarrange(p4, p5, p6, p7,
                  nrow=5)

# Plots of metabolism
# GPP
p1 = ggplot(subset(merged.res, Model=="OLS")) + theme_light() +
  geom_line(aes(y=GPP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE"), aes(y=GPP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE + Kalman filter"), aes(y=GPP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="Bayesian"), aes(y=GPP, x=Date, color = Model),lwd = 1.25) +
  ylab(expression(paste("GPP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))

# R
p2 = ggplot(subset(merged.res, Model=="OLS")) + theme_light() +
  geom_line(aes(y=R, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE"), aes(y=R, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE + Kalman filter"), aes(y=R, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="Bayesian"), aes(y=R, x=Date, color = Model),lwd = 1.25) +
  ylab(expression(paste("R (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))

# NEP
p3 = ggplot(subset(merged.res, Model=="OLS")) + theme_light() +
  geom_line(aes(y=NEP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE"), aes(y=NEP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="MLE + Kalman filter"), aes(y=NEP, x=Date, color = Model),lwd = 1.25) +
  geom_line(data = subset(merged.res, Model=="Bayesian"), aes(y=NEP, x=Date, color = Model),lwd = 1.25) +
  ylab(expression(paste("NEP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))

fig1 <- ggarrange(p1 + rremove("xlab"), p2 + rremove("xlab"), p3 + rremove("xlab"),
                  nrow=3, common.legend = TRUE, legend="right")

annotate_figure(fig1, top = text_grob("Estimated metabolism of pond B3P3"))
```

# 14: References

### 2024-11-19 LakeMetabolism_project/project_22/reports/sondes_status_2022.Rmd
First push

---
title: "Sensor status report 2022"
author: "Emanuel Mauch"
date: "2023-07-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
setwd("~/ZIVI_EAWAG/project_22/sondes_status_report_2022")
rm(list= ls())
source("~/ZIVI_EAWAG/project_22/Moritz_Luehrig_paper_stuff/methods_packages.R")
```

This is a status report of the sondes used for the stickleback-experiments 2022 in Greenland.
The upper table shows the measuring period of each of the 11 sondes used (the data for sonde2 pond ERL122 apparently became inaccessible), the number of observations and some comments.

```{r, echo=FALSE}
status <- read.delim("~/ZIVI_EAWAG/project_22/sondes_status_report_2022/sondes_status_2022.txt")
print(status)
```

The lower table is a completeness-check of the observations, during the period where we had complete days (cutting at the beginning and in the end to ensure equal periods of time for all sondes). It is apparent that all data is complete except the one from Sonde15 in pond ERL152.

```{r, echo=FALSE}
complete <- fread("~/ZIVI_EAWAG/project_22/data/sonde_data_completeness.txt", sep="\t")
print(complete)
```

# Summary:

* Two sondes apparently lost power early (sonde15 pond ERL152, sonde12 pond B3P4).
* One sonde didn't measure optical dissovled oxygen and its derivates (ODO, sonde11 pond B3P0).
* Additionally, sonde15 in pond ERL152 displayed huge data-gaps when plotted (visible in the completeness-table). Either there must have been some problem with the sonde itsef, or the data-gaps occurred when the data was transferred to the field laptop and 
subsequently splitted.

### 2024-11-21 LakeMetabolism_project/Pond_profile_summaries/code/PondProfile_summaries.R
Update for pond profile summaries

@@ -1,0 +1,67 @@
+################################################################################
+# This is a Script to calculate some summary statistics for Ponds in Greenland
+# sampled each summer.
+# The cut profile datasets from 2021-2024 have already been prepared with R scripts
+# beforehand.
+################################################################################
+
+# Step 0: Setup R-script--------------------------------------------------------
+rm(list= ls())
+
+require(data.table) # Advanced data wrangling
+require(openxlsx) # write excel files
+
+# Step 1: Import cut profile datasets 2021-2024---------------------------------
+
+# 2021, 2022, 2023, and 2024
+prof_21 <- fread("../../project_21/data/sondes_profiling_cut/merged_profiles_cut_2021.txt")
+prof_22 <- fread("../../project_22/data/sondes_profiling_cut/merged_profiles_cut_2022.txt")
+prof_23 <- fread("../../project_23/data/sondes_profiling_cut/merged_profiles_cut_2023.txt")
+prof_24 <- fread("../../project_24/data/sondes_profiling_cut/merged_profiles_cut_2024.txt")
+
+# Step 2: Write a function to calculate Pond-wise means, store into a dataset---
+
+means_profiles <- function(data, data_name) {
+  # Select columns from Depth_m (4th column) to the last
+  cols <- names(data)[5:ncol(data)]
+  
+  # extract Year
+  year <- as.numeric(paste0("20", sub(".*_", "", data_name)))
+  
+  # Calculate means grouped by Pond
+  result <- data[, lapply(.SD, mean, na.rm = TRUE), 
+                 by = .(Pond, Day), .SDcols = cols]
+  
+  # Column names of result dataset
+  setnames(result, cols, paste0("mean_", cols))
+  
+  # Add the Year column
+  result[, Year := year]
+  
+  return(result)
+}
+
+# Apply the function to datasets
+result_data_21 <- means_profiles(prof_21, "prof_21")
+result_data_22 <- means_profiles(prof_22, "prof_22")
+result_data_23 <- means_profiles(prof_23, "prof_23")
+result_data_24 <- means_profiles(prof_24, "prof_24")
+
+# Merge
+merged_results <- rbindlist(list(result_data_21, result_data_22, result_data_23,
+                            result_data_24), fill = TRUE)
+
+# Replace NaN with NA, if present
+merged_results[] <- lapply(merged_results, function(x) {
+  if (is.numeric(x)) x[is.nan(x)] <- NA
[…]

### 2024-11-21 LakeMetabolism_project/project_21/code/analysis_metabolism_B1P1_2021.R

@@ -21,7 +21,7 @@
 # Step 0: set up R-script ------------------------------------------------------
 rm(list= ls())
 
-# Packages ad functions from Moritz Luehrig's paper
+# Packages and functions from Moritz Luehrig's paper
 source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
 
 # Estimating lake metabolism with free-water oxygen

### 2024-12-05 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Work on manuscript

%%
%% Camera-ready submissions do not need line numbers, and
%% should have this option removed.
%%

\documentclass[fleqn,11pt,lineno]{manuscript}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul}

\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }

\title{Template for manuscript}

\author[1]{Author One}
\author[1]{Author Two}
\author[2,3]{Author Three}
\author[1]{Author Four}
\affil[1]{Author one affiliation}
\affil[2]{Author two affiliation}
\affil[3]{Author three affiliation}

\corrauthor[1]{Author Four}{email@address}

\keywords{Keyword1; Keyword2; Keyword3}

\begin{abstract}
This is the abstract.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% R specifications
<<include = FALSE>>=
# knitr
library(knitr)
opts_chunk$set(fig.path = 'plots/p', 
               echo = FALSE, 
               results = 'hide',
               fig.height = 4.5,
               fig.align = "center",
               cache = TRUE)

# packages
require(xtable) # generating latex tables from datasets
require(data.table) # data wrangling
require(readxl) # importing excel tables

@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

\section*{Introduction}
...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Materials and Methods}
...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}
...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conclusions}
...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Author contributions}
...

\section*{Institutional review}
...

\section*{Data availability} 
...

\section*{Funding}
...

\section*{Acknowledgments}
...

\section*{Conflicts of interest}
...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{main}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\beginsupplement
\renewcommand\figurename{Supplementary Figure}
\renewcommand\tablename{Supplementary Table}

\section*{Appendix}

\subsection{Study design and setup} \label{subsec:design}

In 2019, 12 glacial lakes ($N =$ 12) were chosen for an experiment near Narsarsuaq,
Greenland (61.1567\textdegree{}N, -45.4254\textdegree{}E).
These glacial lakes vary in area (0.21 to 1.82 hectares) and maximum
depth (2 to 8 m), but are all clustered within a few
kilometers of each other. All lakes were fishless at the beginning of the experiment.
Six lakes were subsequently introduced with three-spined sticklebacks
(\textit{Gasterosteus aculeatus}) from nearby lakes.
Lake B1P1, B2P2, and B3P3 were introduced with \textit{Gasterosteus aculeatus} from a single
population (lake L26, 61.253333\textdegree{}N, -45.529141\textdegree{}E),
while lake B2P3, B3P1, and B3P2 were introduced with \textit{Gasterosteus aculeatus} from
two populations (lake L26, 61.253333\textdegree{}N, -45.529141\textdegree{}E
and lake ERL33, 61.118369\textdegree{}N, -45.580845\textdegree{}E).
The remaining six lakes B1P4, B2P4, B3P0, ERL85, ERL122, and ERL152 were
used as fishless control. For the purpose of this study, the origin
of the introduced \textit{Gasterosteus aculeatus} is of minor importance,
as they all originate from the same area (Supplementary Table~\ref{tab:lakes}).

In 2021, 2022, and 2023, all 12 lakes were monitored over several days.
For that purpose, EXO2 multiparameter sondes were installed
(YSI, Yellow Springs, OH, USA), tracking ecosystem parameters with high
frequency (2-minute intervals in 2021 and 2022, 5-minute intervals in
2023 with the exception of ERL122, which was monitored in 15-minute intervals).
For the purpose of this study, only dissolved oxygen and temperature measurements
yielded from these sondes are relevant. The sensors were situated at a water depth
of approximately 1-1.5 m in each lake. All optical sensors were
wiped clean before every measurement with a built-in wiper.
The monitoring period was 16 September-24 September in 2021, 22 June-3 July in 2022,
and 22 June-17 July in 2023.

<<laketable, results = "asis", echo=FALSE>>=
# Import lakemaster file
lakes <- read_excel("../../Organisation/GL_Lake_Master.xlsx")

# Extract relevant ponds
lakes <- lakes[c(18:23, 73:75, 78, 28, 83),]

# Extract columns
lakes <- lakes[,c("Lake", "Lat", "Long", "Areaha", "Altitude", "Depth")]

# Rename lakes
lakes$Lake <- c("B1P1", "B2P2", "B3P3", "B2P3", "B3P1", "B3P2", "B1P4", "B2P4",
                "B3P0", "ERL85", "ERL122", "ERL152")

# Rename
setnames(lakes, c("Lake", "Latitude (°N)", "Longitude (°E)", "Area (hectare)",
                  "Altitude (m)", "Maximum Depth (m)"))

# Create treatment variable
lakes$Treatment <- c("Fish","Fish","Fish","Fish","Fish","Fish",
                   "No Fish","No Fish","No Fish","No Fish","No Fish","No Fish")

# Reorder
lakes <- lakes[,c("Lake", "Treatment", "Latitude (°N)",
                  "Longitude (°E)", "Altitude (m)", "Area (hectare)",
                  "Maximum Depth (m)")]

# Make a latex table from dataset
lakes <- xtable(lakes, align = c("l","l","l","l","l","l","l","l"),
                digits = c(0,0,0,5,5,0,2,2),
                caption = "Lakes included in the experiment, along with treatment
                and general characteristics.", label = "tab:lakes")

# Print
print(lakes, include.rownames = FALSE, caption.placement = "top", booktabs = TRUE)
@

\subsection{Data sources} \label{subsec:source}

Dissolved oxygen and water temperature measurements were yielded from EXO2 multiparameter
sondes, as described in section~\ref{subsec:design}. For the purpose
of estimating ecosystem metabolism, wind and irradiation data were yielded
from the QAS\_L automated weather station near Narsarsuaq, Greenland \citep{metadata}.

\subsubsection*{Weather data}

\subsection{Data preparation}

\subsection{Statistical analysis}

\subsection{Implementation}

\end{document}

### 2024-12-05 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.tex
Work on manuscript

--- 2024-12-05 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
@@
 
-\documentclass[fleqn,11pt,lineno]{manuscript}
+\documentclass[fleqn,11pt,lineno]{manuscript}\usepackage[]{graphicx}\usepackage[]{xcolor}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlsng}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hldef}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 %%\usepackage{setspace}
@@
 % R specifications
-<<include = FALSE>>=
-# knitr
-library(knitr)
-opts_chunk$set(fig.path = 'plots/p', 
-               echo = FALSE, 
-               results = 'hide',
-               fig.height = 4.5,
-               fig.align = "center",
-               cache = TRUE)
 
-# packages
-require(xtable) # generating latex tables from datasets
-require(data.table) # data wrangling
-require(readxl) # importing excel tables
-
-@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-<<laketable, results = "asis", echo=FALSE>>=
-# Import lakemaster file
-lakes <- read_excel("../../Organisation/GL_Lake_Master.xlsx")
-
-# Extract relevant ponds
-lakes <- lakes[c(18:23, 73:75, 78, 28, 83),]
-
-# Extract columns
-lakes <- lakes[,c("Lake", "Lat", "Long", "Areaha", "Altitude", "Depth")]
-
-# Rename lakes
-lakes$Lake <- c("B1P1", "B2P2", "B3P3", "B2P3", "B3P1", "B3P2", "B1P4", "B2P4",
-                "B3P0", "ERL85", "ERL122", "ERL152")
-
-# Rename
-setnames(lakes, c("Lake", "Latitude (°N)", "Longitude (°E)", "Area (hectare)",
-                  "Altitude (m)", "Maximum Depth (m)"))
-
-# Create treatment variable
-lakes$Treatment <- c("Fish","Fish","Fish","Fish","Fish","Fish",
-                   "No Fish","No Fish","No Fish","No Fish","No Fish","No Fish")
-
-# Reorder
-lakes <- lakes[,c("Lake", "Treatment", "Latitude (°N)",
-                  "Longitude (°E)", "Altitude (m)", "Area (hectare)",
-                  "Maximum Depth (m)")]
-
-# Make a latex table from dataset
-lakes <- xtable(lakes, align = c("l","l","l","l","l","l","l","l"),
-                digits = c(0,0,0,5,5,0,2,2),
-                caption = "Lakes included in the experiment, along with treatment
-                and general characteristics.", label = "tab:lakes")
-
-# Print
-print(lakes, include.rownames = FALSE, caption.placement = "top", booktabs = TRUE)
-@
+% latex table generated in R 4.4.1 by xtable 1.8-4 package
+% Thu Dec  5 16:44:34 2024
+\begin{table}[ht]
+\centering
+\caption{Lakes included in the experiment, along with treatment
+                and general characteristics.} 
+\label{tab:lakes}
+\begin{tabular}{lllllll}
+  \toprule
+Lake & Treatment & Latitude (°N) & Longitude (°E) & Altitude (m) & Area (hectare) & Maximum Depth (m) \\ 
+  \midrule
+B1P1 & Fish & 61.15338 & -45.57081 & 272 & 0.21 & 4.00 \\ 
+  B2P2 & Fish & 61.12299 & -45.55988 & 255 & 0.50 & 3.00 \\ 
+  B3P3 & Fish & 61.13385 & -45.57556 & 258 & 0.30 & 5.00 \\ 
+  B2P3 & Fish & 61.12275 & -45.55696 & 261 & 0.41 & 4.25 \\ 
+  B3P1 & Fish & 61.13130 & -45.51195 & 180 & 0.40 & 2.00 \\ 
+  B3P2 & Fish & 61.12788 & -45.51031 & 201 & 0.53 & 4.50 \\ 
+  B1P4 & No Fish & 61.16552 & -45.56801 & 304 & 0.44 & 2.20 \\ 
+  B2P4 & No Fish & 61.12192 & -45.55497 & 261 & 0.51 & 7.00 \\ 
+  B3P0 & No Fish & 61.13210 & -45.51416 & 177 & 0.81 & 4.00 \\ 
+  ERL85 & No Fish & 61.14171 & -45.59328 & 120 & 1.82 & 8.00 \\ 
+  ERL122 & No Fish & 61.14182 & -45.53623 & 111 & 1.10 & 5.00 \\ 
+  ERL152 & No Fish & 61.14646 & -45.59235 & 156 & 0.73 & 4.50 \\ 
+   \bottomrule
+\end{tabular}
+\end{table}
 

### 2024-12-06 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Work on  manuscript

@@
 \usepackage{soul}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=blue,      
+    urlcolor=blue,
+    citecolor=blue,
+    }
 
@@
 Dissolved oxygen and water temperature measurements were yielded from EXO2 multiparameter
-sondes, as described in section~\ref{subsec:design}. For the purpose
+sondes, as described in section~\nameref{subsec:design}. For the purpose
 of estimating ecosystem metabolism, wind and irradiation data were yielded
-from the QAS\_L automated weather station near Narsarsuaq, Greenland \citep{metadata}.
+from the Programme for Monitoring of the Greenland Ice Sheet (PROMICE), providing automatic
+weather station data \citep{Fausto:2021}.
+The dataset named \texttt{QAS\_L\_hour.csv} originating from the QAS\_L automated weather station
+near Narsarsuaq was downloaded from a
+\href{https://dataverse.geus.dk/citation?persistentId=doi:10.22008/FK2/IW73UU}{public database}
+provided by PROMICE \citep{metadata}.
+
+\subsection{Data preparation}
+
+The data preparation for estimating lake metabolism was done separately for each monitoring
+period (16 September-24 September 2021, 22 June-3 July 2022, and 22 June-17 July 2023).
+
+\subsubsection*{Sonde data}
+
+First, the raw sonde data from each lake were imported and merged into
+one dataset for a given monitoring period. The variables needed for lake metabolism
+estimation were water temperature (\textdegree{}C) and
+dissolved oxygen (mg/L). Next, an outlier analysis was performed by removing
+values higher than three times the median absolute deviation of all values in a
+sliding window of one day window size \citep{Luerig:2021}.
+After outlier removal, the time series of water temperature and dissolved oxygen
+were subsequently investigated for larger data gaps due to potential lack of sensor
+measurements over certain periods.
+
+To ensure overlapping estimation of lake metabolism, the data was subsequently
+cut to achieve equal starting and ending time points for all lakes during a given
+observation period. Due to large data gaps during the period of 2022, we chose
+to keep as much complete days as possible in order to estimate the maximum
+amount of days, rather than selecting the longest common monitoring period
+for all lakes.
+
+After cutting, missing values were replaced by a
+weighted moving average, where the weights of observations around the
+central value decrease exponentially \citep{Moritz:2017}.
+For larger data gaps spanning over several hours, we chose
+to not estimate lake metabolism for the affected days, rather than imputing these values.
 
 \subsubsection*{Weather data}
-
-\subsection{Data preparation}
 

### 2024-12-06 LakeMetabolism_project/project_21/code/analysis_Chloro_mgL_2021.R

@@ -1,281 +1,0 @@
-# Step 0: set up R-script ------------------------------------------------------
-rm(list= ls())
-
-setwd("~/ZIVI_EAWAG/project_21")
-
-source("~/ZIVI_EAWAG/project_21/Moritz_Luehrig_paper_stuff/methods_packages.R")
-
-# Mixed model packages
-library(lme4)
-library(nlme)
-
-# Assisting packages
-library(car)
-library(pastecs)
-library(ggpubr)
-library(GGally)
-library(effects)
-library(arm)
-library(MuMIn)
-
-sonde_key = fread( "~/ZIVI_EAWAG/project_22/ponds_sonde_key.txt", header=T)
-# Treatments:
-# S: fish from single population (L26)
-# D: fish from 2 populations (double, L26+ERL33)
-# NF: no fish
-
-# For t-test:
-# overall pond-wise means
-dat = fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_overall_avg.txt")
-
-# For mixed model:
-# daily pond-wise means (want to account for daily fluctuations by using the daily
-# means of the individual ponds, simultaneously having enough datapoints to fit the model
-# -> need more datapoints than levels of the random effect Sonde later)
-dat2 = fread("~/ZIVI_EAWAG/project_22/data/ponds_sonde_data_daily_avg.txt")
-
-# Step 1: format dataset -------------------------------------------------------
-
-dat = dat[, c("Pond", "Treatment", "Sonde", "Chlorophyll_RFU")]
-dat2 = dat2[, c("Pond", "Treatment", "Sonde", "Chlorophyll_RFU")]
-
-# Summarize S (fish from single population) and D (fish from two populations) into F (Fish)
-dat$Fish <- recode(dat$Treatment, "c('S', 'D') = 'yes'; c('NF') = 'no'")
-dat2$Fish <- recode(dat2$Treatment, "c('S', 'D') = 'yes'; c('NF') = 'no'")
-
-# Convert characters to factors
-dat$Fish <- factor(dat$Fish)
-dat$Sonde <- factor(dat$Sonde)
-dat2$Fish <- factor(dat2$Fish)
-dat2$Sonde <- factor(dat2$Sonde)
-
-# Step 2: EDA ------------------------------------------------------------------
-
-# Step 2.1: Visualize research question
-# Graphically
-ggplot(dat, aes(Fish, Chlorophyll_RFU)) +
[…]

### 2024-12-09 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Work on manuscript

@@
 
-\documentclass[fleqn,11pt,lineno]{manuscript}
+\documentclass[11pt,lineno]{manuscript}
+%\setlength{\mathindent}{0pt}
 %%\usepackage{setspace}
@@
 2023 with the exception of ERL122, which was monitored in 15-minute intervals).
-For the purpose of this study, only dissolved oxygen and temperature measurements
+For the purpose of this study, only dissolved oxygen (hereafter DO) and temperature measurements
 yielded from these sondes are relevant. The sensors were situated at a water depth
@@
 
-Dissolved oxygen and water temperature measurements were yielded from EXO2 multiparameter
+DO ($mg\,L^{-1}$) and water temperature (\textdegree{}$C$) measurements
+were yielded from EXO2 multiparameter
 sondes, as described in section~\nameref{subsec:design}. For the purpose
@@
 provided by PROMICE \citep{metadata}.
+Wind data was provided as average wind speed in hourly intervals ($m\,s^{-1}$), while
+irradiation was provided as downwelling shortwave irradiation additionally
+corrected for the tilt of the sensor ($W\,m^{-2}$).
 
-\subsection{Data preparation}
+\subsection{Data analysis pipeline} \label{subsec:pipeline}
 
-The data preparation for estimating lake metabolism was done separately for each monitoring
+The data preparation and analysis for estimating lake metabolism was done separately for each monitoring
 period (16 September-24 September 2021, 22 June-3 July 2022, and 22 June-17 July 2023).
 
-\subsubsection*{Sonde data}
-
 First, the raw sonde data from each lake were imported and merged into
-one dataset for a given monitoring period. The variables needed for lake metabolism
-estimation were water temperature (\textdegree{}C) and
-dissolved oxygen (mg/L). Next, an outlier analysis was performed by removing
+one dataset for a given monitoring period. The variables required for lake metabolism
+estimation were water temperature and
+DO. Next, an outlier analysis was performed by removing
 values higher than three times the median absolute deviation of all values in a
 sliding window of one day window size \citep{Luerig:2021}.
-After outlier removal, the time series of water temperature and dissolved oxygen
-were subsequently investigated for larger data gaps due to potential lack of sensor
+After outlier removal, the time series of water temperature and DO
+were plotted and subsequently investigated for larger data gaps due to potential lack of sensor
 measurements over certain periods.
@@
 cut to achieve equal starting and ending time points for all lakes during a given
-observation period. Due to large data gaps during the period of 2022, we chose
+monitoring period. Due to large data gaps during the period of 2022, we chose
 to keep as much complete days as possible in order to estimate the maximum
@@
 
-After cutting, missing values were replaced by a
-weighted moving average, where the weights of observations around the
-central value decrease exponentially \citep{Moritz:2017}.
-For larger data gaps spanning over several hours, we chose
-to not estimate lake metabolism for the affected days, rather than imputing these values.
+After cutting the sonde data, they were subsequently merged with the weather data.
+Since the weather data were collected in hourly intervals, they were inflated to match
+the measurement intervals of the sonde data (see section \nameref{subsec:design}).
 
-\subsubsection*{Weather data}
+After merging sonde and weather data, potential missing values due to outlier removal
+were imputed by a weighted moving average, where the weights of observations around the
+central value to be imputed decrease exponentially \citep{Moritz:2017}.
+For larger data gaps spanning over several hours (due to sonde malfunction rather
+than outlier removal), we chose
+to not estimate lake metabolism for the affected days.\smallskip
 
-\subsection{Statistical analysis}
+All data preparation and analysis was done with the \texttt{R} programming language \citep{R}.
+To estimate lake metabolism, the package \texttt{LakeMetabolizer} was used \citep{Winslow:2016}.
+Specifically, a Bayesian framework to estimate whole lake metabolism from free-water
+DO by using the function \texttt{metab.bayesian} was chosen for
+this analysis \citep{Holtgrieve:2010}.
+In order to be able to fit the model, a minimum of 6 variables are needed as input:
 
-\subsection{Implementation}
+\begin{enumerate}
+\item doobs: DO concentration measurements ($mg\,L^{-1}$)
+\item do.sat: Equilibrium DO concentration for specific temperature ($mg\,L^{-1}$, hereafter do.sat)
+\item k.gas: Gas and temperature specific gas transfer coefficient ($m^{-1}$, hereafter k.gas)
+\item par: Photosynthetically active radiation ($\mu{}mol\,m^{-2}\,s^{-1}$, hereafter par)
+\item z.mix: Actively mixed layer depth ($m$, hereafter z.mix)
+\item wtr: Water temperature (\textdegree{}$C$)
+\end{enumerate}
+
+Some of the variables listed above have to be derived from other time series data prior
+to estimating lake metabolism,
+namely do.sat, k.gas, par, and z.mix.
+do.sat was derived by using the function \texttt{o2.at.sat}, which calculates
+the equilibrium DO concentration of oxygen in water at supplied conditions.
+To estimate k.gas, a gas transfer coefficient model must be fit.
+The \texttt{LakeMetabolizer} package offers different methods, and we chose
+an empirical wind-based gas exchange model, introduced by Vachon and
+Prairie in 2013 \citep{Vachon:2013}. This model not only takes wind into
+consideration, but also lake area.
+All models of gas exchange 
+return a k\textsubscript{600} value, a gas exchange normalized to a Schmidt 
+number (Sc) of 600, or O\textsubscript{2} at 17.5 \textdegree{}$C$.
+After estimating k\textsubscript{600}, it must be transformed to k.gas by using the
+function \texttt{k600.2.kGAS} provided by the \texttt{LakeMetabolizer}
+package. par was derived from shortwave irradiation,
+which we had available (see section \nameref{subsec:source}).
+To achieve this transformation, we used the function \texttt{sw.to.par},
+which uses the simple empirical transformation $par = 2.114 \times sw$ \citep{Britton:1976}.
+To estimate z.mix, one normally needs a time series profile of water temperature
+or water density. Since we did not have such data available, we decided to
+simulate actively mixed layer depth by drawing from a uniform distribution
+with limits 0 and maximum depth of the lake. The reasoning behind this simulation
+is that, although the simulated time series of z.mix likely differing substantially
+from the actual, a possible treatment effect of fish versus no fish should still be
+consistent, given the simulation is performed equally in all lakes.\smallskip
+
+After performing the data preparation and the derivation for certain model
+inputs, the Bayesian lake metabolism model was fitted for each lake and
+monitoring period. The Bayesian model is special, as it considers 2 types
+of errors: Differences between the true data generating process and the process
+defined in the model (process error) and errors resulting from inaccuracies
+of DO measurements (observation error). Reflecting this philosophy, the
+Bayesian model distinguishes between 3 categories of DO values: $y$ represents
+the DO measurements, $\alpha$ the true but unknown DO values, and
+$\alpha^{\ast}$ the model's estimates of the true value.
+The observed DO measurements $y$ are modeled as random deviations from the true
+value $\alpha$:
+
+\begin{equation}
+y_{t} \sim N(\alpha_{t}, \tau_{v}),
+\label{eq:doobs}
+\end{equation}
+
+where $\tau_{v}$ is the precision of the observation error (precision is
+the reciprocal of variance).
+Note, that the Bayesian model fits parameter values by making a comparison
+between observed and theoretical values of DO.
+This comparison is made in equation \ref{eq:dotrue}, where we define the true value of 
+DO at time $t$, $\alpha_{t}$, as being normally distributed with mean 
+$\alpha^{\ast}_{t}$ and process precision $\tau_{w}$:
+
+\begin{equation}
+\alpha_{t} \sim N(\alpha^{\ast}_{t}, \tau_{w}),
+\label{eq:dotrue}
+\end{equation}
+
+where $\tau_{w}$ is the precision of the process error.
+The important distinction of process and observation error is that
+process error affects the state of the system at time
+$t + k(k=0, 1, ..., T-t)$, because the state evolves dynamically, whereas
+observation error only affects the state of the system at time $t$.
+
+Both $\tau_{v}$ and $\tau_{w}$ are given minimally informative priors
+following a gamma distribution with shape and rate parameters of 0.001.
+
+The Bayesian model can be described by the following equations:
+
+\begin{gather}
+x^{2} \label{eq:sys1}\\
+x^{3} \label{eq:sys2}
+\end{gather}
 

### 2024-12-09 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.tex
Work on manuscript

@@
 
-\documentclass[fleqn,11pt,lineno]{manuscript}\usepackage[]{graphicx}\usepackage[]{xcolor}
+\documentclass[11pt,lineno]{manuscript}\usepackage[]{graphicx}\usepackage[]{xcolor}
 % maxwidth is the original width if it is less than linewidth
@@
 \usepackage{alltt}
+%\setlength{\mathindent}{0pt}
 %%\usepackage{setspace}

### 2024-12-10 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Work on manuscript

@@
 # packages
+require(LakeMetabolizer) # Modeling Lake Metabolism
+require(dplyr) # data wrangling
 require(xtable) # generating latex tables from datasets
@@
 
-\subsection{Data analysis pipeline} \label{subsec:pipeline}
+\subsection{Data pipeline} \label{subsec:pipeline}
 
@@
 do.sat was derived by using the function \texttt{o2.at.sat}, which calculates
-the equilibrium DO concentration of oxygen in water at supplied conditions.
+the equilibrium DO concentration in water at supplied conditions.
 To estimate k.gas, a gas transfer coefficient model must be fit.
@@
 Prairie in 2013 \citep{Vachon:2013}. This model not only takes wind into
-consideration, but also lake area.
+consideration, but also lake area. Notably, wind speed has to be normalized
+to 10 $m$ sensor height before fitting any gas exchange model, which is achieved
+with the function \texttt{wind.scale}.
 All models of gas exchange 
@@
 process error affects the state of the system at time
-$t + k(k=0, 1, ..., T-t)$, because the state evolves dynamically, whereas
+$t + k (k=0, 1, ..., T-t)$, because the state evolves dynamically, whereas
 observation error only affects the state of the system at time $t$.
@@
 \begin{gather}
-x^{2} \label{eq:sys1}\\
-x^{3} \label{eq:sys2}
+\alpha^{\ast}_{t} =
+\begin{cases}
+\alpha_{t-1} + \alpha_{t}, & \text{if } k_{t} = 0, \\
+\frac{\alpha_{t}}{k_{t-1}} + \frac{-\exp{(-k_{t-1})}\alpha_{t}}{k_{t-1}} +
+\exp{(-k_{t-1})}\alpha_{t-1}, & \text{otherwise},
+\end{cases} \label{eq:sys1} \\
+\alpha_{t} = \mathbf{X}_{t-1}\bm{\beta} + k_{t-1}O_{s,t-1}, \label{eq:sys2} \\
+k_{t} = \frac{K^{\ast}_{t}\Delta t}{z_{t}}. \label{eq:sys3}
 \end{gather}
 
+In this equation structure, $k_{t}$ is the coefficient of gas exchange;
+$\mathbf{X}$ is an $n \times 2$ matrix of predictor variables with $I$
+(irradiation in arbitrary light units) in the first column and $\ln{T}$ (\textdegree{}$C$) in the second
+column; $\bm{\beta}$ is a $2 \times 1$ vector of parameters to be estimated
+($\iota$, $\rho$). $\iota$ represents the parameter for Gross Primary Production
+(hereafter GPP), implying a linear relationship between GPP and irradiation, and $\rho$ represents
+the parameter for Respiration (hereafter R), implying a log-linear relationship
+between R and temperature; $O_{s}$ is the equilibrium DO concentration at
+supplied conditions; $K^{\ast}_{t}$ is a stochastic node,
+with $K^{\ast}_{t} \sim N(K_{t}, \sigma_{k})$, where $K_{t}$ is the gas exchange
+coefficient, and $\sigma_{k}$ the precision thereof; the default precision
+is $1/(0.1 \times K_{t})$; finally, $z_{t}$ is the mixed layer depth.
+
+From equation~\ref{eq:sys1}, we can see that if $k_{t} = 0$ (i.e., no gas exchange
+with the atmosphere), the oxygen levels in the water are modeled to be additive for each
+time step. Furthermore, we can see that the gas exchange coefficient is dependent
+on mixed layer depth (equation~\ref{eq:sys3}).
+
+While the estimate of gas exchange coefficient serves as prior information for $K$,
+priors for the fitted GPP and R parameters ($\iota$ and $\rho$) can also
+be defined. The default priors for $\iota$ and $\rho$ are normal distributions
+with mean 0 and variance $1 \times 10^{5}$
+($\iota_{t} \sim N(0,10^{5})$, $\rho_{t} \sim N(0,10^{5})$) and were used in our case.
+
+To estimate metabolism, the median of the posterior distribution of the parameters
+is used as a scalar estimate. Daily GPP and R estimates represent an integrated
+estimate of these scalars over a 24-hour window. Uncertainty of GPP and R
+estimates is expressed as the posterior standard deviation of the respective
+parameters ($\iota$ and $\rho$), multiplied by the square root of the corresponding
+covariate ($I$ and $\ln{T}$). NEP is the sum of GPP and R, and the standard deviation
+of NEP is the sum of the standard deviations for GPP and R.
+
+In total, 5 parameters are fit in this Bayesian model, namely $\iota$, $\rho$,
+$K$, $\tau_{v}$, and $\tau_{w}$. For all parameters except $K$, (default) minimally
+informative priors were used. Regarding $K$, as described above, its estimate
+(from the separate gas transfer coefficient model) serves as a prior.
+
+Estimates of the posterior distribution of the parameters were sampled using
+Gibbs sampling implemented in Just Another Gibbs Sampler
+(\href{https://sourceforge.net/projects/mcmc-jags/files/}{JAGS}). Prior to running
+the Bayesian model, it must be installed.
+
+\subsection{Sensitivity analysis for mixed layer depth} \label{subsec:sens}
+
+As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
+data to estimate mixed layer depth. An initial approach to deal with that problem
+was to investigate the effect of different mixed layer depths on the daily metabolism
+estimates. For that purpose, we selected a few lakes for different monitoring
+periods (2021, 2022, 2023) and assessed the impact of various, constant
+mixed layer depths over time on the metabolism results.
+
+<<sensanal, results = "asis", echo=FALSE>>=
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../../project_21/data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../../project_21/data/metadata_metabolism_analysis/metadata_2021.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "ERL85")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
+# Isolate the desired period for metabolism estimation
+all <- all[c(121:5160),]
+
+# choose desired period for the metadata
+meta <- meta[c(1:169),]
+
+# rename
+meta <- setnames(meta,c("datetime", "dsr_cor", "wsp"))
+
+meta <- meta %>%
+  mutate(datetime = as.POSIXct(format(datetime, format = "%Y-%m-%d %H:01:00", tz = "UTC"), tz = "UTC"))
+
+# Create a new inflated dataset with measurements every 2 minutes
+# The hourly mean will be assigned to every observation (2min-interval) within that hour
+meta_ext <- meta %>%
+  complete(datetime = seq(from = min(datetime), to = max(datetime), by = "2 min"))
+
+# Fill the missing wind speed and irradiation values with the corresponding hourly values using 'fill'
+meta_ext <- meta_ext %>%
+  fill(wsp, .direction = "up") %>%
+  fill(dsr_cor, .direction = "up")
+
+# Shift wind speed and irradiation one row up
+meta_ext <- meta_ext %>%
+  mutate(wsp = lead(wsp, default = last(wsp))) %>%
+  mutate(dsr_cor = lead(dsr_cor, default = last(dsr_cor)))
+
+# Ommit last row (not included in our timeseries)
+meta_ext <- meta_ext[-nrow(meta_ext), ]
+
+# Reset row names for the final result
+rownames(meta_ext) <- NULL
+
+# Step 2: merge the 2 datasets -------------------------------------------------
+all <- merge(meta_ext, all, by = "datetime")
+
+# Step 3: Missing data imputation ----------------------------------------------
+# We need a complete ODO_mgL timeseries. Therefore we will impute the missing values
+# here, with the package "imputeTS", which is specifically designed to impute time-series
+# observations.
+
+colSums(is.na(all))
+
+# Make a timeseries object
+ts <- ts(all$do.obs, frequency = 720)
+
+# Impute with imputeTS
+imp_all <- na_ma(ts) # use this function!
+imp_all <- data.table(imp_all)
+imp_all$datetime <- all$datetime
+
+# Check for missing values in the imputed dataset
+sum(is.na(imp_all)) # No missing values anymore
+
+# Check imputation by plotting the original and the imputed dataset
+plot(x = all$datetime, y = all$do.obs, type = "l", col = "blue", lwd = 2)
+lines(x = imp_all$datetime, y = imp_all$imp_all, type = "l",
+      col = rgb(1, 0, 0, alpha = 0.3), lwd = 2)
+# The imputation worked very well!
+
+# Replace original column with imputed column
+all$do.obs <- imp_all$imp_all
+sum(is.na(all))
+
+# Step 4: Model choice ---------------------------------------------------------
+# Gas transfer coefficient model: kvachon()
+# - needs wind speed, sensor height, and lake area
+
+# Lake metabolism model: metab.bayesian()
+# Most flexible model
+
+# Step 5: Calculate k600 using the Cole method ---------------------------------
+
+# This function needs specific column names
+all$wnd <- all$wsp
+all$wsp <- NULL
+
+# Normalize wind to 10m sensor height
+wind.scale <- wind.scale(all, wnd.z = 3.05)
+
+all <- merge(all, wind.scale, by = "datetime")
+
+all$wnd <- all$wnd_10
+all$wnd_10 <- NULL
+
+# Also only the 2 columns of interest, otherwise it gets confused
+all.600 <- all[,c("datetime","wnd")]
+k600.vachon <- k.vachon(all.600, lake.area = 18200)
+
+# Merge
+all <- merge(all, k600.vachon, by = "datetime")
+
+# Step 6: Calculate gas-specific k600 ------------------------------------------
+
+kgas <- k600.2.kGAS(all)
+
+# Merge
+all <- merge(all, kgas, by = "datetime")
+
+# only keep k.gas
+all$k600 <- NULL
+
+# Step 7: Calculate dissolved oxygen saturated (do.sat) ------------------------
+
+# I know that the sonde has do.sat measurements, but I have more faith
+# in the authors of this paper to calculate a more accurate do.sat then the
+# sonde-intern calculations.
+
+o2.sat <- o2.at.sat(all[,c('datetime','wtr')])
+
+# Merge
+all <- merge(all, o2.sat, by = "datetime")
+
+# Step 8: Derive photosynthetically active radiation (par) from shortwave irradiation (sw) ----
+# Here, I take the downwelling shortwave irradiation (tilt corrected) from the
+# QAS_L automated weather station a couple of kilometers away from Narsarsuaq
+# It's the closest weather station measuring this parameter, that I could find.
+
+# Derive par from sw
+par <- sw.to.par(all, sw.col = "dsr_cor")
+rownames(par) <- NULL
+
+# Merge
+all <- merge(all, par[,c("datetime", "par")], by = "datetime")
+
+# Step 9: Calculate Actively mixed layer depth (z.mix) -------------------------
+
+################################################################################
+# Set different mixed layer depths of sensitivity analysis
+# For some reason, metab.bayesian does not recognize z.mix columns
+# if they are not named "z.mix", hence I have to create a dataset for each z.mix
+################################################################################
+
+all2 <- all
+all2$z.mix <- 0.5
+
+all3 <-all
+all3$z.mix <- 1
+
+all4 <- all
+all4$z.mix <- 2
+
+all5 <- all
+all5$z.mix <- 3
+
+all6 <- all
+all6$z.mix <- 4
+
+all7 <- all
+all7$z.mix <- 5
+
+all8 <- all
+all8$z.mix <- 6
+
+all9 <- all
+all9$z.mix <- 7
+
+# Step 10: Fit model -----------------------------------------------------------
+
+# Choose columns to keep
+all2 <- all2[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all3 <- all3[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all4 <- all4[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all5 <- all5[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all6 <- all6[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all7 <- all7[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all8 <- all8[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all9 <- all9[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+
+# Mixed layer depth 0.5m over the whole observation period
+bayesian.res_0.5 <- metab(all2, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                          irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                          do.sat.name = "do.sat")
+
+# Mixed layer depth 1m over the whole observation period
+bayesian.res_1 <- metab(all3, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                        do.sat.name = "do.sat")
+
+# Mixed layer depth 2m over the whole observation period
+bayesian.res_2 <- metab(all4, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                        do.sat.name = "do.sat")
+
+# Mixed layer depth 3m over the whole observation period
+bayesian.res_3 <- metab(all5, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                        do.sat.name = "do.sat")
+
+# Mixed layer depth 0.5m over the whole observation period
+bayesian.res_4 <- metab(all6, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                          irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                          do.sat.name = "do.sat")
+
+# Mixed layer depth 1m over the whole observation period
+bayesian.res_5 <- metab(all7, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                        do.sat.name = "do.sat")
+
+# Mixed layer depth 2m over the whole observation period
+bayesian.res_6 <- metab(all8, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                        do.sat.name = "do.sat")
+
+# Mixed layer depth 3m over the whole observation period
+bayesian.res_7 <- metab(all9, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                        do.sat.name = "do.sat")
+
+# Get standard deviations of estimates
+bayesian.sd_0.5 <- attr(bayesian.res_0.5, "metab.sd")
+bayesian.sd_1 <- attr(bayesian.res_1, "metab.sd")
+bayesian.sd_2 <- attr(bayesian.res_2, "metab.sd")
+bayesian.sd_3 <- attr(bayesian.res_3, "metab.sd")
+bayesian.sd_4 <- attr(bayesian.res_4, "metab.sd")
+bayesian.sd_5 <- attr(bayesian.res_5, "metab.sd")
+bayesian.sd_6 <- attr(bayesian.res_6, "metab.sd")
+bayesian.sd_7 <- attr(bayesian.res_7, "metab.sd")
+
+# Create a date variable
+bayesian.res_0.5$Date <- as.Date(paste(bayesian.res_0.5$year, "-", bayesian.res_0.5$doy, sep = ""), format = "%Y-%j")
+bayesian.res_1$Date <- as.Date(paste(bayesian.res_1$year, "-", bayesian.res_1$doy, sep = ""), format = "%Y-%j")
+bayesian.res_2$Date <- as.Date(paste(bayesian.res_2$year, "-", bayesian.res_2$doy, sep = ""), format = "%Y-%j")
+bayesian.res_3$Date <- as.Date(paste(bayesian.res_3$year, "-", bayesian.res_3$doy, sep = ""), format = "%Y-%j")
+bayesian.res_4$Date <- as.Date(paste(bayesian.res_4$year, "-", bayesian.res_4$doy, sep = ""), format = "%Y-%j")
+bayesian.res_5$Date <- as.Date(paste(bayesian.res_5$year, "-", bayesian.res_5$doy, sep = ""), format = "%Y-%j")
+bayesian.res_6$Date <- as.Date(paste(bayesian.res_6$year, "-", bayesian.res_6$doy, sep = ""), format = "%Y-%j")
+bayesian.res_7$Date <- as.Date(paste(bayesian.res_7$year, "-", bayesian.res_7$doy, sep = ""), format = "%Y-%j")
+
+# Select columns to keep
+bayesian.res_0.5 <- bayesian.res_0.5[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_1 <- bayesian.res_1[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_2 <- bayesian.res_2[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_3 <- bayesian.res_3[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_4 <- bayesian.res_4[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_5 <- bayesian.res_5[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_6 <- bayesian.res_6[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_7 <- bayesian.res_7[,c("Date", "GPP", "R", "NEP")]
+
+# Create a date variable
+bayesian.sd_0.5$Date <- as.Date(paste(bayesian.sd_0.5$year, "-", bayesian.sd_0.5$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_1$Date <- as.Date(paste(bayesian.sd_1$year, "-", bayesian.sd_1$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_2$Date <- as.Date(paste(bayesian.sd_2$year, "-", bayesian.sd_2$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_3$Date <- as.Date(paste(bayesian.sd_3$year, "-", bayesian.sd_3$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_4$Date <- as.Date(paste(bayesian.sd_4$year, "-", bayesian.sd_4$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_5$Date <- as.Date(paste(bayesian.sd_5$year, "-", bayesian.sd_5$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_6$Date <- as.Date(paste(bayesian.sd_6$year, "-", bayesian.sd_6$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_7$Date <- as.Date(paste(bayesian.sd_7$year, "-", bayesian.sd_7$doy, sep = ""), format = "%Y-%j")
+
+# Select columns to keep
+bayesian.sd_0.5 <- bayesian.sd_0.5[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_1 <- bayesian.sd_1[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_2 <- bayesian.sd_2[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_3 <- bayesian.sd_3[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_4 <- bayesian.sd_4[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_5 <- bayesian.sd_5[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_6 <- bayesian.sd_6[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_7 <- bayesian.sd_7[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+
+# Merge
+bayesian.merge_0.5 <- merge(bayesian.res_0.5, bayesian.sd_0.5, by = "Date")
+bayesian.merge_1 <- merge(bayesian.res_1, bayesian.sd_1, by = "Date")
+bayesian.merge_2 <- merge(bayesian.res_2, bayesian.sd_2, by = "Date")
+bayesian.merge_3 <- merge(bayesian.res_3, bayesian.sd_3, by = "Date")
+bayesian.merge_4 <- merge(bayesian.res_4, bayesian.sd_4, by = "Date")
+bayesian.merge_5 <- merge(bayesian.res_5, bayesian.sd_5, by = "Date")
+bayesian.merge_6 <- merge(bayesian.res_6, bayesian.sd_6, by = "Date")
+bayesian.merge_7 <- merge(bayesian.res_7, bayesian.sd_7, by = "Date")
+
+# create Z.mix variable identifier
+bayesian.merge_0.5$z.mix <- "0.5m"
+bayesian.merge_1$z.mix <- "1m"
+bayesian.merge_2$z.mix <- "2m"
+bayesian.merge_3$z.mix <- "3m"
+bayesian.merge_4$z.mix <- "4m"
+bayesian.merge_5$z.mix <- "5m"
+bayesian.merge_6$z.mix <- "6m"
+bayesian.merge_7$z.mix <- "7m"
+
+# Merge
+bayesian.merge.all <- rbind(bayesian.merge_0.5, bayesian.merge_1,
+                            bayesian.merge_2, bayesian.merge_3, bayesian.merge_4,
+                            bayesian.merge_5, bayesian.merge_6, bayesian.merge_7)
+
+# Step 11: Visualize the results -----------------------------------------------
+
+# GPP
+p1 = ggplot(data = bayesian.merge.all, aes(x=Date, y=GPP, color=z.mix)) + theme_light() +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "0.5m")) +
+  geom_errorbar(aes(ymin = GPP-GPPsd, ymax = GPP+GPPsd), width = 0.12) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "1m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "2m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "3m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "4m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "5m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "6m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "7m")) +
+  ylab(expression(paste("GPP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))
+
+# R
+p2 = ggplot(data = bayesian.merge.all, aes(x=Date, y=R, color=z.mix)) + theme_light() +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "0.5m")) +
+  geom_errorbar(aes(ymin = R-Rsd, ymax = R+Rsd), width = 0.12) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "1m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "2m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "3m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "4m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "5m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "6m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "7m"))
+  ylab(expression(paste("R (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))
+
+# NEP
+p3 = ggplot(data = bayesian.merge.all, aes(x=Date, y=NEP, color=z.mix)) + theme_light() +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "0.5m")) +
+  geom_errorbar(aes(ymin = NEP-NEPsd, ymax = NEP+NEPsd), width = 0.12) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "1m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "2m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "3m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "4m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "5m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "6m")) +
+  geom_line(data = subset(bayesian.merge.all, z.mix == "7m"))
+  ylab(expression(paste("NEP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))
+
+# Plots of ecosystem parameters
+p4 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=do.obs, x=datetime), color = "gray17") +
+  rremove("xlab") +
+  ylab(expression(paste("DO (mg L",NULL^-1,")")))
+
+p5 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=do.sat, x=datetime), color = "gray17") +
+  rremove("xlab") +
+  ylab(expression(paste("Equilibrium\nDO concentration (mg L",NULL^-1,")")))
+
+p6 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=wtr, x=datetime), color = "gray17") +
+  rremove("xlab") +
+  ylab("Temperature in °C")
+
+p7 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=par, x=datetime), color = "gray17") +
+  rremove("xlab") +
+  ylab(expression(paste("PAR (",mu,"mol m",NULL^-2," s",NULL^-1,")")))
+
+p8 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=k.gas, x=datetime), color = "gray17") +
+  rremove("xlab") +
+  ylab(expression(paste("Gas and temperature specific\ngas transfer coefficient (m",NULL^-1,")")))
+
+p9 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=wnd, x=datetime), color = "gray17") +
+  rremove("xlab") +
+  ylab("Wind speed (m/s)")
+
+fig2 <- ggarrange(p1 + rremove("xlab"), p2 + rremove("xlab"), p3 + rremove("xlab"),
+                  p4 + rremove("xlab"), p5 + rremove("xlab"), p6 + rremove("xlab"),
+                  p7 + rremove("xlab"), p8 + rremove("xlab"), p9 + rremove("xlab"),
+                  nrow=5, ncol = 2,  common.legend = TRUE, legend = "right")
+
+annotate_figure(fig2)
+@
+
 \end{document}

### 2024-12-10 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.tex
Work on manuscript

@@
 % latex table generated in R 4.4.1 by xtable 1.8-4 package
-% Thu Dec  5 16:44:34 2024
+% Tue Dec 10 16:08:53 2024
 \begin{table}[ht]
@@
 \begin{gather}
-x^{2} \label{eq:sys1}\\
-x^{3} \label{eq:sys2}
+\alpha^{\ast}_{t} =
+\begin{cases}
+\alpha_{t-1} + \alpha_{t}, & \text{if } k_{t} = 0, \\
+\frac{\alpha_{t}}{k_{t-1}} + \frac{-\exp{(-k_{t-1})}\alpha_{t}}{k_{t-1}} +
+\exp{(-k_{t-1})}\alpha_{t-1}, & \text{otherwise},
+\end{cases} \label{eq:sys1} \\
+\alpha_{t} = \mathbf{X}_{t-1}\bm{\beta} + k_{t-1}O_{s,t-1}, \label{eq:sys2} \\
+k_{t} = \frac{K^{\ast}_{t}\Delta t}{z_{t}}. \label{eq:sys3}
 \end{gather}
 
+In this equation structure, $k_{t}$ is the coefficient of gas exchange;
+$\mathbf{X}$ is an $n \times 2$ matrix of predictor variables with $I$
+(irradiation in arbitrary light units) in the first column and $\ln{T}$ (\textdegree{}$C$) in the second
+column; $\bm{\beta}$ is a $2 \times 1$ vector of parameters to be estimated
+($\iota$, $\rho$). $\iota$ represents the parameter for Gross Primary Production
+(hereafter GPP), implying a linear relationship between GPP and irradiation, and $\rho$ represents
+the parameter for Respiration (hereafter R), implying a log-linear relationship
+between R and temperature; $O_{s}$ is the equilibrium DO concentration at
+supplied conditions; $K^{\ast}_{t}$ is a stochastic node,
+with $K^{\ast}_{t} \sim N(K_{t}, \sigma_{k})$, where $K_{t}$ is the gas exchange
+coefficient, and $\sigma_{k}$ the precision thereof; the default precision
+is $1/(0.1 \times K_{t})$; finally, $z_{t}$ is the mixed layer depth.
+
+From equation~\ref{eq:sys1}, we can see that if $k_{t} = 0$ (i.e., no gas exchange
+with the atmosphere), the oxygen levels in the water are modeled to be additive for each
+time step. Furthermore, we can see that the gas exchange coefficient is dependent
+on mixed layer depth (equation~\ref{eq:sys3}).
+
+While the estimate of gas exchange coefficient serves as prior information for $K$,
+priors for the fitted GPP and R parameters ($\iota$ and $\rho$) can also
+be defined. The default priors for $\iota$ and $\rho$ are normal distributions
+with mean 0 and variance $1 \times 10^{5}$
+($\iota_{t} \sim N(0,10^{5})$, $\rho_{t} \sim N(0,10^{5})$) and were used in our case.
+
+To estimate metabolism, the median of the posterior distribution of the parameters
+is used as a scalar estimate. Daily GPP and R estimates represent an integrated
+estimate of these scalars over a 24-hour window. Uncertainty of GPP and R
+estimates is expressed as the posterior standard deviation of the respective
+parameters ($\iota$ and $\rho$), multiplied by the square root of the corresponding
+covariate ($I$ and $\ln{T}$). NEP is the sum of GPP and R, and the standard deviation
+of NEP is the sum of the standard deviations for GPP and R.
+
+In total, 5 parameters are fit in this Bayesian model, namely $\iota$, $\rho$,
+$K$, $\tau_{v}$, and $\tau_{w}$. For all parameters except $K$, (default) minimally
+informative priors were used. Regarding $K$, as described above, its estimate
+(from the separate gas transfer coefficient model) serves as a prior.
+
+Estimates of the posterior distribution of the parameters were sampled using
+Gibbs sampling implemented in Just Another Gibbs Sampler
+(\href{https://sourceforge.net/projects/mcmc-jags/files/}{JAGS}). Prior to running
+the Bayesian model, it must be installed.
+
+\subsection{Sensitivity analysis for mixed layer depth} \label{subsec:sens}
+
+As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
+data to estimate mixed layer depth. An initial approach to deal with that problem
+was to investigate the effect of different mixed layer depths on the daily metabolism
+estimates. For that purpose, we selected a few lakes for different monitoring
+periods (2021, 2022, 2023) and assessed the impact of various, constant
+mixed layer depths over time on the metabolism results.
+
+\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Lade nötiges Paket: grid}}\end{kframe}datetime  dsr_cor      wsp     Pond   do.obs      wtr 
+       0        0        0        0      154        0 
+[1] 0
+
+{\centering \includegraphics[width=\maxwidth]{plots/psensanal-1}
+
+}
+
+[1] 0
+[1] "Points removed due to incomplete day or duplicated time step: 0"
+[1] "NA's added to fill in time series: 0"
+[1] "using allK model"
+\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# module glm loaded}}\end{kframe}Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16998
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16988
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16925
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17003
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17076
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16921
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16947
+
+Initializing model
+
+[1] "Points removed due to incomplete day or duplicated time step: 0"
+[1] "NA's added to fill in time series: 0"
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16998
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16988
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16925
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17003
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17076
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16921
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16947
+
+Initializing model
+
+[1] "Points removed due to incomplete day or duplicated time step: 0"
+[1] "NA's added to fill in time series: 0"
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16998
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16988
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16925
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17003
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17076
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16921
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16947
+
+Initializing model
+
+[1] "Points removed due to incomplete day or duplicated time step: 0"
+[1] "NA's added to fill in time series: 0"
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16998
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16988
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16925
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17003
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17076
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16921
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16947
+
+Initializing model
+
+[1] "Points removed due to incomplete day or duplicated time step: 0"
+[1] "NA's added to fill in time series: 0"
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16998
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16988
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16925
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17003
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17076
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16921
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16947
+
+Initializing model
+
+[1] "Points removed due to incomplete day or duplicated time step: 0"
+[1] "NA's added to fill in time series: 0"
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16998
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16988
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16925
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17003
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17076
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16921
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16947
+
+Initializing model
+
+[1] "Points removed due to incomplete day or duplicated time step: 0"
+[1] "NA's added to fill in time series: 0"
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16998
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16988
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16925
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17003
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17076
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16921
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16947
+
+Initializing model
+
+[1] "Points removed due to incomplete day or duplicated time step: 0"
+[1] "NA's added to fill in time series: 0"
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16998
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16988
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16925
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17003
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 17076
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16921
+
+Initializing model
+
+[1] "using allK model"
+Compiling model graph
+   Resolving undeclared variables
+   Allocating nodes
+Graph information:
+   Observed stochastic nodes: 719
+   Unobserved stochastic nodes: 1442
+   Total graph size: 16947
+
+Initializing model
+
+$y
+expression(paste("R (", O[2], " in mg L", NULL^-1, " day", NULL^-1, 
+    ")"))
+
+attr(,"class")
+[1] "labels"
+$y
+expression(paste("NEP (", O[2], " in mg L", NULL^-1, " day", 
+    NULL^-1, ")"))
+
+attr(,"class")
+[1] "labels"
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}\end{kframe}
+
+{\centering \includegraphics[width=\maxwidth]{plots/psensanal-2}
+
+}
+
 \end{document}

### 2024-12-11 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Work on manuscript

--- 2024-12-09 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
@@
 to estimating lake metabolism,
-namely do.sat, k.gas, par, and z.mix.
+namely do.sat, k.gas, par, and z.mix. The necessary functions are provided by the
+\texttt{LakeMetabolizer} package.
 do.sat was derived by using the function \texttt{o2.at.sat}, which calculates
-the equilibrium DO concentration of oxygen in water at supplied conditions.
+the equilibrium DO concentration in water at supplied conditions.
 To estimate k.gas, a gas transfer coefficient model must be fit.
@@
 Prairie in 2013 \citep{Vachon:2013}. This model not only takes wind into
-consideration, but also lake area.
+consideration, but also lake area, and is implemented in the function
+\texttt{k.vachon}. Notably, wind speed has to be normalized
+to 10 $m$ sensor height before fitting any gas exchange model, which is achieved
+with the function \texttt{wind.scale}.
 All models of gas exchange 
@@
 After estimating k\textsubscript{600}, it must be transformed to k.gas by using the
-function \texttt{k600.2.kGAS} provided by the \texttt{LakeMetabolizer}
-package. par was derived from shortwave irradiation,
+function \texttt{k600.2.kGAS}. par was derived from shortwave irradiation,
 which we had available (see section \nameref{subsec:source}).
@@
 \begin{gather}
-x^{2} \label{eq:sys1}\\
-x^{3} \label{eq:sys2}
+\alpha^{\ast}_{t} =
+\begin{cases}
+\alpha_{t-1} + \alpha_{t}, & \text{if } k_{t} = 0, \\
+\frac{\alpha_{t}}{k_{t-1}} + \frac{-\exp{(-k_{t-1})}\alpha_{t}}{k_{t-1}} +
+\exp{(-k_{t-1})}\alpha_{t-1}, & \text{otherwise},
+\end{cases} \label{eq:sys1} \\
+\alpha_{t} = \mathbf{X}_{t-1}\bm{\beta} + k_{t-1}O_{s,t-1}, \label{eq:sys2} \\
+k_{t} = \frac{K^{\ast}_{t}\Delta t}{z_{t}}. \label{eq:sys3}
 \end{gather}
 
+In this equation structure, $k_{t}$ is the coefficient of gas exchange;
+$\mathbf{X}$ is an $n \times 2$ matrix of predictor variables with $I$
+(irradiation in arbitrary light units) in the first column and $\ln{T}$ (\textdegree{}$C$) in the second
+column; $\bm{\beta}$ is a $2 \times 1$ vector of parameters to be estimated
+($\iota$, $\rho$). $\iota$ represents the parameter for Gross Primary Production
+(hereafter GPP), implying a linear relationship between GPP and irradiation, and $\rho$ represents
+the parameter for Respiration (hereafter R), implying a log-linear relationship
+between R and temperature; $O_{s}$ is the equilibrium DO concentration at
+supplied conditions; $K^{\ast}_{t}$ is a stochastic node,
+with $K^{\ast}_{t} \sim N(K_{t}, \sigma_{k})$, where $K_{t}$ is the gas exchange
+coefficient, and $\sigma_{k}$ the precision thereof; the default precision
+is $1/(0.1 \times K_{t})$; finally, $z_{t}$ is the mixed layer depth.
+
+From equation~\ref{eq:sys1}, we can see that if $k_{t} = 0$ (i.e., no gas exchange
+with the atmosphere), the oxygen levels in the water are modeled to be additive for each
+time step. Furthermore, we can see that the gas exchange coefficient is dependent
+on mixed layer depth (equation~\ref{eq:sys3}).
+
+While the estimate of gas exchange coefficient serves as prior information for $K$,
+priors for the fitted GPP and R parameters ($\iota$ and $\rho$) can also
+be defined. The default priors for $\iota$ and $\rho$ are normal distributions
+with mean 0 and variance $1 \times 10^{5}$
+($\iota_{t} \sim N(0,10^{5})$, $\rho_{t} \sim N(0,10^{5})$) and were used in our case.
+
+To estimate metabolism, the median of the posterior distribution of the parameters
+is used as a scalar estimate. Daily GPP and R estimates represent an integrated
+estimate of these scalars over a 24-hour window. Uncertainty of GPP and R
+estimates is expressed as the posterior standard deviation of the respective
+parameters ($\iota$ and $\rho$), multiplied by the square root of the corresponding
+covariate ($I$ and $\ln{T}$). NEP is the sum of GPP and R, and the standard deviation
+of NEP is the sum of the standard deviations for GPP and R.
+
+In total, 5 parameters are fit in this Bayesian model, namely $\iota$, $\rho$,
+$K$, $\tau_{v}$, and $\tau_{w}$. For all parameters except $K$, (default) minimally
+informative priors were used. Regarding $K$, as described above, its estimate
+(from the separate gas transfer coefficient model) serves as a prior.
+
+Estimates of the posterior distribution of the parameters were sampled using
+Gibbs sampling implemented in Just Another Gibbs Sampler
+(\href{https://sourceforge.net/projects/mcmc-jags/files/}{JAGS}). Prior to running
+the Bayesian model, it must be installed.
+
+\subsection{Sensitivity analysis for mixed layer depth} \label{subsec:sens}
+
+As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
+data to estimate mixed layer depth. An initial approach to deal with that problem
+was to investigate the effect of different mixed layer depths on the daily metabolism
+estimates. For that purpose, we selected a few lakes for different monitoring
+periods (2021, 2022, 2023) and assessed the impact of various, constant
+mixed layer depths over time on the metabolism results.
+
 \end{document}

### 2024-12-11 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.tex
Work on manuscript

@@
 % latex table generated in R 4.4.1 by xtable 1.8-4 package
-% Tue Dec 10 16:08:53 2024
+% Wed Dec 11 09:32:21 2024
 \begin{table}[ht]
@@
 to estimating lake metabolism,
-namely do.sat, k.gas, par, and z.mix.
+namely do.sat, k.gas, par, and z.mix. The necessary functions are provided by the
+\texttt{LakeMetabolizer} package.
 do.sat was derived by using the function \texttt{o2.at.sat}, which calculates
@@
 Prairie in 2013 \citep{Vachon:2013}. This model not only takes wind into
-consideration, but also lake area. Notably, wind speed has to be normalized
+consideration, but also lake area, and is implemented in the function
+\texttt{k.vachon}. Notably, wind speed has to be normalized
 to 10 $m$ sensor height before fitting any gas exchange model, which is achieved
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Lade nötiges Paket: grid}}\end{kframe}datetime  dsr_cor      wsp     Pond   do.obs      wtr 
-       0        0        0        0      154        0 
-[1] 0
-
-{\centering \includegraphics[width=\maxwidth]{plots/psensanal-1}
-
-}
-
-[1] 0
-[1] "Points removed due to incomplete day or duplicated time step: 0"
-[1] "NA's added to fill in time series: 0"
-[1] "using allK model"
-\begin{kframe}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# module glm loaded}}\end{kframe}Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16998
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16988
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16925
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17003
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17076
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16921
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16947
-
-Initializing model
-
-[1] "Points removed due to incomplete day or duplicated time step: 0"
-[1] "NA's added to fill in time series: 0"
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16998
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16988
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16925
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17003
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17076
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16921
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16947
-
-Initializing model
-
-[1] "Points removed due to incomplete day or duplicated time step: 0"
-[1] "NA's added to fill in time series: 0"
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16998
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16988
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16925
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17003
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17076
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16921
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16947
-
-Initializing model
-
-[1] "Points removed due to incomplete day or duplicated time step: 0"
-[1] "NA's added to fill in time series: 0"
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16998
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16988
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16925
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17003
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17076
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16921
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16947
-
-Initializing model
-
-[1] "Points removed due to incomplete day or duplicated time step: 0"
-[1] "NA's added to fill in time series: 0"
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16998
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16988
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16925
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17003
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17076
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16921
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16947
-
-Initializing model
-
-[1] "Points removed due to incomplete day or duplicated time step: 0"
-[1] "NA's added to fill in time series: 0"
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16998
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16988
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16925
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17003
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17076
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16921
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16947
-
-Initializing model
-
-[1] "Points removed due to incomplete day or duplicated time step: 0"
-[1] "NA's added to fill in time series: 0"
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16998
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16988
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16925
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17003
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17076
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16921
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16947
-
-Initializing model
-
-[1] "Points removed due to incomplete day or duplicated time step: 0"
-[1] "NA's added to fill in time series: 0"
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16998
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16988
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16925
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17003
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 17076
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16921
-
-Initializing model
-
-[1] "using allK model"
-Compiling model graph
-   Resolving undeclared variables
-   Allocating nodes
-Graph information:
-   Observed stochastic nodes: 719
-   Unobserved stochastic nodes: 1442
-   Total graph size: 16947
-
-Initializing model
-
-$y
-expression(paste("R (", O[2], " in mg L", NULL^-1, " day", NULL^-1, 
-    ")"))
-
-attr(,"class")
-[1] "labels"
-$y
-expression(paste("NEP (", O[2], " in mg L", NULL^-1, " day", 
-    NULL^-1, ")"))
-
-attr(,"class")
-[1] "labels"
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call(C\_textBounds, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in grid.Call.graphics(C\_text, as.graphicsAnnot(x\$label), x\$x, x\$y, : font metrics unknown for character 0x0a in encoding cp1252}}\end{kframe}
-
-{\centering \includegraphics[width=\maxwidth]{plots/psensanal-2}
-
-}
-
 \end{document}

### 2024-12-11 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Work on manuscript

@@
 % R specifications
-<<include = FALSE>>=
+<<setup, include = FALSE>>=
 # knitr
@@
                echo = FALSE, 
-               results = 'hide',
-               fig.height = 4.5,
                fig.align = "center",
@@
 \begin{cases}
-\alpha_{t-1} + \alpha_{t}, & \text{if } k_{t} = 0, \\
+\alpha_{t-1} + \alpha_{t} & \text{if } k_{t} = 0, \\
 \frac{\alpha_{t}}{k_{t-1}} + \frac{-\exp{(-k_{t-1})}\alpha_{t}}{k_{t-1}} +
-\exp{(-k_{t-1})}\alpha_{t-1}, & \text{otherwise},
+\exp{(-k_{t-1})}\alpha_{t-1} & \text{otherwise},
 \end{cases} \label{eq:sys1} \\
@@
 As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
-data to estimate mixed layer depth. An initial approach to deal with that problem
-was to investigate the effect of different mixed layer depths on the daily metabolism
+data to estimate mixed layer depth. An initial approach to assess this issue
+was to investigate the effect of different mixed layer depths on daily metabolism
 estimates. For that purpose, we selected a few lakes for different monitoring
-periods (2021, 2022, 2023) and assessed the impact of various, constant
-mixed layer depths over time on the metabolism results.
+periods (2021, 2022, 2023). Notably, mixed layer
+was held constant, which is rarely the case in reality.
+In Figure~\ref{fig:sens}, an example of a sensitivity analysis for lake
+B1P1 in 2021 is depicted. Plots A-C depict the daily GPP, R, and NEP estimates
+for different mixed layer depths. For each mixed layer value, a separate model
+was fitted, holding all other covariates equal.
+Apparently, mixed layer depth substantially
+impacts respiration, where a smaller mixed layer depth is associated with
+higher (more negative) R. In contrast, GPP is barely affected by mixed
+layer depth. Plots D-H show the input variables required to fit the metabolism
+models, apart from mixed layer depth. Since mixed layer particularly
+effects daily R estimates, careful consideration with regards to overcoming
+this limitation is required. Notably, the effect of variation in mixed layer
+depth was consistent across most lakes and monitoring periods
+
+<<sensanal1, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE>>=
+# Packages ad functions from Moritz Luehrig's paper
+source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")
+
+# Estimating lake metabolism with free-water oxygen
+# See "report_analysis_metabolism_B3P3_2022" for further details
+require(LakeMetabolizer)
+
+# For plotting
+require(GGally)
+
+# Imputation of NAs for time-series (our NAs are due to outlier processing)
+require(imputeTS)
+
+# For Bayesian lake metabolism modeling
+require(R2jags) # Also, installing JAGS is necessary under
+# http://www.sourceforge.net/projects/mcmc-jags/files
+
+require(ggpubr)
+require(grid) # Arranging multiple plots
+require(grDevices) # Saving png files
+
+# This is our complete dataset of the sondes measurements 2021
+# Measurement Interval: 2 minutes
+all <- fread("../../project_21/data/processed_data_sondes/ponds_sonde_data_all.txt")
+
+# Importing the metadata
+# Wind and irradiation
+# Measurement Interval: 1 hour, hourly averages
+# Source: QAS_L automated weather station near Narsarsuaq
+# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
+# wind sensor height: 2.65 + 0.4 = ca 3.05m
+meta <- fread("../../project_21/data/metadata_metabolism_analysis/metadata_2021.txt")
+
+# Step 1: data formatting ------------------------------------------------------
+
+# Select columns to keep from our time series
+all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]
+
+# Select Pond B1P1 (Treatment: Fish)
+all <- subset(all, Pond == "B1P1")
+
+# Rename
+all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))
+
+# Isolate the desired period (described in the introduction)
+# Unfortunately, B1P1 had a huge data-gap so we can only estimate
+# metabolism before (we have 4 complete days)
+all <- all[c(121:3000),]
+
+# choose desired period for the metadata
+meta <- meta[c(1:97),]
+
+# rename
+meta <- setnames(meta,c("datetime", "dsr_cor", "wsp"))
+
+meta <- meta %>%
+  mutate(datetime = as.POSIXct(format(datetime, format = "%Y-%m-%d %H:01:00", tz = "UTC"), tz = "UTC"))
+
+# Create a new inflated dataset with measurements every 2 minutes
+# The hourly mean will be assigned to every observation (2min-interval) within that hour
+meta_ext <- meta %>%
+  complete(datetime = seq(from = min(datetime), to = max(datetime), by = "2 min"))
+
+# Fill the missing wind speed and irradiation values with the corresponding hourly values using 'fill'
+meta_ext <- meta_ext %>%
+  fill(wsp, .direction = "up") %>%
+  fill(dsr_cor, .direction = "up")
+
+# Shift wind speed and irradiation one row up
+meta_ext <- meta_ext %>%
+  mutate(wsp = lead(wsp, default = last(wsp))) %>%
+  mutate(dsr_cor = lead(dsr_cor, default = last(dsr_cor)))
+
+# Ommit last row (not included in our timeseries)
+meta_ext <- meta_ext[-nrow(meta_ext), ]
+
+# Reset row names for the final result
+rownames(meta_ext) <- NULL
+
+# Step 2: merge the 2 datasets -------------------------------------------------
+all <- merge(meta_ext, all, by = "datetime")
+
+# Step 3: Missing data imputation ----------------------------------------------
+# We need a complete ODO_mgL timeseries. Therefore we will impute the missing values
+# here, with the package "imputeTS", which is specifically designed to impute time-series
+# observations.
+
+# 113 NAs (due to outlier processing)
+# colSums(is.na(all))
+
+# Make a timeseries object
+ts <- ts(all$do.obs, frequency = 720)
+
+# Impute with imputeTS
+imp_all <- na_ma(ts) # use this function!
+imp_all <- data.table(imp_all)
+imp_all$datetime <- all$datetime
+
+# Check for missing values in the imputed dataset
+#sum(is.na(imp_all)) # No missing values anymore
+
+# Check imputation by plotting the original and the imputed dataset
+# plot(x = all$datetime, y = all$do.obs, type = "l", col = "blue", lwd = 2)
+# lines(x = imp_all$datetime, y = imp_all$imp_all, type = "l",
+#       col = rgb(1, 0, 0, alpha = 0.3), lwd = 2)
+# The imputation worked very well!
+
+# Replace original column with imputed column
+all$do.obs <- imp_all$imp_all
+# sum(is.na(all))
+
+# Step 4: Model choice ---------------------------------------------------------
+# Gas transfer coefficient model: kvachon()
+# - needs wind speed, sensor height, and lake area
+
+# Lake metabolism model: metab.bayesian()
+# Most flexible model
+
+# Step 5: Calculate k600 using the Cole method ---------------------------------
+
+# This function needs specific column names
+all$wnd <- all$wsp
+all$wsp <- NULL
+
+# Normalize wind to 10m sensor height
+wind.scale <- wind.scale(all, wnd.z = 3.05)
+
+all <- merge(all, wind.scale, by = "datetime")
+
+all$wnd <- all$wnd_10
+all$wnd_10 <- NULL
+
+# Also only the 2 columns of interest, otherwise it gets confused
+all.600 <- all[,c("datetime","wnd")]
+k600.vachon <- k.vachon(all.600, lake.area = 2100)
+
+# Merge
+all <- merge(all, k600.vachon, by = "datetime")
+
+# Step 6: Calculate gas-specific k600 ------------------------------------------
+
+kgas <- k600.2.kGAS(all)
+
+# Merge
+all <- merge(all, kgas, by = "datetime")
+
+# only keep k.gas
+all$k600 <- NULL
+
+# Step 7: Calculate dissolved oxygen saturated (do.sat) ------------------------
+
+# I know that the sonde has do.sat measurements, but I have more faith
+# in the authors of this paper to calculate a more accurate do.sat then the
+# sonde-intern calculations.
+
+o2.sat <- o2.at.sat(all[,c('datetime','wtr')])
+
+# Merge
+all <- merge(all, o2.sat, by = "datetime")
+
+# Step 8: Derive photosynthetically active radiation (par) from shortwave irradiation (sw) ----
+# Here, I take the downwelling shortwave irradiation (tilt corrected) from the
+# QAS_L automated weather station a couple of kilometers away from Narsarsuaq
+# It's the closest weather station measuring this parameter, that I could find.
+
+# Derive par from sw
+par <- sw.to.par(all, sw.col = "dsr_cor")
+rownames(par) <- NULL
+
+# Merge
+all <- merge(all, par[,c("datetime", "par")], by = "datetime")
+
+# Step 9: Calculate Actively mixed layer depth (z.mix) -------------------------
+
+################################################################################
+# The max depth of pond B1P1 is about 4m.
+# According to the profiling plots, B1P1 had an actively mixed layer depth of
+# about 2m on Sept 10 2021.
+# We will fit a model with mixed layer depth of 0.5, 1, 2, and 3 meters for this pond.
+# The ponds maximum depth is 4m.
+################################################################################
+
+# Set different mixed layer depths of sensitivity analysis
+# For some reason, metab.bayesian does not recognize z.mix columns
+# if they are not named "z.mix", hence I have to create a dataset for each z.mix
+all2 <- all
+all2$z.mix <- 0.5
+
+all3 <-all
+all3$z.mix <- 1
+
+all4 <- all
+all4$z.mix <- 2
+
+all5 <- all
+all5$z.mix <- 3
+
+# Step 10: Fit model -----------------------------------------------------------
+
+# Choose columns to keep
+all2 <- all2[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all3 <- all3[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all4 <- all4[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+all5 <- all5[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
+
+capture.output({
+  # Mixed layer depth 0.5m over the whole observation period
+bayesian.res_0.5 <- metab(all2, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                      irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                      do.sat.name = "do.sat")
+
+# Mixed layer depth 1m over the whole observation period
+bayesian.res_1 <- metab(all3, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                        do.sat.name = "do.sat")
+
+# Mixed layer depth 2m over the whole observation period
+bayesian.res_2 <- metab(all4, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                        do.sat.name = "do.sat")
+
+# Mixed layer depth 3m over the whole observation period
+bayesian.res_3 <- metab(all5, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
+                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
+                        do.sat.name = "do.sat")
+}, file = "NUL")
+@
+
+\vspace{0.5cm}
+<<sensanal2, results='asis', fig.cap= "\\label{fig:sens}Example of a sensitivity analysis for mixed layer depth in lake B1P1, 2021.
+Figures A-C depict GPP, R, and NEP estimates for different mixed layer depths.
+Figures D-H depict time series of input variables needed for metabolism estimation.", fig.align='center',fig.height=7.5>>=
+# Get standard deviations of estimates
+bayesian.sd_0.5 <- attr(bayesian.res_0.5, "metab.sd")
+bayesian.sd_1 <- attr(bayesian.res_1, "metab.sd")
+bayesian.sd_2 <- attr(bayesian.res_2, "metab.sd")
+bayesian.sd_3 <- attr(bayesian.res_3, "metab.sd")
+
+# Create a date variable
+bayesian.res_0.5$Date <- as.Date(paste(bayesian.res_0.5$year, "-", bayesian.res_0.5$doy, sep = ""), format = "%Y-%j")
+bayesian.res_1$Date <- as.Date(paste(bayesian.res_1$year, "-", bayesian.res_1$doy, sep = ""), format = "%Y-%j")
+bayesian.res_2$Date <- as.Date(paste(bayesian.res_2$year, "-", bayesian.res_2$doy, sep = ""), format = "%Y-%j")
+bayesian.res_3$Date <- as.Date(paste(bayesian.res_3$year, "-", bayesian.res_3$doy, sep = ""), format = "%Y-%j")
+
+# Select columns to keep
+bayesian.res_0.5 <- bayesian.res_0.5[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_1 <- bayesian.res_1[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_2 <- bayesian.res_2[,c("Date", "GPP", "R", "NEP")]
+bayesian.res_3 <- bayesian.res_3[,c("Date", "GPP", "R", "NEP")]
+
+# Create a date variable
+bayesian.sd_0.5$Date <- as.Date(paste(bayesian.sd_0.5$year, "-", bayesian.sd_0.5$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_1$Date <- as.Date(paste(bayesian.sd_1$year, "-", bayesian.sd_1$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_2$Date <- as.Date(paste(bayesian.sd_2$year, "-", bayesian.sd_2$doy, sep = ""), format = "%Y-%j")
+bayesian.sd_3$Date <- as.Date(paste(bayesian.sd_3$year, "-", bayesian.sd_3$doy, sep = ""), format = "%Y-%j")
+
+# Select columns to keep
+bayesian.sd_0.5 <- bayesian.sd_0.5[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_1 <- bayesian.sd_1[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_2 <- bayesian.sd_2[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+bayesian.sd_3 <- bayesian.sd_3[,c("Date", "GPPsd", "Rsd", "NEPsd")]
+
+bayesian.merge_0.5 <- merge(bayesian.res_0.5, bayesian.sd_0.5, by = "Date")
+bayesian.merge_1 <- merge(bayesian.res_1, bayesian.sd_1, by = "Date")
+bayesian.merge_2 <- merge(bayesian.res_2, bayesian.sd_2, by = "Date")
+bayesian.merge_3 <- merge(bayesian.res_3, bayesian.sd_3, by = "Date")
+
+# create Z.mix variable identifier
+bayesian.merge_0.5$z.mix <- "0.5m"
+bayesian.merge_1$z.mix <- "1m"
+bayesian.merge_2$z.mix <- "2m"
+bayesian.merge_3$z.mix <- "3m"
+
+# Merge
+bayesian.merge.all <- rbind(bayesian.merge_0.5, bayesian.merge_1,
+                            bayesian.merge_2, bayesian.merge_3)
+
+# Step 11: Visualize the results -----------------------------------------------
+
+# GPP
+p1 <- ggplot(data = bayesian.merge.all, aes(x = Date, y = GPP, linetype = z.mix)) + 
+  theme_light() +
+  geom_line() +
+  geom_errorbar(aes(ymin = GPP - GPPsd, ymax = GPP + GPPsd), width = 0.12,
+                linetype = "solid") +
+  scale_linetype_manual(
+    values = c("0.5m" = "solid", "1m" = "dashed", "2m" = "dotted", "3m" = "dotdash")
+  ) +
+  ylab(expression(paste("GPP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")"))) +
+  labs(linetype = "Mixed layer depth")
+
+# R
+p2 <- ggplot(data = bayesian.merge.all, aes(x=Date, y=R, linetype=z.mix)) + theme_light() +
+  geom_line() +
+  geom_errorbar(aes(ymin = R-Rsd, ymax = R+Rsd), width = 0.12,
+                linetype = "solid") +
+  scale_linetype_manual(
+    values = c("0.5m" = "solid", "1m" = "dashed", "2m" = "dotted", "3m" = "dotdash")
+  ) +
+  ylab(expression(paste("R (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")"))) +
+  labs(linetype = "Mixed layer depth")
+
+# NEP
+p3 = ggplot(data = bayesian.merge.all, aes(x=Date, y=NEP, linetype=z.mix)) + theme_light() +
+  geom_line() +
+  geom_errorbar(aes(ymin = NEP-NEPsd, ymax = NEP+NEPsd), width = 0.12,
+                linetype = "solid") +
+
+  scale_linetype_manual(
+    values = c("0.5m" = "solid", "1m" = "dashed", "2m" = "dotted", "3m" = "dotdash")
+  ) +
+  ylab(expression(paste("NEP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")"))) +
+  labs(linetype = "Mixed layer depth")
+
+# Plots of ecosystem parameters
+p4 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=do.obs, x=datetime)) +
+  rremove("xlab") +
+  ylab(expression(paste("DO (mg L",NULL^-1,")")))
+
+p5 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=do.sat, x=datetime)) +
+  rremove("xlab") +
+  ylab(expression(paste("DO.sat (mg L",NULL^-1,")")))
+
+p6 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=wtr, x=datetime)) +
+  rremove("xlab") +
+  ylab("Temperature (°C)")
+
+p7 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=par, x=datetime)) +
+  rremove("xlab") +
+  ylab(expression(paste("PAR (",mu,"mol m",NULL^-2," s",NULL^-1,")")))
+
+p8 = ggplot((all)) + theme_light() +
+  geom_line(aes(y=k.gas, x=datetime)) +
+  rremove("xlab") +
+  ylab(expression(paste("Gas transfer coefficient (m",NULL^-1,")")))
+
+fig2 <- ggarrange(p1 + rremove("xlab"), p2 + rremove("xlab"), p3 + rremove("xlab"),
+                  p4 + rremove("xlab"), p5 + rremove("xlab"), p6 + rremove("xlab"),
+                  p7 + rremove("xlab"), p8 + rremove("xlab"), nrow=4, ncol = 2,
+                  common.legend = TRUE, legend = "bottom",
+                  labels = c("A", "B", "C", "D", "E", "F", "G", "H"),label.x = -0.045,
+                  align = "hv")
+
+fig2 <- annotate_figure(fig2) +
+  theme(plot.margin = margin(t = 5, r = 12, b = 5, l = 12))
+print(fig2)
+@
+\vspace{0.5cm}
 

### 2024-12-11 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.tex
Work on manuscript

@@
 % latex table generated in R 4.4.1 by xtable 1.8-4 package
-% Wed Dec 11 09:32:21 2024
+% Wed Dec 11 10:21:21 2024
 \begin{table}[ht]
@@
 As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
-data to estimate mixed layer depth. An initial approach to deal with that problem
-was to investigate the effect of different mixed layer depths on the daily metabolism
+data to estimate mixed layer depth. An initial approach to assess this issue
+was to investigate the effect of different mixed layer depths on daily metabolism
 estimates. For that purpose, we selected a few lakes for different monitoring
-periods (2021, 2022, 2023) and assessed the impact of various, constant
-mixed layer depths over time on the metabolism results.
+periods (2021, 2022, 2023). Notably, mixed layer
+was held constant, which is rarely the case in reality.
+In Figure~\ref{fig:sens}, an example of a sensitivity analysis for lake
+B1P1 in 2021 is depicted. Plots A-C depict the daily GPP, R, and NEP estimates
+for different mixed layer depths. For each mixed layer value, a separate model
+was fitted, holding all other covariates equal.
+Apparently, mixed layer depth substantially
+impacts respiration, where a smaller mixed layer depth is associated with
+higher (more negative) R. In contrast, GPP is barely affected by mixed
+layer depth. Plots D-H show the input variables required to fit the metabolism
+models, apart from mixed layer depth. Since mixed layer particularly
+effects daily R estimates, careful consideration with regards to overcoming
+this limitation is required. Notably, the effect of variation in mixed layer
+depth was consistent across most lakes and monitoring periods
+
+\vspace{0.5cm}
+\begin{figure}
+
+{\centering \includegraphics[width=\maxwidth]{plots/psensanal2-1}
+
+}
+
+\caption{\label{fig:sens}Example of a sensitivity analysis for mixed layer depth in lake B1P1, 2021.
+Figures A-C depict GPP, R, and NEP estimates for different mixed layer depths.
+Figures D-H depict time series of input variables needed for metabolism estimation.}\label{fig:sensanal2}
+\end{figure}
+
+\vspace{0.5cm}
 

### 2024-12-12 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Writing README files

@@
                   p7 + rremove("xlab"), p8 + rremove("xlab"), nrow=4, ncol = 2,
-                  common.legend = TRUE, legend = "bottom",
-                  labels = c("A", "B", "C", "D", "E", "F", "G", "H"),label.x = -0.045,
+                  common.legend = TRUE, legend = "top",
+                  labels = c("A", "B", "C", "D", "E", "F", "G", "H"),label.x = -0.043,
                   align = "hv")
@@
 fig2 <- annotate_figure(fig2) +
-  theme(plot.margin = margin(t = 5, r = 12, b = 5, l = 12))
+  theme(plot.margin = margin(t = 5, r = 8, b = 5, l = 12))
 print(fig2)

### 2024-12-12 LakeMetabolism_project/project_21/code/make_data_2021_intercept_correction.R

@@ -1,671 +1,0 @@
-################################################################################
-# This is a script where the aim is to do an intercept-correction regarding the
-# Sondes-data of the Stickeback-experiments of Blakes Group in Greenland 2021.
-# The variable of interest is Chlorophyll ug/L measured by the Sondes, which will
-# be compared with the actual Chlorophyll content measured chemically at the same specific
-# point in time. All the other datapoints of this sonde will then be adjusted according to
-# this difference. For example, if the sondes measurement at a given time-point 
-# gives 12 ug/L and the chemical analysis gives 11 ug/L, 1 ug/L will be subtracted
-# from all the datapoints of this sonde.
-# The idea is that the Sondes in the different ponds are then adjusted for factory-differences
-# which makes them better comparable.
-# Unfortunately, the chemical measurements were made a few days prior to the
-# deployment sondes. Therefore, I will take the average
-# of the Chlorophyll measurements measured by the deployment sondes at the same day-time
-# as the chemical measurements to compare.
-################################################################################
-
-# Step 0: set up R-script ------------------------------------------------------
-
-rm(list= ls())
-
-library(lubridate)
-
-setwd("~/ZIVI_EAWAG/project_21")
-
-source("~/ZIVI_EAWAG/project_21/Moritz_Luehrig_paper_stuff/methods_packages.R")
-
-# import the chlorophyll A dataset, containing the Chlorophyll mg/L measurements
-# chemically analyzed at a specific point in time
-# Danina told me that they took the water samples mostly right after the deployment,
-# so I added 10 minutes to the last deployment observation to determine the timepoint
-# of the water-sample
-chloro <- fread("~/ZIVI_EAWAG/project_21/data/chloro_a_2021.txt", sep = "\t")
-
-# Import the complete dataset
[…]
